### 2016-05-10 paper3_manuscript.tex
20160510

%\documentclass[draftclsnofoot,onecolumn]{IEEEtran}
\documentclass[3p]{elsarticle}
\usepackage{tipa}
\usepackage{amsmath}%math
\usepackage{amsthm}%proof
\usepackage{xcolor}%color
\usepackage{bm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage[colorlinks,linkcolor=black,anchorcolor=black,citecolor=black]{hyperref}
\usepackage{amsfonts,amssymb}
\usepackage{color,soul}
\theoremstyle{plain}
\newtheorem{assumption}{Assumption}
\newtheorem{mydef}{Definition}
\newtheorem{mylem}{Lemma}
\newtheorem{myrem}{Remark}
\newtheorem{mythm}{Theorem}
\begin{document}
\begin{frontmatter}
\title{Dual terminal sliding mode control}
\author{Zhiqiang Ma}
\author{Guanghui Sun\corref{cor1}}
\ead{guanghuisun@hit.edu.cn}
\cortext[cor1]{Corresponding author}
\address{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China}

\begin{abstract}
\end{abstract}
\begin{keyword}
\end{keyword}
\end{frontmatter}
\section{Introduction}
\section{Dual sliding mode control}
Consider a four-order nominal nonlinear system:
\begin{align}
\dot x_1(t) &= x_2(t)\\
\dot x_2(t) &= f_1(\bm x,t)+g_1(\bm x,t)+b_1(\bm x,t)u_1(t)\\
\dot x_3(t) &= x_4(t)\\
\dot x_5(t) &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)u_2(t)\label{eq:four order system}
\end{align}
where $bm x = [x_1,x_2,x_3,x_4]^T$ is the system vector state; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$; $u_i(t)$, $i=1,2$ stands for the scalar input; $g_i(\bm x,t)$, $i=1,2$  is a defined as a bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0$, meaning the uncertainty and disturbance of the system. For the system mentioned above, we can establish a desired dual sliding manifold as:
\begin{align}
\bm s(t) = [s_1(t),s_2(t)]^T
\end{align}
where
\begin{align}
s_1(t) = x_2(t)+\vert x_1(t)\vert^{\alpha_1} sgn(x_1(t))+x_1^3(t)-x_3(t)\\
s_2(t) = x_4(t)+\vert x_3(t)\vert^{\alpha_2} sgn(x_3(t))+x_3^3(t)+x_1(t)\label{eq:dual sliding manifold}
\end{align}
where $sgn(x)$ is the sign function, and $0<\alpha_i<1$. For the sake of simplicity, the symbol $t$ is usually omitting in this paper, which does not cause any confusion, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding manifold $\bm s(t)$ is often abbreviated to $\bm s$.\par
Dual sliding mode control inputs can be given according the following theorem.
\begin{mythm}
The four-order system (\ref{eq:four order system}) will reach the desired manifold $\bm s = 0$ shown in Eq. (\ref{eq:dual sliding manifold}) in finite time. The states of the system will converge to zero along the manifold $\bm s=0$ in finite time, if the inputs are designed as follows:
\begin{align}
u_1 = -b_1(\bm x)^{-1}(f_1(\bm x)+\alpha_1\vert x_1\vert^{\alpha_1-1}x_2+3x_1^2x_2-x_4+k_1sgn(s_1))\\
u_2 = -b_2(\bm x)^{-1}(f_2(\bm x)+\alpha_2\vert x_3\vert^{\alpha_2-1}x_4+3x_3^2x_4+x_2+k_2sgn(s_2))
\end{align}
where $k_i = l_i+\eta_i$, $i=1,2$ , $\eta_i>0$ is a positive scalar value.
\end{mythm}
\begin{proof}
Consider the Lyapunov function $V=\frac{1}{2}{\bm s}^T\bm s$, the derivative of which with respect to time $\dot V = {\bm s}^T \bm {\dot s}$ follows
\begin{align}
\dot V &= {\bm s}^T\bm{\dot  s}\\
&=s_1\dot s_1+s_2\dot s_2\\
&=s_1(f_1(\bm x)+g_1(\bm x)+b_1(\bm x)u_1+\alpha_1\vert x_1\vert^{\alpha_1-1}x_2+3x_1^2x_2-x_4)\\
&\quad +s_2(f_2(\bm x)+g_2(\bm x)+b_2(\bm x)u_2+\alpha_2\vert x_3\vert^{\alpha_2-1}x_4+3x_3^2x_4+x_2)\label{eq:V_1}
\end{align}
By substituting inputs (\ref{eq:dual sliding manifold}) in Eq. (\ref{eq:V_1}) yeilds
\begin{align}
\dot V &= s_1(-k_1sgn(s_1)+g_1(\bm x))+s_2(-k_2sgn(s_2)+g_2(\bm x))\\
&= -\eta_1s_1sgn(s_1)-\eta_2s_2sgn(s_2)+(g_1(\bm x)s_1 - l_1s_1sgn(s_1))+(g_2(\bm x)s_2 - l_2s_2sgn(s_2))\\
&= -\eta_1\vert s_1\vert-\eta_2\vert s_2\vert+(g_1(\bm x)s_1 - l_1\vert s_1\vert)+(g_2(\bm x)s_2 - l_2\vert s_2\vert)\\
&\le - \min(\eta_1,\eta_2)(\vert s_1\vert+\vert s_2\vert)\\
&\le -\min(\eta_1,\eta_2)({\bm s}^T\bm s)^\frac{1}{2}\\
&\le -\sqrt{2}\min(\eta_1,\eta_2)V^\frac{1}{2}\le 0
\end{align}
Hence, the system (\ref{eq:four order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergent time can be calculated according to the finite time convergence theory. 
\end{proof}
\section{Acknowledgment}
This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61503097).
\section{References}
\bibliography{paper3_ref}
\bibliographystyle{elsarticle-num}
\end{document}

### 2016-05-11 paper3_manuscript.tex
20160511

@@
 \begin{align}
+\begin{split}
 \dot x_1(t) &= x_2(t)\\
@@
 \dot x_3(t) &= x_4(t)\\
-\dot x_5(t) &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)u_2(t)\label{eq:four order system}
+\dot x_5(t) &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)u_2(t),\label{eq:four order system}
+\end{split}
 \end{align}
@@
 \begin{align}
-\bm s(t) = [s_1(t),s_2(t)]^T
+\bm s(t) = [s_1(t),s_2(t)]^T,
 \end{align}
@@
 \begin{align}
-s_1(t) = x_2(t)+\vert x_1(t)\vert^{\alpha_1} sgn(x_1(t))+x_1^3(t)-x_3(t)\\
-s_2(t) = x_4(t)+\vert x_3(t)\vert^{\alpha_2} sgn(x_3(t))+x_3^3(t)+x_1(t)\label{eq:dual sliding manifold}
+\begin{split}
+s_1(t) &= x_2(t)+\vert x_1(t)\vert^{\alpha} sgn(x_1(t))+x_1^3(t)-x_3(t)\\
+s_2(t) &= x_4(t)+\vert x_3(t)\vert^{\alpha} sgn(x_3(t))+x_3^3(t)+x_1(t),\label{eq:dual sliding manifold}
+\end{split}
 \end{align}
-where $sgn(x)$ is the sign function, and $0<\alpha_i<1$.
+where $sgn(x)$ is the sign function, and $0<\alpha<1$ is a positive constant.
 For the sake of simplicity, the symbol $t$ is usually omitting in this paper, which does not cause any confusion, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding manifold $\bm s(t)$ is often abbreviated to $\bm s$.\par
-Dual sliding mode control inputs can be given according the following theorem.
-\begin{mythm}
-The four-order system (\ref{eq:four order system}) will reach the desired manifold $\bm s = 0$ shown in Eq.
+There exist two lemmas about the finite convergence theory, providing convergent forms which contribute to the verification of the finite convergence about the dual sliding mode control.
+\begin{mylem}
+As described in \cite{moulay2006finite}, it is assumed that the continuous function $V(t)$ is positive-define, satisfying the following condition:
+\begin{align}
+\dot V(t)\le -dV^\beta(t)\quad\forall t\ge t_0, V(t_0)\ge 0,
+\end{align}
+where $d$ is a positive scalar, and $0<\beta<1$. Then the function $V(t)$ can converge to the origin for any given $t_0$, and typically the finite convergent time $t_r$ can be given as follows:
+\begin{align}
+t_r \le t_0+\frac{V^{1-\beta}(t_0)}{d(1-\beta)}.
+\end{align}\label{lemma:1}
+\end{mylem}
+\begin{mylem}
+Considering a two-order system:
+\begin{align}
+\dot x_1&=-\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2\\
+\dot x_2&=-\vert x_2\vert^\alpha sgn(x_3)-x_2^3-x_1.\label{eq:normal sliding manifold}
+\end{align}\par
+Selecting $V(t) = \frac{x_1^2+x_2^2}{2}$ obtains the finite convergent time as follows \cite{moulay2006finite}:
+%since $\vert x\vert-x^\alpha+\vert x\vert \ge 0,0<\alpha<1$
+\begin{align}
+%t_s\le t_0+\frac{2(x_1^2+x_2^2)^{1-\alpha}}{1-\alpha}
+t_s\le t_0+\frac{(2V(t_0))^{\frac{1-\alpha}{2}}}{1-\alpha},
+\end{align}
+where the definitions of  $t_s$, $t_0$, $\alpha$ are similar to Lemma \ref{lemma:1}. Introducing the amplitude scalar $d$ into the Eqs.~(\ref{eq:normal sliding manifold}) obtains  more normal forms:
+\begin{align}
+\dot x_1&=-d(\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2)\\
+\dot x_2&=-d(\vert x_2\vert^\alpha sgn(x_2)-x_2^3-x_1),\label{eq:more normal sliding manifold}
+\end{align}
+the convergent time of which is 
+\begin{align}
+t_s\le t_0+\frac{(2V(t_0))^{\frac{1-\alpha}{2}}}{d(1-\alpha)}.
+\end{align}\label{lemma:2}
+\end{mylem}
+For stabilization of the four-order system shown as~Eq. (\ref{eq:four order system}), dual sliding mode control inputs can be given according the following theorem.
+\begin{mythm}\label{theorem:1}Dual Sliding Mode (DSM) Control Design. 
+The four-order system (\ref{eq:four order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq.
 (\ref{eq:dual sliding manifold}) in finite time.
@@
 \begin{align}
-u_1 = -b_1(\bm x)^{-1}(f_1(\bm x)+\alpha_1\vert x_1\vert^{\alpha_1-1}x_2+3x_1^2x_2-x_4+k_1sgn(s_1))\\
-u_2 = -b_2(\bm x)^{-1}(f_2(\bm x)+\alpha_2\vert x_3\vert^{\alpha_2-1}x_4+3x_3^2x_4+x_2+k_2sgn(s_2))
+u_1 &= -b_1(\bm x)^{-1}(f_1(\bm x)+\alpha\vert x_1\vert^{\alpha-1}x_2+3x_1^2x_2-x_4+k_1sgn(s_1))\\
+u_2 &= -b_2(\bm x)^{-1}(f_2(\bm x)+\alpha\vert x_3\vert^{\alpha-1}x_4+3x_3^2x_4+x_2+k_2sgn(s_2)),
 \end{align}
-where $k_i = l_i+\eta_i$, $i=1,2$ , $\eta_i>0$ is a positive scalar value.
+where $k_i = l_i+\eta_i$, $i=1,2$; $\eta_i>0$ is a positive scalar value.
 \end{mythm}
@@
 \begin{align}
+\begin{split}
 \dot V &= {\bm s}^T\bm{\dot  s}\\
 &=s_1\dot s_1+s_2\dot s_2\\
-&=s_1(f_1(\bm x)+g_1(\bm x)+b_1(\bm x)u_1+\alpha_1\vert x_1\vert^{\alpha_1-1}x_2+3x_1^2x_2-x_4)\\
-&\quad +s_2(f_2(\bm x)+g_2(\bm x)+b_2(\bm x)u_2+\alpha_2\vert x_3\vert^{\alpha_2-1}x_4+3x_3^2x_4+x_2)\label{eq:V_1}
+&=s_1(f_1(\bm x)+g_1(\bm x)+b_1(\bm x)u_1+\alpha\vert x_1\vert^{\alpha-1}x_2+3x_1^2x_2-x_4)\\
+&\quad +s_2(f_2(\bm x)+g_2(\bm x)+b_2(\bm x)u_2+\alpha\vert x_3\vert^{\alpha-1}x_4+3x_3^2x_4+x_2).\label{eq:V_1}
+\end{split}
 \end{align}
-By substituting inputs (\ref{eq:dual sliding manifold}) in Eq. (\ref{eq:V_1}) yeilds
-\begin{align}
+Substituting inputs (\ref{eq:dual sliding manifold}) in~Eq. (\ref{eq:V_1}) yields
+\begin{align*}
 \dot V &= s_1(-k_1sgn(s_1)+g_1(\bm x))+s_2(-k_2sgn(s_2)+g_2(\bm x))\\
@@
 &\le -\min(\eta_1,\eta_2)({\bm s}^T\bm s)^\frac{1}{2}\\
-&\le -\sqrt{2}\min(\eta_1,\eta_2)V^\frac{1}{2}\le 0
+&\le -\sqrt{2}\min(\eta_1,\eta_2)V^\frac{1}{2}\le 0.
+\end{align*}
+Hence, the system (\ref{eq:four order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergent time can be calculated according to the finite time convergence theory.\par
+Once the system (\ref{eq:four order system}) reaches the desired manifold~(\ref{eq:dual sliding manifold}), the whole system is handled by the reduced system:
+\begin{align*}
+\dot x_1&=-\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_3\\
+\dot x_3&=-\vert x_3\vert^\alpha sgn(x_3)-x_3^3-x_1.
+\end{align*}\par
+The total convergent time can be calculated by dividing the convergence into two phase with respect to the relation between the system and the manifold, namely, the approaching phase and the sliding phase, and specifically, according to Lemma \ref{lemma:2}, the total finite convergent time $t_f$ can be given out directly:
+\begin{align}
+t_f = \underbrace{t_0+\frac{\sqrt{2}V^{\frac{1}{2}}(t_0)}{\min(\eta_1,\eta_2)}}_{t_r}+\underbrace{\frac{(2\hat V(t_r))^{\frac{1-\alpha}{2}}}{1-\alpha}}_{t_s}<\infty,
 \end{align}
-Hence, the system (\ref{eq:four order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergent time can be calculated according to the finite time convergence theory.
+where $\hat V(t) = \frac{x_1^2+x_3^2}{2}$ is the Lyapunov function describing the convergent motion of the reduced system.
+The approaching and sliding time are defined as $t_r$ and $t_s$, respectively.
+This completes the proof.
 \end{proof}
+On the basis of Theorem \ref{theorem:1}, we can develop the parameters in the manifold to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:four order system}), and furthermore this method makes the design of the manifold more flexible.
+Considering the system~(\ref{eq:four order system}) with the manifold manifold $\bm s = [s_1,s_2]^T$, the details of which can be described by following expressions:
+\begin{align}
+\begin{split}
+s_1(t) &= x_2(t)+\gamma(\vert x_1(t)\vert^{\alpha} sgn(x_1(t))+x_1^3(t))-\lambda x_3(t)\\
+s_2(t) &= x_4(t)+\gamma(\vert x_3(t)\vert^{\alpha} sgn(x_3(t))+x_3^3(t))+\lambda x_1(t),\label{eq:modified dual sliding manifold}
+\end{split}
+\end{align}
+where $\gamma$ is a positive constant and $\lambda\in R$ is a regulable parameter. Hence, the modified dual sliding mode control inputs are formed in the following theorem.
+\begin{mythm}\label{theorem:2}Modified Dual Sliding Mode (MDSM) Control Design.
+The four-order system (\ref{eq:four order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq.
+(\ref{eq:modified dual sliding manifold}) in finite time.
+The states of the system will converge to zero along the manifold $\bm s=0$ in finite time, if the inputs are designed as follows:
+\begin{align}
+u_1 &= -b_1(\bm x)^{-1}(f_1(\bm x)+\gamma\alpha\vert x_1\vert^{\alpha-1}x_2+3\gamma x_1^2x_2-\lambda x_4+k_1sgn(s_1))\\
+u_2 &= -b_2(\bm x)^{-1}(f_2(\bm x)+\gamma\alpha\vert x_3\vert^{\alpha-1}x_4+3\gamma x_3^2x_4+\lambda x_2+k_2sgn(s_2)),
+\end{align}
+where $k_i = l_i+\eta_i$, $i=1,2$; $\eta_i>0$ is a positive scalar value. The total finite convergent time can be described as:
+\begin{align}
+t_f = \underbrace{t_0+\frac{\sqrt{2}V^{\frac{1}{2}}(t_0)}{\min(\eta_1,\eta_2)}}_{t_r}+\underbrace{\frac{(2\hat V(t_r))^{\frac{1-\alpha}{2}}}{\gamma(1-\alpha)}}_{t_s}<\infty,
+\end{align}
+\end{mythm}
+\begin{proof}
+The proof is similar to Theorem \ref{theorem:1}, hence it's omitted here.
+\end{proof}
+\begin{myrem}
+Design a terminal sliding mode controller for the four-order system~(\ref{eq:four order system}), and theoretically, the finite convergent time can be calculated by applying the techniques mentioned in \cite{feng2013nonsingular}.
+\end{myrem}
 \section{Acknowledgment}

### 2016-05-11 paper3_manuscript.tex
20160512

@@
 \begin{align}
-t_f = \underbrace{t_0+\frac{\sqrt{2}V^{\frac{1}{2}}(t_0)}{\min(\eta_1,\eta_2)}}_{t_r}+\underbrace{\frac{(2\hat V(t_r))^{\frac{1-\alpha}{2}}}{\gamma(1-\alpha)}}_{t_s}<\infty,
+t_f = \underbrace{t_0+\frac{\sqrt{2}V^{\frac{1}{2}}(t_0)}{\min(\eta_1,\eta_2)}}_{t_r}+\underbrace{\frac{(2\hat V(t_r))^{\frac{1-\alpha}{2}}}{\gamma(1-\alpha)}}_{t_s}<\infty,\label{eq:total convergent time}
 \end{align}
@@
 \end{proof}
+\begin{myrem}
+After introducing the parameters $\lambda$ and $\gamma$ into the DSM scheme, the performances of the approaching and sliding phases become regulatable, meaning that these parameters can adjust the convergent time analytically.
+Although $\lambda$ does not appear in Eq.~(\ref{eq:total convergent time}), the establishment of $V(t_0)$ involves it when the state $\bm x$ has been fixed.
+Strictly speaking, it affects the approaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V(t)=\bm s^T(t)\bm s(t) = 0,\forall t\ge t_r$.
+\end{myrem}
 \begin{myrem}

### 2016-05-12 paper3_manuscript.tex
20160512

@@
 \begin{align}
-u_1 &= -b_1(\bm x)^{-1}(f_1(\bm x)+\alpha\vert x_1\vert^{\alpha-1}x_2+3x_1^2x_2-x_4+k_1sgn(s_1))\\
-u_2 &= -b_2(\bm x)^{-1}(f_2(\bm x)+\alpha\vert x_3\vert^{\alpha-1}x_4+3x_3^2x_4+x_2+k_2sgn(s_2)),
+u_1 &= -b_1^{-1}(\bm x)(f_1(\bm x)+\alpha\vert x_1\vert^{\alpha-1}x_2+3x_1^2x_2-x_4+k_1sgn(s_1))\\
+u_2 &= -b_2^{-1}(\bm x)(f_2(\bm x)+\alpha\vert x_3\vert^{\alpha-1}x_4+3x_3^2x_4+x_2+k_2sgn(s_2)),
 \end{align}
@@
 \begin{align}
-u_1 &= -b_1(\bm x)^{-1}(f_1(\bm x)+\gamma\alpha\vert x_1\vert^{\alpha-1}x_2+3\gamma x_1^2x_2-\lambda x_4+k_1sgn(s_1))\\
-u_2 &= -b_2(\bm x)^{-1}(f_2(\bm x)+\gamma\alpha\vert x_3\vert^{\alpha-1}x_4+3\gamma x_3^2x_4+\lambda x_2+k_2sgn(s_2)),
+\begin{split}
+u_1 &= -b_1^{-1}(\bm x)(f_1(\bm x)+\gamma\alpha\vert x_1\vert^{\alpha-1}x_2+3\gamma x_1^2x_2-\lambda x_4+k_1sgn(s_1))\\
+u_2 &= -b_2^{-1}(\bm x)(f_2(\bm x)+\gamma\alpha\vert x_3\vert^{\alpha-1}x_4+3\gamma x_3^2x_4+\lambda x_2+k_2sgn(s_2)),\label{eq:modified input}
+\end{split}
 \end{align}
@@
 \end{proof}
+After introducing the parameters $\lambda$ and $\gamma$ into the DSM scheme, the performances of the approaching and sliding phases become regulatable, meaning that these parameters can adjust the convergent time analytically.
+Although $\lambda$ does not appear in Eq.~(\ref{eq:total convergent time}), the establishment of $V(t_0)$ involves it when the state $\bm x(t_0)$ has been fixed.
+Strictly speaking, it affects the approaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V(t)=\bm s^T(t)\bm s(t) = 0,\forall t\ge t_r$.
+Admittedly, the variety of $\lambda$ is only modestly helpful in this approaching time regulation due to its limited effect on $V(t_0)$.
+$\eta$ is said to be an ''approaching speed'' according to its function, a suitable selection of which will adjust the approaching time as desired in some extent.
+Hence, $\lambda$ cooperates with $\eta$ to manage the approaching status, and by utilizing the similar analysis, owing to $\gamma$ adjusting the speed of sliding phase, it can be defined as the management parameter of the sliding status.
 \begin{myrem}
-After introducing the parameters $\lambda$ and $\gamma$ into the DSM scheme, the performances of the approaching and sliding phases become regulatable, meaning that these parameters can adjust the convergent time analytically.
-Although $\lambda$ does not appear in Eq.~(\ref{eq:total convergent time}), the establishment of $V(t_0)$ involves it when the state $\bm x$ has been fixed.
-Strictly speaking, it affects the approaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V(t)=\bm s^T(t)\bm s(t) = 0,\forall t\ge t_r$.
+For the proposed designs, the parameter $\gamma$ can be defined as different scalar for the individual input, if so, one can produce the total convergent time as:
+\begin{align}
+t_f = \underbrace{t_0+\frac{\sqrt{2}V^{\frac{1}{2}}(t_0)}{\min(\eta_1,\eta_2)}}_{t_r}+\underbrace{\frac{(2\hat V(t_r))^{\frac{1-\alpha}{2}}}{\min(\gamma_1,\gamma_2)(1-\alpha)}}_{t_s}<\infty,\label{eq:normal total convergent time}
+\end{align}
+with $\gamma_i$ corresponding to the original parameter $\gamma$ in input $u_i$.
 \end{myrem}
-\begin{myrem}
-Design a terminal sliding mode controller for the four-order system~(\ref{eq:four order system}), and theoretically, the finite convergent time can be calculated by applying the techniques mentioned in \cite{feng2013nonsingular}.
-\end{myrem}
+The finite convergence of the DSM and MDSM scheme has been verified clearly, but similar to the conventional terminal sliding mode control, there exists another obstacle in the design mentioned above, namely, the issue of the singularity in control inputs.
+Essentially, the singularity occurs in Eq.~(\ref{eq:modified input}) when $x_1=0$ but $x_2\neq 0$ in $u_1$ (the phenomena happens to $u_2$ under the same condition).
+For coping with the singularity, a nonsingular MDSM scheme is presented after introducing an analytical technique into the MDSM scheme based on the following lemma \cite{feng2013nonsingular}.
+\begin{mylem}\label{lemma:3}
+Considering the four-order system (\ref{eq:four order system}), the terminal sliding mode manifold can be designed as:
+\begin{align*}
+s_1(t) &= x_2(t)+\gamma_1\vert x_1\vert^{\alpha_1}sgn(x_1)\\
+s_2(t) &= x_4(t)+\gamma_2\vert x_3\vert^{\alpha_2}sgn(x_3),
+\end{align*}
+and nonsingular inputs are given out directly as follows:
+\begin{align*}
+u_1 &= b^{-1}_1(\bm x)(-f_1(\bm x)+sat(u_{f1},u_{s1})-k_1sgn(s_1))\\
+u_2 &= b^{-1}_2(\bm x)(-f_2(\bm x)+sat(u_{f2},u_{s2})-k_2sgn(s_2)),
+\end{align*}
+in which
+\begin{align*}
+u_{f1}&=-\gamma_1\alpha_1\vert x_1\vert^{\alpha_1-1}x_2\\
+u_{f2}&=-\gamma_2\alpha_2\vert x_3\vert^{\alpha_2-1}x_4,
+\end{align*}
+where $sat(u_f,u_s)$ is a saturation function:
+\begin{align}
+sat(u_f,u_s)=
+\begin{cases}
+u_s\quad &u_f\ge u_s\\
+u_f\quad &-u_s\le u_f< u_s\\
+-u_s\quad &u_f\le -u_s
+\end{cases},
+\end{align}
+and $u_s>0$ can be determined according to the requirements of the performance.\par
+Adopting the control scheme mentioned above, the system~(\ref{eq:four order system}) will converge to zero in finite time without any singularity occurring during the regulation process.
+\end{mylem}
+\begin{mythm}
+Consider a four-order system (\ref{eq:four order system}), and for eliminating the singularity in inputs of the MDSM scheme, select a new inputs to complete the nonsingular MDSM scheme.
+Introducing the saturation terms into the original inputs yields:
+\begin{align}
+u_1 &= -b_1^{-1}(\bm x)(f_1(\bm x)-sat(u_{f1},u_{s1})+3\gamma x_1^2x_2-\lambda x_4+k_1sgn(s_1))\\
+u_2 &= -b_2^{-1}(\bm x)(f_2(\bm x)-sat(u_{f2},u_{s2})+3\gamma x_3^2x_4+\lambda x_2+k_2sgn(s_2)),\label{eq:nonsingular modified input}
+\end{align}
+one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:four order system}), providing the finite time convergence by using sliding mode technique.
+\end{mythm}
+\begin{proof}
+The proof is similar to the graphical analysis mentioned in \cite{feng2013nonsingular}, and omitted here.
+\end{proof}
+\section{Dual sliding mode control for rigid manipulators}
+In this section, a dual sliding mode control is proposed for the rigid $2$-link robot manipulator
+\begin{align}
+\bm {M(q)\ddot q}+\bm {C(q,\dot q)}+\bm {g(q)}=\bm {\tau}(t)+\bm{d}(t),
+\end{align}
+where $\bm q(t)$ is the $2\times 1$ vector of joint angular position; $\bm {M(q)}$ is the $2\times 2$ inertia matrix; $\bm{C(q,\dot q)}$ denotes the Coriolis and centrifugal forces by using the $n\times1$ vector; $\bm{g(q)}$ stands for the $n\times 1$ gravitational torque; $\bm{\tau}(t)$ is referred to as the joint torques which are the inputs practically; $\bm d(t)$ expresses the $n\times 1$ bounded input disturbances vector.
 \section{Acknowledgment}

### 2016-05-13 paper3_manuscript.tex
20160513

@@
 \theoremstyle{plain}
-\newtheorem{assumption}{Assumption}
+\newtheorem{myas}{Assumption}
 \newtheorem{mydef}{Definition}
@@
 \begin{split}
-\dot V &= {\bm s}^T\bm{\dot  s}\\
+\dot V &= {\bm s}^T\dot{\bm  s}\\
 &=s_1\dot s_1+s_2\dot s_2\\
@@
 \begin{align}
-\bm {M(q)\ddot q}+\bm {C(q,\dot q)}+\bm {g(q)}=\bm {\tau}(t)+\bm{d}(t),
+M(\bm q)\ddot {\bm q}+C(\bm q,\dot {\bm q})+g(\bm q)= \bm\tau(t)+{\bm d}(t),\label{eq:lagrangian system}
 \end{align}
-where $\bm q(t)$ is the $2\times 1$ vector of joint angular position; $\bm {M(q)}$ is the $2\times 2$ inertia matrix; $\bm{C(q,\dot q)}$ denotes the Coriolis and centrifugal forces by using the $n\times1$ vector; $\bm{g(q)}$ stands for the $n\times 1$ gravitational torque; $\bm{\tau}(t)$ is referred to as the joint torques which are the inputs practically; $\bm d(t)$ expresses the $n\times 1$ bounded input disturbances vector.
+where $\bm q(t) = $ is the $2\times 1$ vector of joint angular position; ${M(\bm q)}$ is the $2\times 2$ inertia matrix; ${C(\bm q,\dot{\bm q})}$ denotes the Coriolis and centrifugal forces by using the $n\times1$ vector; ${g(\bm q)}$ stands for the $n\times 1$ gravitational torque; $\bm{\tau}(t)$ is referred to as the joint torques which are the inputs practically; $\bm d(t)$ expresses the $n\times 1$ bounded input disturbances vector.
+Normally, there exist some uncertainties in the manipulator, producing the dynamic equations:
+\begin{align}
+(M_0(\bm q)+\Delta {M(\bm q))\ddot {\bm q}}+{C_0(\bm q,\dot {\bm q})+\Delta C(\bm q,\dot {\bm q})}+g_0(\bm q)+\Delta g(\bm q)=\bm {\tau}(t)+\bm{d}(t),
+\end{align}
+where $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$ and $g_0(\bm q)$ are the estimated terms affected by the the uncertainties including $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$, $g_0(\bm q)$, and the disturbance $\bm{d}(t)$.
+Particularly, the following assumption is exhibited to explain the bounded characteristics of the robot dynamics \cite{feng2002non}:
+\begin{align*}
+&\Vert M(\bm q)\Vert< \theta_0\\
+&\Vert C(\bm q,\dot {\bm q})\Vert< \phi_0+\phi_1\Vert\bm q\Vert+\phi_2\Vert\dot{\bm q}\Vert^2\\
+&\Vert g(\bm q)\Vert< \psi_0+\psi_1\Vert\bm q\Vert\\
+&\Vert \bm {\rho}(t)\Vert< \mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2,
+\end{align*}
+where $\bm {\rho}(t) = -\Delta M(\bm q)-\Delta C(\bm q,\dot {\bm q})-\Delta g(\bm q)$, and $\theta_0$, $\phi_0$, $\phi_1$, $\phi_2$, $\psi_0$, $\psi_1$, $\mu_0$, $\mu_1$, $\mu_2$ are positive constants.\par
+Select $\bm q_d$ as the desired state of the Lagrangian system~(\ref{eq:lagrangian system}), and the derivative of $\bm q_d$ is designated as $\dot {\bm q}_d$.
+Hence the state error can be given out intuitively:
+\begin{align}
+\bm \varepsilon = \bm q -\bm q_d
+\end{align}
+With the purpose of simplifying the proceeding derivation, some symbol definitions for vector operating are presented in advance.
+For expressing the $n$-dimension vector including a sort of compound functions, the following symbol is introduced:
+\begin{align*}
+\lceil\bm h(t)\bm p(t)+\bm v(t)\rfloor = (h_1(t)p_1(t)+v_1(t),h_2(t)p_2(t)+v_2(t),\ldots,h_n(t)p_n(t)+v_n(t))^T.
+\end{align*}
+On the basis of the above results, one can design the dual sliding mode scheme for $2$-link robot manipulator by utilizing the following theorem.
+\begin{mythm}
+For the rigid $2$-link manipulator~(\ref{eq:lagrangian system}), if the dual sliding mode manifold is selected as
+\begin{align}
+\bm s = \dot{\bm \varepsilon}+C_\gamma\lceil\bm{sgn}^\alpha(\bm \varepsilon)+\bm\varepsilon^3\rfloor+C_\lambda{\bm\varepsilon},
+\end{align}
+where
+\begin{align}
+\begin{split}
+&C_\gamma=diag[\gamma_1,\gamma_2]\\
+&C_\lambda=
+\begin{pmatrix}
+0 &-\lambda\\ \lambda &0
+\end{pmatrix}\\
+&{sgn}^\alpha(\varepsilon)=\vert\varepsilon\vert^\alpha sgn(\varepsilon),
+\end{split}
+\end{align}
+furthermore, one can obtain the corresponding input as follows to stabilize the system~(\ref{eq:lagrangian system}) as desired in finite time.
+\begin{align}
+\begin{split}
+\bm\tau &= \bm u_0+\bm u_1 +\bm u_2\\
+\bm u_0 &= -M_0(\bm q)C_r\lceil\alpha\vert\bm\varepsilon\vert^{\alpha-1}\dot{\bm \varepsilon}+3\bm \varepsilon^2\dot{\bm \varepsilon}\rfloor-M_0(\bm q)C_\lambda\dot{\bm \varepsilon}\\
+\bm u_1 &= M_0(\bm q)\ddot {\bm q}_d+C_0(\bm q,\dot {\bm q})+g_0(\bm q)\\
+\bm u_2 &= -\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2).
+\end{split}
+\end{align}
+in which it is assumed that the parameters $\mu_0$, $\mu_1$ and $\mu_2$ are known.
+\end{mythm}
+\begin{proof}
+Select the Lyapunov function
+\begin{align}
+V=\frac{1}{2}\bm s^T\bm s,
+\end{align} 
+the derivative of which can be described as
+\begin{align}
+\begin{split}
+\dot V &= \bm s^T\dot{\bm s}=\bm s^T(\ddot{\bm \varepsilon}+C_r\lceil\alpha\vert\bm\varepsilon\vert^{\alpha-1}\dot{\bm \varepsilon}+3\bm \varepsilon^2\dot{\bm \varepsilon}\rfloor+C_\lambda\dot{\bm \varepsilon})\\
+&=\bm s^T(M_0^{-1}(\bm q)(-M_0(\bm q)\ddot {\bm q}_d-C_0(\bm q,\dot {\bm q})-g_0(\bm q)+\bm\tau+\bm\rho(t))\\
+&\quad+C_r\lceil\alpha\vert\bm\varepsilon\vert^{\alpha-1}\dot{\bm \varepsilon}+3\bm \varepsilon^2\dot{\bm \varepsilon}\rfloor+C_\lambda\dot{\bm \varepsilon})\\
+&=\bm s^T(M_0^{-1}(\bm q)(\bm u_0+\bm u_2+\bm\rho(t))+C_r\lceil\alpha\vert\bm\varepsilon\vert^{\alpha-1}\dot{\bm \varepsilon}+3\bm \varepsilon^2\dot{\bm \varepsilon}\rfloor+C_\lambda\dot{\bm \varepsilon})\\
+&=\bm s^TM_0^{-1}(\bm q)(-\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2)+\bm\rho(t))\\
+&\le (\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2)\Vert M_0^{-1}(\bm q)\Vert\Vert \bm s\Vert
+\end{split}
+\end{align}
+\end{proof}
 \section{Acknowledgment}

### 2016-05-13 paper3_manuscript.tex
20160513

@@
 \newtheorem{mylem}{Lemma}
+\newtheorem{mythm}{Theorem}
+
+%\theoremstyle{remark}
+\theoremstyle{remark}
 \newtheorem{myrem}{Remark}
-\newtheorem{mythm}{Theorem}
+
 \begin{document}
@@
 \begin{align}
+\begin{split}
 \dot x_1&=-\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2\\
 \dot x_2&=-\vert x_2\vert^\alpha sgn(x_3)-x_2^3-x_1.\label{eq:normal sliding manifold}
+\end{split}
 \end{align}\par
@@
 \end{mylem}
-\begin{mythm}
+\begin{mythm}\label{theorem:3}
 Consider a four-order system (\ref{eq:four order system}), and for eliminating the singularity in inputs of the MDSM scheme, select a new inputs to complete the nonsingular MDSM scheme.
@@
 On the basis of the above results, one can design the dual sliding mode scheme for $2$-link robot manipulator by utilizing the following theorem.
-\begin{mythm}
+\begin{mythm}\label{theorem:4}
 For the rigid $2$-link manipulator~(\ref{eq:lagrangian system}), if the dual sliding mode manifold is selected as
 \begin{align}
-\bm s = \dot{\bm \varepsilon}+C_\gamma\lceil\bm{sgn}^\alpha(\bm \varepsilon)+\bm\varepsilon^3\rfloor+C_\lambda{\bm\varepsilon},
+\bm s = \dot{\bm \varepsilon}+C_\gamma\lceil\bm{sgn}^\alpha(\bm \varepsilon)+\bm\varepsilon^3\rfloor+C_\lambda{\bm\varepsilon},\label{eq:lagrangian manifold}
 \end{align}
@@
 &=\bm s^TM_0^{-1}(\bm q)(-\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2)+\bm\rho(t))\\
-&\le (\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2)\Vert M_0^{-1}(\bm q)\Vert\Vert \bm s\Vert
+&\le -(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2)\Vert M_0^{-1}(\bm q)\Vert\Vert \bm s\Vert+\Vert\bm\rho(t)\Vert\Vert M_0^{-1}(\bm q)\Vert\Vert \bm s\Vert\\
+&\le -(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2-\Vert\bm\rho(t)\Vert)\Vert M_0^{-1}(\bm q)\Vert\Vert \bm s\Vert.
 \end{split}
 \end{align}
+The above result means that
+\begin{align}
+\dot V \le \varrho\Vert\bm s\Vert<0,
+\end{align}
+where
+\begin{align}
+\varrho=(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2-\Vert\bm\rho(t)\Vert)\Vert M_0^{-1}(\bm q)\Vert>0
+\end{align}
+and $\Vert\bm s\Vert\neq 0$, hence, the Lyapunov stability has been proved, meaning that the system will reach the desired manifold~(\ref{eq:lagrangian manifold}) in finite time.
+Once the reaching condition is satisfied, one can achieve a reduced system by substituting $\bm s = 0$ into the system~(\ref{eq:lagrangian system}).
+It owns the form, similar to Eq.~(\ref{eq:normal sliding manifold}), and therefore, one can adopt Theorem \ref{theorem:2} to drive the reduced system converging to the origin in finite time.
+The proof is completed.
 \end{proof}
+\begin{myrem}
+At this point, the dual sliding mode control scheme for $2$-link robot manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator.
+Consider a $n$-link robot manipulator in where $n$ is an even number, and the desired sliding manifold can be designed as
+\begin{align}
+\bm s = \dot{\bm \varepsilon}+C_{\gamma n}\lceil\bm{sgn}^\alpha(\bm \varepsilon)+\bm\varepsilon^3\rfloor+C_{\lambda n}{\bm\varepsilon},
+\end{align}
+where
+\begin{align}
+\begin{split}
+&C_{\gamma n}=diag[\gamma_1,\gamma_2,\ldots,\gamma_n]\\
+&C_{\lambda n}=
+\begin{pmatrix}
+\begin{pmatrix}
+0 &-\lambda\\ \lambda &0
+\end{pmatrix} &O_{2\times 2} & & &\\
+O_{2\times 2} &\begin{pmatrix}
+0 &-\lambda\\ \lambda &0
+\end{pmatrix} & & &\\
+& &\ddots & &\\
+& & &\begin{pmatrix}
+0 &-\lambda\\ \lambda &0
+\end{pmatrix} &O_{2\times 2}\\
+& & &O_{2\times 2} &\begin{pmatrix}
+0 &-\lambda\\ \lambda &0
+\end{pmatrix}
+\end{pmatrix}.
+\end{split}
+\end{align}\par
+Referring to Theorem \ref{theorem:4}, one can obtain the dual sliding mode control input for the even $n$-link manipulator.
+Essentially, this technique requires that the sliding mode manifold has to consist of $n/2$ pairs of individual sliding surfaces, in another words, this design for the manifold can be regarded as a work for yielding manifolds of the $n/2$ sub-systems.\par
+Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension can be excluded by using conventional terminal sliding mode control, which results in that the remained $n-1$-link manipulator can be controlled by the proposed DSM scheme.
+\end{myrem}
+\begin{myrem}
+The singularity of the DSM scheme for the robot manipulator can be eliminated by using the technique introduced in \ref{theorem:3}.
+\end{myrem}
 \section{Acknowledgment}

### 2016-05-14 paper3_manuscript.tex
20160512

@@
 \begin{myrem}
-The singularity of the DSM scheme for the robot manipulator can be eliminated by using the technique introduced in \ref{theorem:3}.
+The singularity of the DSM scheme for the robot manipulator can be eliminated by using the technique introduced in Theorem \ref{theorem:3}.
 \end{myrem}
+\begin{myrem}
+One can use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the dual sliding mode control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically.
+\end{myrem}
+\section{Simulation studies}
+In this section, two studies will be presented, namely, a verification on the effectiveness of the proposed DSM and MDSM schemes and an application to a manipulator stabilization evaluating the performance of the control schemes.
+\subsection{Effectiveness study}
+For verifying the effectiveness of the DSM control scheme, consider the following four-order nonlinear system with the disturbance:
+\begin{align}
+\dot x_1 &= x_2\\
+\dot x_2 &= x_1^3+0.1\sin(20t)+u_1\\
+\dot x_3 &= x_4\\
+\dot x_4 &= 0.3\sin(3t)+0.5e^{-3t}+u_2,
+\end{align}
+\subsection{Performance of the robot manipulator}
 \section{Acknowledgment}

### 2016-05-14 paper3_manuscript.tex
20160514

@@
 \subsection{Effectiveness study}
-For verifying the effectiveness of the DSM control scheme, consider the following four-order nonlinear system with the disturbance:
+For verifying the effectiveness of the proposed control scheme, consider the following four-order nonlinear system with the disturbance:
 \begin{align}
+\begin{split}
 \dot x_1 &= x_2\\
@@
 \dot x_3 &= x_4\\
-\dot x_4 &= 0.3\sin(3t)+0.5e^{-3t}+u_2,
+\dot x_4 &= 0.3\sin(3t)+0.5e^{-3t}+u_2,\label{eq:simulation four order system}
+\end{split}
 \end{align}
+and one can produce a DSM control scheme conveniently.
+It is obvious that the disturbance in the system~(\ref{eq:simulation four order system}) behaves bounded, which is said to be the following uncertainty terms:
+\begin{align*}
+\Vert g_1(x,t)\Vert &= \Vert 0.1\sin(20t)\Vert\le 0.1\\
+\Vert g_2(x,t)\Vert &= \Vert 0.3\sin(3t)+0.5e^{-3t}\Vert\le 0.8,
+\end{align*}
+and hence, based on the analysis in Theorem~\ref{theorem:1}, $\eta_1>0.1$ and $\eta_2>0.8$ can be determined accordingly to guarantee the reaching condition of the desired sliding manifold.
+Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation four order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.
 \subsection{Performance of the robot manipulator}
+In order to evaluate the performance of the proposed control scheme, a simulation about the $2$-link robot manipulator is presented in the following.
+The dynamics of this manipulator can be explained by the dynamic equations in following forms:
+\begin{align}
+\begin{bmatrix}
+m_{12}(q_2) &m_{12}(q_2)\\
+m_{21}(q_2) &m_{22}
+\end{bmatrix}
+\begin{pmatrix}
+\ddot q_1\\
+\ddot q_2
+\end{pmatrix}
++
+\begin{bmatrix}
+-c(q_2)\dot q_1^2-2c(q_2)\dot q_1\dot q_2\\
+c(q_2)\dot q_2^2
+\end{bmatrix}+
+\begin{bmatrix}
+\xi_1(q_1,q_2) g\\
+\xi_2(q_1,q_2) g
+\end{bmatrix}=
+\begin{pmatrix}
+\tau_1\\
+\tau_2
+\end{pmatrix},
+\end{align}
+where
+\begin{align*}
+&m_{11}(q_2)=(m_1+m_2)r_1^2+m_2r_2^2+2m_2r_1r_2\cos(q_2)+J_1,\\
+&m_{12}(q_2)=m_2r_2^2+m_2r_1r_2\cos(q_2),\\
+&m_{21}(q_2)=m_{12}(q_2),\\
+&m_{22}=m_2r_2^2+J_2,\\
+&c(q_2)=m_2r_1r_2\sin(q_2),\\
+&\xi_1(q_1,q_2) =((m_1+m_2)r_1\cos(q_2)+m_2r_2\cos(q_1+q_2)),\\
+&\xi_2(q_1,q_2) = m_2r_2\cos(q_1+q_2).
+\end{align*}
 \section{Acknowledgment}

### 2016-05-15 paper3_manuscript.tex
20160514
20160515

--- 2016-05-14 paper3_manuscript.tex
@@
 One can use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the dual sliding mode control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically.
+For handling the chattering, the $sign()$ can be replaced with $sat(x,\delta)$, and the bounded value $\delta$ is determined according to actual needs.
 \end{myrem}
@@
 \dot x_3 &= x_4\\
-\dot x_4 &= 0.3\sin(3t)+0.5e^{-3t}+u_2,
+\dot x_4 &= 0.3\sin(3t)+0.5e^{-3t}+u_2,\label{eq:simulation four order system}
+\end{split}
 \end{align}
+and one can produce a MDSM control scheme conveniently.
+It is obvious that the disturbance in the system~(\ref{eq:simulation four order system}) behaves bounded, which is said to be the following uncertainty terms:
+\begin{align*}
+\Vert g_1(x,t)\Vert &= \Vert 0.1\sin(20t)\Vert\le 0.1\\
+\Vert g_2(x,t)\Vert &= \Vert 0.3\sin(3t)+0.5e^{-3t}\Vert\le 0.8,
+\end{align*}
+and hence, based on the analysis in Theorem~\ref{theorem:1}, $\eta_1>0.1$ and $\eta_2>0.8$ can be determined accordingly to guarantee the reaching condition of the desired sliding manifold.
+Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation four order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
+The system is supposed to be conducted to the desired state $\bm x_d=(0,0,0,0)$ from a prescript state $\bm x_0=(1.2,1.2,1.2,1.2)$.
+Admittedly, this prescript condition leads to a lager initial approaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding manifold, therefore a large approaching speed $k_i$ is required correspondingly.
+The control parameters are chosen as: $\alpha = 0.6$, $\lambda = 0.5$, $\gamma = 3$ and $\eta = 20$.
+Besides the large approaching speed selected, $\gamma$ accelerates the sliding phase indirectly.
+Therefore the design of the MDSM controller for the system~(\ref{eq:simulation four order system}) is finished, and the corresponding simulation results are illustrated in Figure~\ref{Figure:2} and Figure~\ref{Figure:3}.\par
+From Figure~\ref{Figure:2}, it's apparent that the states converge to their desired states.
+Figure~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely related to $\eta$, for the purpose of avoiding the largely chattering caused by $\eta$, the saturation function $sat()$ is applied to take place of $sign()$ to absorb it.
+Also, although the states have be adjusted to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range.
+The nature of the situation mention above is the input compensating the error caused by the distance.\par
+At this point, some effectiveness of the MDSM control scheme proposed above has been verified, and in the next section, we will apply it to stabilize the behavior of a $2$-link robot manipulator directly.
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth]{paper3_fig2.eps}
+\caption{1}
+\label{Figure:2}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth]{paper3_fig3.eps}
+\caption{2}
+\label{Figure:3}
+\end{figure}
 \subsection{Performance of the robot manipulator}
+In order to evaluate the performance of the proposed control scheme, a simulation about the $2$-link robot manipulator is presented in the following context.
+Figure~\ref{Figure:1} is the $2$-link manipulator schematic, the dynamics of which can be explained by the dynamic equations in following forms:
+
+\begin{figure}
+\centering
+\includegraphics[width=0.4\textwidth]{paper3_fig1.eps}
+\caption{2}
+\label{Figure:1}
+\end{figure}
+
+\begin{align}
+\begin{bmatrix}
+m_{12}(q_2) &m_{12}(q_2)\\
+m_{21}(q_2) &m_{22}
+\end{bmatrix}
+\begin{pmatrix}
+\ddot q_1\\
+\ddot q_2
+\end{pmatrix}
++
+\begin{bmatrix}
+-c(q_2)\dot q_1^2-2c(q_2)\dot q_1\dot q_2\\
+c(q_2)\dot q_2^2
+\end{bmatrix}+
+\begin{bmatrix}
+\xi_1(q_1,q_2) g\\
+\xi_2(q_1,q_2) g
+\end{bmatrix}=
+\begin{pmatrix}
+\tau_1\\
+\tau_2
+\end{pmatrix},
+\end{align}
+where
+\begin{align*}
+&m_{11}(q_2)=(m_1+m_2)r_1^2+m_2r_2^2+2m_2r_1r_2\cos(q_2)+J_1,\\
+&m_{12}(q_2)=m_2r_2^2+m_2r_1r_2\cos(q_2),\\
+&m_{21}(q_2)=m_{12}(q_2),\\
+&m_{22}=m_2r_2^2+J_2,\\
+&c(q_2)=m_2r_1r_2\sin(q_2),\\
+&\xi_1(q_1,q_2) =(m_1+m_2)r_1\cos(q_2)+m_2r_2\cos(q_1+q_2),\\
+&\xi_2(q_1,q_2) = m_2r_2\cos(q_1+q_2).
+\end{align*}\par
+The values of the parameters are listed here, $r_1=1m$, $r_2=0.8m$, $J_1=5 kgm$, $J_2=5kgm$, $m_1=0.5kg$, $m_2=1.5kg$.
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth]{paper3_fig4.eps}
+\caption{2}
+\label{Figure:4}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth]{paper3_fig5.eps}
+\caption{2}
+\label{Figure:5}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth]{paper3_fig6.eps}
+\caption{2}
+\label{Figure:6}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth]{paper3_fig7.eps}
+\caption{2}
+\label{Figure:7}
+\end{figure}
 \section{Acknowledgment}

### 2016-05-15 paper3_manuscript.tex
20160515

@@
 Particularly, the following assumption is exhibited to explain the bounded characteristics of the robot dynamics \cite{feng2002non}:
-\begin{align*}
-&\Vert M(\bm q)\Vert< \theta_0\\
-&\Vert C(\bm q,\dot {\bm q})\Vert< \phi_0+\phi_1\Vert\bm q\Vert+\phi_2\Vert\dot{\bm q}\Vert^2\\
-&\Vert g(\bm q)\Vert< \psi_0+\psi_1\Vert\bm q\Vert\\
-&\Vert \bm {\rho}(t)\Vert< \mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2,
-\end{align*}
+\begin{align}
+&\Vert M(\bm q)\Vert< \theta_0\notag\\
+&\Vert C(\bm q,\dot {\bm q})\Vert< \phi_0+\phi_1\Vert\bm q\Vert+\phi_2\Vert\dot{\bm q}\Vert^2\notag\\
+&\Vert g(\bm q)\Vert< \psi_0+\psi_1\Vert\bm q\notag\Vert
+&\Vert \bm {\rho}(t)\Vert< \mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2,\label{eq:manipulator uncertainty}
+\end{align}
 where $\bm {\rho}(t) = -\Delta M(\bm q)-\Delta C(\bm q,\dot {\bm q})-\Delta g(\bm q)$, and $\theta_0$, $\phi_0$, $\phi_1$, $\phi_2$, $\psi_0$, $\psi_1$, $\mu_0$, $\mu_1$, $\mu_2$ are positive constants.\par
@@
 The values of the parameters are listed here, $r_1=1m$, $r_2=0.8m$, $J_1=5 kgm$, $J_2=5kgm$, $m_1=0.5kg$, $m_2=1.5kg$.
+In this model, the uncertainty is brought in by estimated terms, namely, $\bar m_1=0.4$ and $\bar m_2=1.2$ which are all not the actuate value obviously.
+In addition, owing to that it sits on many terms in the dynamic equations, it's a severe challenge to guarantee the performance.
+Accordingly, the uncertainty parameters in Eq.~(\ref{eq:manipulator uncertainty}) are assumed to be $\mu_0=10$, $\mu_1=3$, $\mu_2=3$.\par
+This section will give a set of simulation to examine the performance of the MDSM control in tracking the certain angle condition.
+The behavior of the manipulator should fulfill the initial and desired condition, namely, $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$.
+In order to ensure the stability and a fast convergent speed, the control parameters are chosen conservatively to make the manipulator track the desired attitude in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $\eta = 100$.
+The terminal sliding mode control (TSM) scheme, as a comparison, is also implemented to regulate the behavior of the manipulator, the main control parameters of which are selected as $\alpha = 0.6$, $\gamma = 5$ and $\eta = 150$ to get a fairly good control performance.\par
+The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}.
 \begin{figure}

### 2016-05-16 paper3_manuscript.tex
20160516

@@
 \section{Introduction}
-\section{Dual sliding mode control}
-Consider a four-order nominal nonlinear system:
+(...background of sliding mode control...)\par
+(...sliding mode control develop...)\par
+Recent years, the sliding mode control has become a popular solution to the issue about various control and signal process missions \cite{zhao2015nonlinear,zhang2015attitude}.
+Meza-S{\'a}nchez et al.
+applied the second sliding mode controller to a 3-DOF helicopter prototype, and verified the effectiveness via the experimental test bed \cite{meza2015output}.
+Zheng et al.
+implemented sliding mode control to eliminate the effect of the input quantization generated between the coder and the decoder \cite{zheng2016sliding}.
+Guzman et al.
+investigated the application of a sliding mode control in a power factor rectifier with constant switching frequency \cite{guzman2016sliding}.
+Said et al.
+designed a robust adaptive sliding mode method for a boost converter to guarantee the asymptotically stability \cite{oucheriah2013pwm}.
+high order sliding mode control \cite{castillo2015higher,palosz2015laser}, super-twisting sliding mode\cite{zhao2015finite,liu2015second}
+(...the terminal sliding mode develop...)\par
+Normal linear hyperplane-based sliding mode control takes two steps to solve a problem about the stability, namely, conducting the system states onto the prescript sliding manifold and driving these states to the origin along the manifold.
+The first step is said to be the approaching phase which usually requires the states asymptotically or exponentially converge to the desired manifold, and the second step is the sliding phase which is related to the designed manifold closely.
+For achieving a fast convergence, the terminal sliding mode (TSM) control is developed based on the finite time control \cite{haimo1986finite,bhat1997finite,mu2016switching}, and comparing with the sliding mode control design mentioned above, the most significant contributions of the terminal sliding mode is introducing the finite time convergence to the sliding phase.
+Owing to the fast convergence, the terminal sliding mode control has been utilized to achieve the high precise control, i.e., in \cite{li2015robust}, an adaptive TSM scheme controlled a $2$-link robotic manipulator to track the variable signal.
+\par
+In this paper, a dual sliding mode (DSM) controller is proposed for a class of two-order nonlinear systems with disturbances and uncertainties.
+A novel DSM manifold is exploited to fulfill the finite time convergence, and the approaching and sliding time are both able to be calculated directly.
+A modified DSM (MDSM) control scheme is presented to stabilize the motion of the $n$-link robotic manipulators.
+The remained paper is organized as follows: Section~\ref{sec:2} introduces a DSM scheme for a class of two-order system, and the finite time convergence of the approaching and sliding is verified.
+In addition, we add performance parameters for improving the DSM scheme to obtain the MDSM scheme, and the newly presented method has a better performance in theoretical analysis.
+In Section~\ref{sec:3}, the MDSM is applied to the motion regulation of the $n$-link robotic  manipulator, and the stability analysis is also carried out.
+Section~\ref{sec:4} exhibited the simulation results, and finally the conclusion is assigned in Section~\ref{sec:5}.
+\section{Dual sliding mode control}\label{sec:2}
+Consider a two-order nominal nonlinear system:
 \begin{align}
@@
 \dot x_3(t) &= x_4(t)\\
-\dot x_5(t) &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)u_2(t),\label{eq:four order system}
+\dot x_4(t) &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)u_2(t),\label{eq:two order system}
 \end{split}
@@
 \end{mylem}
-For stabilization of the four-order system shown as~Eq. (\ref{eq:four order system}), dual sliding mode control inputs can be given according the following theorem.
+For stabilization of the two-order system shown as~Eq. (\ref{eq:two order system}), dual sliding mode control inputs can be given according the following theorem.
 \begin{mythm}\label{theorem:1}Dual Sliding Mode (DSM) Control Design.
-The four-order system (\ref{eq:four order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq.
+The two-order system (\ref{eq:two order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq.
 (\ref{eq:dual sliding manifold}) in finite time.
@@
 \end{align*}
-Hence, the system (\ref{eq:four order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergent time can be calculated according to the finite time convergence theory.\par
-Once the system (\ref{eq:four order system}) reaches the desired manifold~(\ref{eq:dual sliding manifold}), the whole system is handled by the reduced system:
+Hence, the system (\ref{eq:two order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergent time can be calculated according to the finite time convergence theory.\par
+Once the system (\ref{eq:two order system}) reaches the desired manifold~(\ref{eq:dual sliding manifold}), the whole system is handled by the reduced system:
 \begin{align*}
@@
 \end{proof}
-On the basis of Theorem \ref{theorem:1}, we can develop the parameters in the manifold to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:four order system}), and furthermore this method makes the design of the manifold more flexible.
-Considering the system~(\ref{eq:four order system}) with the manifold manifold $\bm s = [s_1,s_2]^T$, the details of which can be described by following expressions:
+On the basis of Theorem \ref{theorem:1}, we can develop the parameters in the manifold to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:two order system}), and furthermore this method makes the design of the manifold more flexible.
+Considering the system~(\ref{eq:two order system}) with the manifold manifold $\bm s = [s_1,s_2]^T$, the details of which can be described by following expressions:
 \begin{align}
@@
 \begin{mythm}\label{theorem:2}Modified Dual Sliding Mode (MDSM) Control Design.
-The four-order system (\ref{eq:four order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq.
+The two-order system (\ref{eq:two order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq.
 (\ref{eq:modified dual sliding manifold}) in finite time.
@@
 \begin{mylem}\label{lemma:3}
-Considering the four-order system (\ref{eq:four order system}), the terminal sliding mode manifold can be designed as:
+Considering the two-order system (\ref{eq:two order system}), the terminal sliding mode manifold can be designed as:
 \begin{align*}
@@
 and $u_s>0$ can be determined according to the requirements of the performance.\par
-Adopting the control scheme mentioned above, the system~(\ref{eq:four order system}) will converge to zero in finite time without any singularity occurring during the regulation process.
+Adopting the control scheme mentioned above, the system~(\ref{eq:two order system}) will converge to zero in finite time without any singularity occurring during the regulation process.
 \end{mylem}
 \begin{mythm}\label{theorem:3}
-Consider a four-order system (\ref{eq:four order system}), and for eliminating the singularity in inputs of the MDSM scheme, select a new inputs to complete the nonsingular MDSM scheme.
+Consider a two-order system (\ref{eq:two order system}), and for eliminating the singularity in inputs of the MDSM scheme, select a new inputs to complete the nonsingular MDSM scheme.
 Introducing the saturation terms into the original inputs yields:
@@
 \end{align}
-one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:four order system}), providing the finite time convergence by using sliding mode technique.
+one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:two order system}), providing the finite time convergence by using sliding mode technique.
 \end{mythm}
@@
 \end{proof}
-\section{Dual sliding mode control for rigid manipulators}
-In this section, a dual sliding mode control is proposed for the rigid $2$-link robot manipulator
+\section{Dual sliding mode control for rigid manipulators}\label{sec:3}
+In this section, a dual sliding mode control is proposed for the rigid $2$-link robotic manipulator
 \begin{align}
@@
 where $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$ and $g_0(\bm q)$ are the estimated terms affected by the the uncertainties including $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$, $g_0(\bm q)$, and the disturbance $\bm{d}(t)$.
-Particularly, the following assumption is exhibited to explain the bounded characteristics of the robot dynamics \cite{feng2002non}:
+Particularly, the following assumption is exhibited to explain the bounded characteristics of the robotic dynamics \cite{feng2002non}:
 \begin{align}
@@
 &\Vert C(\bm q,\dot {\bm q})\Vert< \phi_0+\phi_1\Vert\bm q\Vert+\phi_2\Vert\dot{\bm q}\Vert^2\notag\\
-&\Vert g(\bm q)\Vert< \psi_0+\psi_1\Vert\bm q\notag\Vert
+&\Vert g(\bm q)\Vert< \psi_0+\psi_1\Vert\bm q\notag\Vert\\
 &\Vert \bm {\rho}(t)\Vert< \mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2,\label{eq:manipulator uncertainty}
@@
 \end{align*}
-On the basis of the above results, one can design the dual sliding mode scheme for $2$-link robot manipulator by utilizing the following theorem.
+On the basis of the above results, one can design the dual sliding mode scheme for $2$-link robotic manipulator by utilizing the following theorem.
 \begin{mythm}\label{theorem:4}
@@
 \bm u_1 &= M_0(\bm q)\ddot {\bm q}_d+C_0(\bm q,\dot {\bm q})+g_0(\bm q)\\
-\bm u_2 &= -\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2).
+\bm u_2 &= -k\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}.
 \end{split}
 \end{align}
-in which it is assumed that the parameters $\mu_0$, $\mu_1$ and $\mu_2$ are known.
+in which $k>\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2$, and it is assumed that the parameters $\mu_0$, $\mu_1$ and $\mu_2$ are known.
 \end{mythm}
@@
 \begin{myrem}
-At this point, the dual sliding mode control scheme for $2$-link robot manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator.
-Consider a $n$-link robot manipulator in where $n$ is an even number, and the desired sliding manifold can be designed as
+At this point, the dual sliding mode control scheme for $2$-link robotic manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator.
+Consider a $n$-link robotic manipulator in where $n$ is an even number, and the desired sliding manifold can be designed as
 \begin{align}
@@
 \begin{myrem}
-The singularity of the DSM scheme for the robot manipulator can be eliminated by using the technique introduced in Theorem \ref{theorem:3}.
+The singularity of the DSM scheme for the robotic manipulator can be eliminated by using the technique introduced in Theorem \ref{theorem:3}.
 \end{myrem}
@@
 \end{myrem}
-\section{Simulation studies}
+\section{Simulation studies}\label{sec:4}
 In this section, two studies will be presented, namely, a verification on the effectiveness of the proposed DSM and MDSM schemes and an application to a manipulator stabilization evaluating the performance of the control schemes.
 \subsection{Effectiveness study}
-For verifying the effectiveness of the proposed control scheme, consider the following four-order nonlinear system with the disturbance:
+For verifying the effectiveness of the proposed control scheme, consider the following two-order nonlinear system with the disturbance:
 \begin{align}
@@
 \dot x_3 &= x_4\\
-\dot x_4 &= 0.3\sin(3t)+0.5e^{-3t}+u_2,\label{eq:simulation four order system}
+\dot x_4 &= 0.3\sin(3t)+0.5e^{-3t}+u_2,\label{eq:simulation two order system}
 \end{split}
@@
 and one can produce a MDSM control scheme conveniently.
-It is obvious that the disturbance in the system~(\ref{eq:simulation four order system}) behaves bounded, which is said to be the following uncertainty terms:
+It is obvious that the disturbance in the system~(\ref{eq:simulation two order system}) behaves bounded, which is said to be the following uncertainty terms:
 \begin{align*}
@@
 \end{align*}
-and hence, based on the analysis in Theorem~\ref{theorem:1}, $\eta_1>0.1$ and $\eta_2>0.8$ can be determined accordingly to guarantee the reaching condition of the desired sliding manifold.
-Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation four order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
+and hence, based on the analysis in Theorem~\ref{theorem:1}, $l_1>0.1$ and $l_2>0.8$ can be determined accordingly to guarantee the reaching condition of the desired sliding manifold.
+Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation two order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
 The system is supposed to be conducted to the desired state $\bm x_d=(0,0,0,0)$ from a prescript state $\bm x_0=(1.2,1.2,1.2,1.2)$.
 Admittedly, this prescript condition leads to a lager initial approaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding manifold, therefore a large approaching speed $k_i$ is required correspondingly.
-The control parameters are chosen as: $\alpha = 0.6$, $\lambda = 0.5$, $\gamma = 3$ and $\eta = 20$.
+The control parameters are chosen as: $\alpha = 0.6$, $\lambda = 0.5$, $\gamma = 3$ and $k = 20$.
 Besides the large approaching speed selected, $\gamma$ accelerates the sliding phase indirectly.
-Therefore the design of the MDSM controller for the system~(\ref{eq:simulation four order system}) is finished, and the corresponding simulation results are illustrated in Figure~\ref{Figure:2} and Figure~\ref{Figure:3}.\par
+Therefore the design of the MDSM controller for the system~(\ref{eq:simulation two order system}) is finished, and the corresponding simulation results are illustrated in Figure~\ref{Figure:2} and Figure~\ref{Figure:3}.\par
 From Figure~\ref{Figure:2}, it's apparent that the states converge to their desired states.
@@
 The nature of the situation mention above is the input compensating the error caused by the distance.\par
-At this point, some effectiveness of the MDSM control scheme proposed above has been verified, and in the next section, we will apply it to stabilize the behavior of a $2$-link robot manipulator directly.
+At this point, some effectiveness of the MDSM control scheme proposed above has been verified, and in the next section, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.
 \begin{figure}
@@
 \end{figure}
-\subsection{Performance of the robot manipulator}
-In order to evaluate the performance of the proposed control scheme, a simulation about the $2$-link robot manipulator is presented in the following context.
+\subsection{Performance of the robotic manipulator}
+In order to evaluate the performance of the proposed control scheme, a simulation about the $2$-link robotic manipulator is presented in the following context.
 Figure~\ref{Figure:1} is the $2$-link manipulator schematic, the dynamics of which can be explained by the dynamic equations in following forms:
@@
 The behavior of the manipulator should fulfill the initial and desired condition, namely, $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$.
-In order to ensure the stability and a fast convergent speed, the control parameters are chosen conservatively to make the manipulator track the desired attitude in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $\eta = 100$.
-The terminal sliding mode control (TSM) scheme, as a comparison, is also implemented to regulate the behavior of the manipulator, the main control parameters of which are selected as $\alpha = 0.6$, $\gamma = 5$ and $\eta = 150$ to get a fairly good control performance.\par
+In order to ensure the stability and a fast convergent speed, the control parameters are chosen conservatively to make the manipulator track the desired attitude in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $k = 100$.
+The terminal sliding mode control (TSM) scheme, as a comparison, is also implemented to regulate the behavior of the manipulator:
+\begin{align}
+\begin{split}
+\bm s &= \dot{\bm \varepsilon}+C_\gamma\lceil\bm{sgn}^\alpha(\bm \varepsilon)\rfloor\\
+\bm\tau &= \bm u_0+\bm u_1 +\bm u_2\\
+\bm u_0 &= -M_0(\bm q)C_r\lceil\alpha\vert\bm\varepsilon\vert^{\alpha-1}\dot{\bm \varepsilon}\rfloor\\
+\bm u_1 &= M_0(\bm q)\ddot {\bm q}_d+C_0(\bm q,\dot {\bm q})+g_0(\bm q)\\
+\bm u_2 &= -k\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}.
+\end{split}
+\end{align}
+where the main control parameters of which are selected as $\alpha = 0.6$, $\gamma = 5$ and $k = 150$ to get a fairly good control performance.\par
 The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}.
+Comparatively speaking, $q_1$ reaches the desired state at about $3s$ with the MDSM scheme, the reaching time of which is approximating $0.8s$ less than of the TSM scheme, and $q_2$ performs similar behaviors with a reasonable variable range of the angular rates.
+One can concentrate on the mission time of the entire motion, and inductively the time is decided by the manipulator finishing the final motion, i.e., for the manipulator controlled by utilizing the MDSM scheme, one can obtain the mission time $3s$ approximately, comparing with $3.25s$ for the TSM control.
+More notably, the control parameters of the TSM scheme have been optimally selected, whereas if using the parameters for the MDSM scheme, one can only get a fairy poor performance in the regulation, which leads to meaningless comparison.
+Therefore these results show that the MDSM control scheme can achieve the regulation of the manipulator effectively.
 \begin{figure}
@@
 \end{figure}
-
+The more general case, the robotic manipulator is usually required to track variable signal, is discussed in this section.
+Particularly, one can continue to use the parameters of the controller mentioned above, and the mission condition is changed as follows:
+\begin{align*}
+&(\bm q_0^T, \dot{\bm q}_0^T)= (1.5,1.5,0,0)\\
+&{\bm q}_d^T=(1.25-(1/5)e^{-t}+(1/20)e^{-4t},1.25+(9/40)e^{-t}-(1/4)e^{-2t})
+\end{align*}\par
+The simulation results are demonstrated in Figure~\ref{Figure:6} and Figure~\ref{Figure:7}, which plot the curves of states of the system~(\ref{eq:simulation two order system}) regulated by adopting the MDSM scheme.
+The control system completes the tracking mission at about $3.2s$ from a prescript initial condition, which performs a fairly small overshoot in the angle regulation.
 \begin{figure}
@@
 \end{figure}
+\section{Conclusion}\label{sec:5}
+A dual sliding mode control for n-link robotic manipulator has been presented.
+The method integrates two individual subsystem as a unity, then builds the manifold and input for it to complete the controller design.
+The control scheme can guarantee the reaching condition of the desired sliding manifold, meanwhile the system states can converge to the origin along the desired manifold.
+Also, the entire convergent time can be calculated accordingly.
+Developing the basic dual sliding mode yields the modified dual sliding mode control, providing a solution to eliminating chattering, avoiding singularity and fast convergence.
+For dealing with the under actuated characteristics which may appear in the system, the hierachical sliding mode technique will be considered to introduce into the control scheme, however, the control parameters selection is still a challenge.
 \section{Acknowledgment}

### 2016-05-17 paper3_manuscript.tex
20160517

@@
 \begin{frontmatter}
-\title{Dual terminal sliding mode control}
+\title{A New Dual Terminal Sliding Mode Control Design For Rigid Robotic Manipulator}
 \author{Zhiqiang Ma}
@@
 \begin{abstract}
+This paper proposes a novel dual terminal sliding mode control for rigid robotic manipulator.
+A new terminal sliding mode manifold design technique is addressed to achieve finite time convergence of the sliding phase, and furthermore utilizing the involved dual variables combines the individual sliding mode surfaces to obtain a integral sliding mode dynamics, the convergent time of which is also integral for the entire system.
+The newly proposed method also has the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motion of the rigid robotic manipulator.
+Simulation results validate the theoretical analysis about the proposed method.
 \end{abstract}
 \begin{keyword}
+Finite time control; Robotic manipulator control; Terminal sliding mode; Sliding mode manifold design; Stability analysis
 \end{keyword}
@@
 \section{Introduction}
-(...background of sliding mode control...)\par
-(...sliding mode control develop...)\par
-Recent years, the sliding mode control has become a popular solution to the issue about various control and signal process missions \cite{zhao2015nonlinear,zhang2015attitude}.
+Variable structure systems (VSS) are best known due to its insensitivity to parameter variations and uncertainties~\cite{slotine1991applied}.
+Its widely utilization in practice case, such as DC and AC motors, process control, aircrafts, satellites, robots and so on, has validated robustness of VSS.
+As one of the most important branch of the VSS, the sliding mode control (SMC) has become a popular solution to the issue about various control and signal process missions in recent years~\cite{zhao2015nonlinear,zhang2015attitude}.
 Meza-S{\'a}nchez et al.
-applied the second sliding mode controller to a 3-DOF helicopter prototype, and verified the effectiveness via the experimental test bed \cite{meza2015output}.
+applied the second order sliding mode controller to a 3-DOF helicopter prototype, and verified the effectiveness via the experimental test bed~\cite{meza2015output}.
 Zheng et al.
-implemented sliding mode control to eliminate the effect of the input quantization generated between the coder and the decoder \cite{zheng2016sliding}.
+implemented the SMC to eliminate the effect of the input quantization generated between the coder and the decoder~\cite{zheng2016sliding}.
 Guzman et al.
-investigated the application of a sliding mode control in a power factor rectifier with constant switching frequency \cite{guzman2016sliding}.
+investigated the application of a SMC in a power factor rectifier with constant switching frequency~\cite{guzman2016sliding}.
 Said et al.
-designed a robust adaptive sliding mode method for a boost converter to guarantee the asymptotically stability \cite{oucheriah2013pwm}.
-high order sliding mode control \cite{castillo2015higher,palosz2015laser}, super-twisting sliding mode\cite{zhao2015finite,liu2015second}
-(...the terminal sliding mode develop...)\par
-Normal linear hyperplane-based sliding mode control takes two steps to solve a problem about the stability, namely, conducting the system states onto the prescript sliding manifold and driving these states to the origin along the manifold.
-The first step is said to be the approaching phase which usually requires the states asymptotically or exponentially converge to the desired manifold, and the second step is the sliding phase which is related to the designed manifold closely.
-For achieving a fast convergence, the terminal sliding mode (TSM) control is developed based on the finite time control \cite{haimo1986finite,bhat1997finite,mu2016switching}, and comparing with the sliding mode control design mentioned above, the most significant contributions of the terminal sliding mode is introducing the finite time convergence to the sliding phase.
-Owing to the fast convergence, the terminal sliding mode control has been utilized to achieve the high precise control, i.e., in \cite{li2015robust}, an adaptive TSM scheme controlled a $2$-link robotic manipulator to track the variable signal.
+designed a robust adaptive sliding mode method to guarantee the asymptotically stability of a boost converter~\cite{oucheriah2013pwm}.
+Roughly speaking, the SMC scheme is competent for normal scientific mission, due to its insensitivity of parameters and uncertainties in system, however, there still exist some obstacles, such as noncontinuous switching input in high frequency and desired convergent speed design~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some practical engineering cases~\cite{fridman2011sliding}.
 \par
-In this paper, a dual sliding mode (DSM) controller is proposed for a class of two-order nonlinear systems with disturbances and uncertainties.
-A novel DSM manifold is exploited to fulfill the finite time convergence, and the approaching and sliding time are both able to be calculated directly.
-A modified DSM (MDSM) control scheme is presented to stabilize the motion of the $n$-link robotic manipulators.
-The remained paper is organized as follows: Section~\ref{sec:2} introduces a DSM scheme for a class of two-order system, and the finite time convergence of the approaching and sliding is verified.
-In addition, we add performance parameters for improving the DSM scheme to obtain the MDSM scheme, and the newly presented method has a better performance in theoretical analysis.
-In Section~\ref{sec:3}, the MDSM is applied to the motion regulation of the $n$-link robotic  manipulator, and the stability analysis is also carried out.
+For alleviating the side effects, many researchers addressed remarkable approaches to improve the performance of the SMC scheme in last decade~\cite{zong2013quasi,santiesteban2013time,mu2015continuous,evangelista2013lyapunov,gonzalez2014chattering,dadras2012fractional,zhao2013output}.
+Among these methods, the high order sliding mode control and super-twisting sliding mode control efforts to generate the continuous inputs~\cite{castillo2015higher,palosz2015laser,edwards2016adaptive,zhao2015finite,liu2015second}, which eliminate the chattering by hiding the switching in high-order terms or absorbing the switching via some techniques.
+\par
+Besides the issue on repressing the chattering, the fast convergence of the SMC scheme is also a hot subject.
+Normal linear sliding mode control takes two steps to solve a problem about the stability, namely, conducting the system states onto the prescript sliding manifold and driving these states to the origin along the manifold, and an accelerating operation usually occurs in this two phases.
+The first step is said to be the approaching phase which usually requires the states converge to the desired manifold in finite time, and selecting suitable Lyapunov function and control parameters may accelerate this process; the second step is the sliding phase which is related to the designed manifold closely, and normal manifold design techniques can just guarantee the asymptotically convergence.
+For achieving a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and comparing with the sliding mode control design mentioned above, the most significant contributions of the terminal sliding mode is introducing the finite time convergence to the sliding phase to complete the global finite time convergence.
+Owing to the global finite time convergence, the terminal sliding mode control has been utilized to achieve the high precise control, i.e., in~\cite{li2015robust}, an adaptive TSM scheme controlled a $2$-link robotic manipulator to track the variable signal.
+Feng et al.
+presented a global terminal sliding mode algorithm for manipulating the rigid robot, and produced the control design by using Lagrangian dynamic expression~\cite{feng2002non}.
+In~\cite{kamal2016continuous}, Kamal addressed a continuous homogeneous sliding mode algorithm for a perturbed second-order plant, and the algorithm could be regarded as a combination of terminal and super-twisting sliding-mode, providing a convergence control in finite time.
+\par
+According to the achievements mentioned above, one can find that the conventional terminal sliding mode manifold design techniques are similar, since they are all based on the single variable finite time control, in another words, the sliding mode dynamics only involves the individual variable and its derivative essentially~\cite{mu2016switching}.
+This nature makes the TSM scheme become an individual control subsystem, which leads to the complicity of global convergent time in some extent.
+In this paper, an integral sliding mode manifold technique is proposed for finite time stability of the two-order system, and the novel manifold involves two variables to guarantee the integral finite time convergence, and the convergent time can be obtained easily.
+Also, the nonsingularity and chattering suppression are available in the scheme.
+\par
+In this paper, a dual sliding mode (DTSM) controller is proposed for a class of two-order nonlinear systems with disturbances and uncertainties.
+A novel DTSM manifold is exploited to fulfill the finite time convergence, and the approaching and sliding time are both able to be calculated directly.
+A modified DTSM (MDTSM) control scheme is presented to stabilize the motion of the $n$-link robotic manipulators.
+The remained paper is organized as follows: Section~\ref{sec:2} introduces a DTSM scheme for a class of two-order system, and the finite time convergence of the approaching and sliding is verified.
+In addition, we add performance parameters for improving the DTSM scheme to obtain the MDTSM scheme, and the newly presented method has a better performance in theoretical analysis.
+In Section~\ref{sec:3}, the MDTSM is applied to the motion regulation of the $n$-link robotic  manipulator, and the stability analysis is also carried out.
 Section~\ref{sec:4} exhibited the simulation results, and finally the conclusion is assigned in Section~\ref{sec:5}.
-\section{Dual sliding mode control}\label{sec:2}
+\section{Dual terminal sliding mode control}\label{sec:2}
 Consider a two-order nominal nonlinear system:
@@
 \end{align}
-where $bm x = [x_1,x_2,x_3,x_4]^T$ is the system vector state; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$; $u_i(t)$, $i=1,2$ stands for the scalar input; $g_i(\bm x,t)$, $i=1,2$  is a defined as a bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0$, meaning the uncertainty and disturbance of the system.
-For the system mentioned above, we can establish a desired dual sliding manifold as:
+where $\bm x = [x_1,x_2,x_3,x_4]^T$ is the system vector state; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$; $u_i(t)$, $i=1,2$ stands for the scalar input; $g_i(\bm x,t)$, $i=1,2$  is a defined as a bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0$, meaning the uncertainty and disturbance of the system.
+For the system mentioned above, we can establish a desired dual terminal sliding manifold as:
 \begin{align}
@@
 For the sake of simplicity, the symbol $t$ is usually omitting in this paper, which does not cause any confusion, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding manifold $\bm s(t)$ is often abbreviated to $\bm s$.\par
-There exist two lemmas about the finite convergence theory, providing convergent forms which contribute to the verification of the finite convergence about the dual sliding mode control.
+There exist two lemmas about the finite convergence theory, providing convergent forms which contribute to the verification of the finite convergence about the DTSM control.
 \begin{mylem}
-As described in \cite{moulay2006finite}, it is assumed that the continuous function $V(t)$ is positive-define, satisfying the following condition:
+As described in~\cite{moulay2006finite}, it is assumed that the continuous function $V(t)$ is positive-define, satisfying the following condition:
 \begin{align}
@@
 \end{align}\par
-Selecting $V(t) = \frac{x_1^2+x_2^2}{2}$ obtains the finite convergent time as follows \cite{moulay2006finite}:
+Selecting $V(t) = \frac{x_1^2+x_2^2}{2}$ obtains the finite convergent time as follows~\cite{moulay2006finite}:
 %since $\vert x\vert-x^\alpha+\vert x\vert \ge 0,0<\alpha<1$
@@
 \end{mylem}
-For stabilization of the two-order system shown as~Eq. (\ref{eq:two order system}), dual sliding mode control inputs can be given according the following theorem.
-\begin{mythm}\label{theorem:1}Dual Sliding Mode (DSM) Control Design.
+For stabilization of the two-order system shown as~Eq. (\ref{eq:two order system}), DTSM control inputs can be given according the following theorem.
+\begin{mythm}\label{theorem:1}Dual Terminal Sliding Mode (DTSM) Control Design.
 The two-order system (\ref{eq:two order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq.
@@
 \end{align}
-where $\gamma$ is a positive constant and $\lambda\in R$ is a regulable parameter. Hence, the modified dual sliding mode control inputs are formed in the following theorem.
-\begin{mythm}\label{theorem:2}Modified Dual Sliding Mode (MDSM) Control Design.
+where $\gamma$ is a positive constant and $\lambda\in R$ is a regulable parameter. Hence, the modified dual terminal sliding mode control inputs are formed in the following theorem.
+\begin{mythm}\label{theorem:2}Modified Dual Terminal Sliding Mode Control Design.
 The two-order system (\ref{eq:two order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq.
@@
 \end{proof}
-After introducing the parameters $\lambda$ and $\gamma$ into the DSM scheme, the performances of the approaching and sliding phases become regulatable, meaning that these parameters can adjust the convergent time analytically.
+After introducing the parameters $\lambda$ and $\gamma$ into the DTSM scheme, the performances of the approaching and sliding phases become regulatable, meaning that these parameters can adjust the convergent time analytically.
 Although $\lambda$ does not appear in Eq.~(\ref{eq:total convergent time}), the establishment of $V(t_0)$ involves it when the state $\bm x(t_0)$ has been fixed.
@@
 \end{myrem}
-The finite convergence of the DSM and MDSM scheme has been verified clearly, but similar to the conventional terminal sliding mode control, there exists another obstacle in the design mentioned above, namely, the issue of the singularity in control inputs.
+The finite convergence of the DTSM and MDTSM scheme has been verified clearly, but similar to the conventional terminal sliding mode control, there exists another obstacle in the design mentioned above, namely, the issue of the singularity in control inputs.
 Essentially, the singularity occurs in Eq.~(\ref{eq:modified input}) when $x_1=0$ but $x_2\neq 0$ in $u_1$ (the phenomena happens to $u_2$ under the same condition).
-For coping with the singularity, a nonsingular MDSM scheme is presented after introducing an analytical technique into the MDSM scheme based on the following lemma \cite{feng2013nonsingular}.
+For coping with the singularity, a nonsingular MDTSM scheme is presented after introducing an analytical technique into the MDTSM scheme based on the following lemma~\cite{feng2013nonsingular}.
 \begin{mylem}\label{lemma:3}
@@
 \begin{mythm}\label{theorem:3}
-Consider a two-order system (\ref{eq:two order system}), and for eliminating the singularity in inputs of the MDSM scheme, select a new inputs to complete the nonsingular MDSM scheme.
+Consider a two-order system (\ref{eq:two order system}), and for eliminating the singularity in inputs of the MDTSM scheme, select a new inputs to complete the nonsingular MDTSM scheme.
 Introducing the saturation terms into the original inputs yields:
@@
 \begin{proof}
-The proof is similar to the graphical analysis mentioned in \cite{feng2013nonsingular}, and omitted here.
+The proof is similar to the graphical analysis mentioned in~\cite{feng2013nonsingular}, and omitted here.
 \end{proof}
-\section{Dual sliding mode control for rigid manipulators}\label{sec:3}
-In this section, a dual sliding mode control is proposed for the rigid $2$-link robotic manipulator
+\section{Dual terminal sliding mode control for rigid manipulators}\label{sec:3}
+In this section, a DTSM control is proposed for the rigid $2$-link robotic manipulator
 \begin{align}
@@
 where $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$ and $g_0(\bm q)$ are the estimated terms affected by the the uncertainties including $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$, $g_0(\bm q)$, and the disturbance $\bm{d}(t)$.
-Particularly, the following assumption is exhibited to explain the bounded characteristics of the robotic dynamics \cite{feng2002non}:
+Particularly, the following assumption is exhibited to explain the bounded characteristics of the robotic dynamics~\cite{feng2002non}:
 \begin{align}
@@
 \end{align*}
-On the basis of the above results, one can design the dual sliding mode scheme for $2$-link robotic manipulator by utilizing the following theorem.
+On the basis of the above results, one can design the DTSM scheme for $2$-link robotic manipulator by utilizing the following theorem.
 \begin{mythm}\label{theorem:4}
-For the rigid $2$-link manipulator~(\ref{eq:lagrangian system}), if the dual sliding mode manifold is selected as
+For the rigid $2$-link manipulator~(\ref{eq:lagrangian system}), if the dual terminal sliding mode manifold is selected as
 \begin{align}
@@
 &=\bm s^T(M_0^{-1}(\bm q)(\bm u_0+\bm u_2+\bm\rho(t))+C_r\lceil\alpha\vert\bm\varepsilon\vert^{\alpha-1}\dot{\bm \varepsilon}+3\bm \varepsilon^2\dot{\bm \varepsilon}\rfloor+C_\lambda\dot{\bm \varepsilon})\\
-&=\bm s^TM_0^{-1}(\bm q)(-\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2)+\bm\rho(t))\\
+&=\bm s^TM_0^{-1}(\bm q)(-k\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}+\bm\rho(t))\\
 &\le -(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2)\Vert M_0^{-1}(\bm q)\Vert\Vert \bm s\Vert+\Vert\bm\rho(t)\Vert\Vert M_0^{-1}(\bm q)\Vert\Vert \bm s\Vert\\
@@
 \begin{myrem}
-At this point, the dual sliding mode control scheme for $2$-link robotic manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator.
+At this point, the DTSM scheme for $2$-link robotic manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator.
 Consider a $n$-link robotic manipulator in where $n$ is an even number, and the desired sliding manifold can be designed as
@@
 \end{align}\par
-Referring to Theorem \ref{theorem:4}, one can obtain the dual sliding mode control input for the even $n$-link manipulator.
+Referring to Theorem \ref{theorem:4}, one can obtain the DTSM input for the even $n$-link manipulator.
 Essentially, this technique requires that the sliding mode manifold has to consist of $n/2$ pairs of individual sliding surfaces, in another words, this design for the manifold can be regarded as a work for yielding manifolds of the $n/2$ sub-systems.\par
-Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension can be excluded by using conventional terminal sliding mode control, which results in that the remained $n-1$-link manipulator can be controlled by the proposed DSM scheme.
+Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension can be excluded by using conventional terminal sliding mode control, which results in that the remained $n-1$-link manipulator can be controlled by the proposed DTSM scheme.
 \end{myrem}
 \begin{myrem}
-The singularity of the DSM scheme for the robotic manipulator can be eliminated by using the technique introduced in Theorem \ref{theorem:3}.
+The singularity of the DTSM scheme for the robotic manipulator can be eliminated by using the technique introduced in Theorem \ref{theorem:3}.
 \end{myrem}
 \begin{myrem}
-One can use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the dual sliding mode control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically.
+One can use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the DTSM control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically.
 For handling the chattering, the $sign()$ can be replaced with $sat(x,\delta)$, and the bounded value $\delta$ is determined according to actual needs.
@@
 \section{Simulation studies}\label{sec:4}
-In this section, two studies will be presented, namely, a verification on the effectiveness of the proposed DSM and MDSM schemes and an application to a manipulator stabilization evaluating the performance of the control schemes.
+In this section, two studies will be presented, namely, a verification on the effectiveness of the proposed DTSM and MDTSM schemes and an application to a manipulator stabilization evaluating the performance of the control schemes.
 \subsection{Effectiveness study}
@@
 \end{align}
-and one can produce a MDSM control scheme conveniently.
+and one can produce a MDTSM control scheme conveniently.
 It is obvious that the disturbance in the system~(\ref{eq:simulation two order system}) behaves bounded, which is said to be the following uncertainty terms:
@@
 Besides the large approaching speed selected, $\gamma$ accelerates the sliding phase indirectly.
-Therefore the design of the MDSM controller for the system~(\ref{eq:simulation two order system}) is finished, and the corresponding simulation results are illustrated in Figure~\ref{Figure:2} and Figure~\ref{Figure:3}.\par
+Therefore the design of the MDTSM controller for the system~(\ref{eq:simulation two order system}) is finished, and the corresponding simulation results are illustrated in Figure~\ref{Figure:2} and Figure~\ref{Figure:3}.\par
 From Figure~\ref{Figure:2}, it's apparent that the states converge to their desired states.
@@
 The nature of the situation mention above is the input compensating the error caused by the distance.\par
-At this point, some effectiveness of the MDSM control scheme proposed above has been verified, and in the next section, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.
+At this point, some effectiveness of the MDTSM control scheme proposed above has been verified, and in the next section, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.
 \begin{figure}
@@
 Accordingly, the uncertainty parameters in Eq.~(\ref{eq:manipulator uncertainty}) are assumed to be $\mu_0=10$, $\mu_1=3$, $\mu_2=3$.\par
-This section will give a set of simulation to examine the performance of the MDSM control in tracking the certain angle condition.
+This section will give a set of simulation to examine the performance of the MDTSM control in tracking the certain angle condition.
 The behavior of the manipulator should fulfill the initial and desired condition, namely, $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$.
@@
 The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}.
-Comparatively speaking, $q_1$ reaches the desired state at about $3s$ with the MDSM scheme, the reaching time of which is approximating $0.8s$ less than of the TSM scheme, and $q_2$ performs similar behaviors with a reasonable variable range of the angular rates.
-One can concentrate on the mission time of the entire motion, and inductively the time is decided by the manipulator finishing the final motion, i.e., for the manipulator controlled by utilizing the MDSM scheme, one can obtain the mission time $3s$ approximately, comparing with $3.25s$ for the TSM control.
-More notably, the control parameters of the TSM scheme have been optimally selected, whereas if using the parameters for the MDSM scheme, one can only get a fairy poor performance in the regulation, which leads to meaningless comparison.
-Therefore these results show that the MDSM control scheme can achieve the regulation of the manipulator effectively.
+Comparatively speaking, $q_1$ reaches the desired state at about $3s$ with the MDTSM scheme, the reaching time of which is approximating $0.8s$ less than of the TSM scheme, and $q_2$ performs similar behaviors with a reasonable variable range of the angular rates.
+One can concentrate on the mission time of the entire motion, and inductively the time is decided by the manipulator finishing the final motion, i.e., for the manipulator controlled by utilizing the MDTSM scheme, one can obtain the mission time $3s$ approximately, comparing with $3.25s$ for the TSM control.
+More notably, the control parameters of the TSM scheme have been optimally selected, whereas if using the parameters for the MDTSM scheme, one can only get a fairy poor performance in the regulation, which leads to meaningless comparison.
+Therefore these results show that the MDTSM control scheme can achieve the regulation of the manipulator effectively.
 \begin{figure}
@@
 \end{align*}\par
-The simulation results are demonstrated in Figure~\ref{Figure:6} and Figure~\ref{Figure:7}, which plot the curves of states of the system~(\ref{eq:simulation two order system}) regulated by adopting the MDSM scheme.
+The simulation results are demonstrated in Figure~\ref{Figure:6} and Figure~\ref{Figure:7}, which plot the curves of states of the system~(\ref{eq:simulation two order system}) regulated by adopting the MDTSM scheme.
 The control system completes the tracking mission at about $3.2s$ from a prescript initial condition, which performs a fairly small overshoot in the angle regulation.
@@
 \section{Conclusion}\label{sec:5}
-A dual sliding mode control for n-link robotic manipulator has been presented.
+A DTSM control for n-link robotic manipulator has been presented.
 The method integrates two individual subsystem as a unity, then builds the manifold and input for it to complete the controller design.
@@
 Also, the entire convergent time can be calculated accordingly.
-Developing the basic dual sliding mode yields the modified dual sliding mode control, providing a solution to eliminating chattering, avoiding singularity and fast convergence.
+Developing the basic DTSM yields the MDTSM control, providing a solution to eliminating chattering, avoiding singularity and fast convergence.
 For dealing with the under actuated characteristics which may appear in the system, the hierachical sliding mode technique will be considered to introduce into the control scheme, however, the control parameters selection is still a challenge.

### 2016-05-18 paper3_manuscript.tex
20160518

@@
 \section{Introduction}
-Variable structure systems (VSS) are best known due to its insensitivity to parameter variations and uncertainties~\cite{slotine1991applied}.
+Variable structure systems (VSS) are best known due to their insensitivity to parameter variations and uncertainties~\cite{slotine1991applied}.
 Its widely utilization in practice case, such as DC and AC motors, process control, aircrafts, satellites, robots and so on, has validated robustness of VSS.
@@
 designed a robust adaptive sliding mode method to guarantee the asymptotically stability of a boost converter~\cite{oucheriah2013pwm}.
-Roughly speaking, the SMC scheme is competent for normal scientific mission, due to its insensitivity of parameters and uncertainties in system, however, there still exist some obstacles, such as noncontinuous switching input in high frequency and desired convergent speed design~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some practical engineering cases~\cite{fridman2011sliding}.
+Roughly speaking, the SMC scheme is competent for normal scientific mission, due to its insensitivity of parameters and uncertainties in system, however, there still exist some obstacles, such as noncontinuous switching input in high frequency and convergent speed design~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some practical engineering cases~\cite{fridman2011sliding}.
 \par
@@
 Besides the issue on repressing the chattering, the fast convergence of the SMC scheme is also a hot subject.
-Normal linear sliding mode control takes two steps to solve a problem about the stability, namely, conducting the system states onto the prescript sliding manifold and driving these states to the origin along the manifold, and an accelerating operation usually occurs in this two phases.
+Normal linear sliding mode control takes two steps to solve a problem about the stability, namely, conducting the system states onto the prescript sliding manifold and driving these states to the origin along the manifold, and some accelerating operations usually occur in this two phases.
 The first step is said to be the approaching phase which usually requires the states converge to the desired manifold in finite time, and selecting suitable Lyapunov function and control parameters may accelerate this process; the second step is the sliding phase which is related to the designed manifold closely, and normal manifold design techniques can just guarantee the asymptotically convergence.
@@
 \end{align}
-where $\bm x = [x_1,x_2,x_3,x_4]^T$ is the system vector state; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$; $u_i(t)$, $i=1,2$ stands for the scalar input; $g_i(\bm x,t)$, $i=1,2$  is a defined as a bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0$, meaning the uncertainty and disturbance of the system.
+where $\bm x = [x_1,x_2,x_3,x_4]^T$ is the system vector state; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$; $u_i(t)$, $i=1,2$ stands for the scalar input; $g_i(\bm x,t)$, $i=1,2$  is defined as a bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0$, meaning the uncertainty and disturbance of the system.
 For the system mentioned above, we can establish a desired dual terminal sliding manifold as:
@@
 For the sake of simplicity, the symbol $t$ is usually omitting in this paper, which does not cause any confusion, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding manifold $\bm s(t)$ is often abbreviated to $\bm s$.\par
-There exist two lemmas about the finite convergence theory, providing convergent forms which contribute to the verification of the finite convergence about the DTSM control.
+There exist two lemmas about the finite convergence theory, providing convergent forms which contribute to the verification of the finite time convergence about the DTSM control.
 \begin{mylem}
@@
 \begin{mylem}
-Considering a two-order system:
+Consider a two-order system:
 \begin{align}
@@
 \dot x_1&=-\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2\\
-\dot x_2&=-\vert x_2\vert^\alpha sgn(x_3)-x_2^3-x_1.\label{eq:normal sliding manifold}
+\dot x_2&=-\vert x_2\vert^\alpha sgn(x_3)-x_2^3-x_1,\label{eq:normal sliding manifold}
 \end{split}
 \end{align}\par
-Selecting $V(t) = \frac{x_1^2+x_2^2}{2}$ obtains the finite convergent time as follows~\cite{moulay2006finite}:
+and selecting $V(t) = \frac{x_1^2+x_2^2}{2}$ obtains the finite convergent time as follows~\cite{moulay2006finite}:
 %since $\vert x\vert-x^\alpha+\vert x\vert \ge 0,0<\alpha<1$
@@
 For stabilization of the two-order system shown as~Eq. (\ref{eq:two order system}), DTSM control inputs can be given according the following theorem.
-\begin{mythm}\label{theorem:1}Dual Terminal Sliding Mode (DTSM) Control Design.
+\begin{mythm}\label{theorem:1}Dual Terminal Sliding Mode Control Design.
 The two-order system (\ref{eq:two order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq.
@@
 \begin{align}
+\begin{split}
 u_1 &= -b_1^{-1}(\bm x)(f_1(\bm x)+\alpha\vert x_1\vert^{\alpha-1}x_2+3x_1^2x_2-x_4+k_1sgn(s_1))\\
-u_2 &= -b_2^{-1}(\bm x)(f_2(\bm x)+\alpha\vert x_3\vert^{\alpha-1}x_4+3x_3^2x_4+x_2+k_2sgn(s_2)),
+u_2 &= -b_2^{-1}(\bm x)(f_2(\bm x)+\alpha\vert x_3\vert^{\alpha-1}x_4+3x_3^2x_4+x_2+k_2sgn(s_2)),\label{eq:DSM input}
+\end{split}
 \end{align}
@@
 \end{align}
-Substituting inputs (\ref{eq:dual sliding manifold}) in~Eq. (\ref{eq:V_1}) yields
+Substituting inputs (\ref{eq:DSM input}) in~Eq. (\ref{eq:V_1}) yields
 \begin{align*}
@@
 On the basis of Theorem \ref{theorem:1}, we can develop the parameters in the manifold to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:two order system}), and furthermore this method makes the design of the manifold more flexible.
-Considering the system~(\ref{eq:two order system}) with the manifold manifold $\bm s = [s_1,s_2]^T$, the details of which can be described by following expressions:
+Consider the system~(\ref{eq:two order system}) with the manifold manifold $\bm s = [s_1,s_2]^T$, the details of which can be described by following expressions:
 \begin{align}
@@
 \begin{mythm}\label{theorem:3}
-Consider a two-order system (\ref{eq:two order system}), and for eliminating the singularity in inputs of the MDTSM scheme, select a new inputs to complete the nonsingular MDTSM scheme.
+Consider a two-order system (\ref{eq:two order system}), and for eliminating the singularity in inputs of the MDTSM scheme, select new inputs to complete the nonsingular MDTSM scheme.
 Introducing the saturation terms into the original inputs yields:
@@
 One can use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the DTSM control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically.
-For handling the chattering, the $sign()$ can be replaced with $sat(x,\delta)$, and the bounded value $\delta$ is determined according to actual needs.
+For handling the chattering, the $sign(x)$ can be replaced with $sat(x,\delta)$, and the bounded value $\delta$ is determined according to actual needs.
 \end{myrem}
@@
 Also, although the states have be adjusted to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range.
-The nature of the situation mention above is the input compensating the error caused by the distance.\par
+The nature of the situation mentioned above is the input compensating the error caused by the distance.\par
 At this point, some effectiveness of the MDTSM control scheme proposed above has been verified, and in the next section, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.
@@
 \includegraphics[width=0.7\textwidth]{paper3_fig2.eps}
-\caption{1}
+\caption{Phase space trajectory}
 \label{Figure:2}
@@
 \includegraphics[width=0.7\textwidth]{paper3_fig3.eps}
-\caption{2}
+\caption{System inputs}
 \label{Figure:3}
@@
 \includegraphics[width=0.4\textwidth]{paper3_fig1.eps}
-\caption{2}
+\caption{$2$-link manipulator schematic}
 \label{Figure:1}
@@
 The values of the parameters are listed here, $r_1=1m$, $r_2=0.8m$, $J_1=5 kgm$, $J_2=5kgm$, $m_1=0.5kg$, $m_2=1.5kg$.
-In this model, the uncertainty is brought in by estimated terms, namely, $\bar m_1=0.4$ and $\bar m_2=1.2$ which are all not the actuate value obviously.
+In this model, the uncertainty is brought in by estimated terms, namely, $\bar m_1=0.4$ and $\bar m_2=1.2$ which are all not the actual value obviously.
 In addition, owing to that it sits on many terms in the dynamic equations, it's a severe challenge to guarantee the performance.
@@
 \includegraphics[width=0.7\textwidth]{paper3_fig4.eps}
-\caption{2}
+\caption{Response of $q_1$ channel}
 \label{Figure:4}
@@
 \includegraphics[width=0.7\textwidth]{paper3_fig5.eps}
-\caption{2}
+\caption{Response of $q_2$ channel}
 \label{Figure:5}
@@
 \includegraphics[width=0.7\textwidth]{paper3_fig6.eps}
-\caption{2}
+\caption{Tracking performance of $q_1$ channel}
 \label{Figure:6}
@@
 \includegraphics[width=0.7\textwidth]{paper3_fig7.eps}
-\caption{2}
+\caption{Tracking performance of $q_2$ channel}
 \label{Figure:7}

### 2016-05-19 paper3_manuscript.tex
20160519

@@
 Normal linear sliding mode control takes two steps to solve a problem about the stability, namely, conducting the system states onto the prescript sliding manifold and driving these states to the origin along the manifold, and some accelerating operations usually occur in this two phases.
-The first step is said to be the approaching phase which usually requires the states converge to the desired manifold in finite time, and selecting suitable Lyapunov function and control parameters may accelerate this process; the second step is the sliding phase which is related to the designed manifold closely, and normal manifold design techniques can just guarantee the asymptotically convergence.
+The first step is said to be the approaching phase which usually requires the states converge to the desired manifold in finite time, and selecting suitable Lyapunov function and control parameters may accelerate this process; the second step is the sliding phase which is related to the designed manifold closely, and normal manifold design techniques are able to guarantee the asymptotically convergence.
 For achieving a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and comparing with the sliding mode control design mentioned above, the most significant contributions of the terminal sliding mode is introducing the finite time convergence to the sliding phase to complete the global finite time convergence.
@@
 This nature makes the TSM scheme become an individual control subsystem, which leads to the complicity of global convergent time in some extent.
-In this paper, an integral sliding mode manifold technique is proposed for finite time stability of the two-order system, and the novel manifold involves two variables to guarantee the integral finite time convergence, and the convergent time can be obtained easily.
+In this paper, an integral sliding mode manifold technique is proposed for finite time stability of the two-order system, and the novel manifold involves two variables to guarantee the integral finite time convergence, and the convergent time is obtained easily.
 Also, the nonsingularity and chattering suppression are available in the scheme.
@@
 \begin{mylem}
-As described in~\cite{moulay2006finite}, it is assumed that the continuous function $V(t)$ is positive-define, satisfying the following condition:
+As described in~\cite{moulay2006finite}, it's assumed that the continuous function $V(t)$ is positive-define, satisfying the following condition:
 \begin{align}
@@
 \end{align}
-where $d$ is a positive scalar, and $0<\beta<1$. Then the function $V(t)$ can converge to the origin for any given $t_0$, and typically the finite convergent time $t_r$ can be given as follows:
+where $d$ is a positive scalar, and $0<\beta<1$. Then the function $V(t)$ converges to the origin for any given $t_0$, and typically the finite convergent time $t_r$ can be given as follows:
 \begin{align}
@@
 \end{mylem}
-For stabilization of the two-order system shown as~Eq. (\ref{eq:two order system}), DTSM control inputs can be given according the following theorem.
+For stabilization of the two-order system shown as~Eq. (\ref{eq:two order system}), DTSM control inputs are addressed according the following theorem.
 \begin{mythm}\label{theorem:1}Dual Terminal Sliding Mode Control Design.
@@
 \end{align*}
-Hence, the system (\ref{eq:two order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergent time can be calculated according to the finite time convergence theory.\par
+Hence, the system (\ref{eq:two order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergent time is calculated according to the finite time convergence theory.\par
 Once the system (\ref{eq:two order system}) reaches the desired manifold~(\ref{eq:dual sliding manifold}), the whole system is handled by the reduced system:
@@
 \end{align*}\par
-The total convergent time can be calculated by dividing the convergence into two phase with respect to the relation between the system and the manifold, namely, the approaching phase and the sliding phase, and specifically, according to Lemma \ref{lemma:2}, the total finite convergent time $t_f$ can be given out directly:
+The total convergent time can be calculated by dividing the convergence into two phase with respect to the relation between the system and the manifold, namely, the approaching phase and the sliding phase, and specifically, according to Lemma \ref{lemma:2}, the total finite convergent time $t_f$ is calculated from:
 \begin{align}
@@
 \end{proof}
-On the basis of Theorem \ref{theorem:1}, we can develop the parameters in the manifold to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:two order system}), and furthermore this method makes the design of the manifold more flexible.
-Consider the system~(\ref{eq:two order system}) with the manifold manifold $\bm s = [s_1,s_2]^T$, the details of which can be described by following expressions:
+On the basis of Theorem \ref{theorem:1}, we proceed to develop the parameters in the manifold to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:two order system}), and furthermore this method makes the design of the manifold more flexible.
+Consider the system~(\ref{eq:two order system}) with the manifold manifold $\bm s = [s_1,s_2]^T$, the details of which are described by following expressions:
 \begin{align}
@@
 \end{align}
-where $k_i = l_i+\eta_i$, $i=1,2$; $\eta_i>0$ is a positive scalar value. The total finite convergent time can be described as:
+where $k_i = l_i+\eta_i$, $i=1,2$; $\eta_i>0$ is a positive scalar value. The total finite convergent time is calculated from:
 \begin{align}
@@
 $\eta$ is said to be an ''approaching speed'' according to its function, a suitable selection of which will adjust the approaching time as desired in some extent.
-Hence, $\lambda$ cooperates with $\eta$ to manage the approaching status, and by utilizing the similar analysis, owing to $\gamma$ adjusting the speed of sliding phase, it can be defined as the management parameter of the sliding status.
+Hence, $\lambda$ cooperates with $\eta$ to manage the approaching status, and by utilizing the similar analysis, owing to $\gamma$ adjusting the speed of sliding phase, it's able to be defined as the management parameter of the sliding status.
 \begin{myrem}
-For the proposed designs, the parameter $\gamma$ can be defined as different scalar for the individual input, if so, one can produce the total convergent time as:
+For the proposed designs, the parameter $\gamma$ may be defined as different scalar for the individual input, if so, one can produce the total convergent time as:
 \begin{align}
@@
 \begin{mylem}\label{lemma:3}
-Considering the two-order system (\ref{eq:two order system}), the terminal sliding mode manifold can be designed as:
+Considering the two-order system (\ref{eq:two order system}), the terminal sliding mode manifold is designed as:
 \begin{align*}
@@
 \end{align}
-and $u_s>0$ can be determined according to the requirements of the performance.\par
+and $u_s>0$ is determined according to the requirements of the performance.\par
 Adopting the control scheme mentioned above, the system~(\ref{eq:two order system}) will converge to zero in finite time without any singularity occurring during the regulation process.
@@
 where $\bm {\rho}(t) = -\Delta M(\bm q)-\Delta C(\bm q,\dot {\bm q})-\Delta g(\bm q)$, and $\theta_0$, $\phi_0$, $\phi_1$, $\phi_2$, $\psi_0$, $\psi_1$, $\mu_0$, $\mu_1$, $\mu_2$ are positive constants.\par
-Select $\bm q_d$ as the desired state of the Lagrangian system~(\ref{eq:lagrangian system}), and the derivative of $\bm q_d$ is designated as $\dot {\bm q}_d$.
-Hence the state error can be given out intuitively:
+Select $\bm q_d$ as the desired state of the Lagrangian system~(\ref{eq:lagrangian system}), and the derivative of $\bm q_d$ is designated as $\dot {\bm q}_d$. Hence the state error is stated as:
 \begin{align}
@@
 \end{align}
-furthermore, one can obtain the corresponding input as follows to stabilize the system~(\ref{eq:lagrangian system}) as desired in finite time.
+furthermore, the corresponding input follows to stabilize the system~(\ref{eq:lagrangian system}) as desired in finite time.
 \begin{align}
@@
 \end{align}
-in which $k>\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2$, and it is assumed that the parameters $\mu_0$, $\mu_1$ and $\mu_2$ are known.
+in which $k>\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2$, and it's assumed that the parameters $\mu_0$, $\mu_1$ and $\mu_2$ are known.
 \end{mythm}
@@
 \end{align}
-the derivative of which can be described as
+the derivative of which is described as
 \begin{align}
@@
 Once the reaching condition is satisfied, one can achieve a reduced system by substituting $\bm s = 0$ into the system~(\ref{eq:lagrangian system}).
-It owns the form, similar to Eq.~(\ref{eq:normal sliding manifold}), and therefore, one can adopt Theorem \ref{theorem:2} to drive the reduced system converging to the origin in finite time.
+It owns the form, similar to Eq.~(\ref{eq:normal sliding manifold}), and therefore, adopting Theorem \ref{theorem:2} drives the reduced system converging to the origin in finite time.
 The proof is completed.
@@
 At this point, the DTSM scheme for $2$-link robotic manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator.
-Consider a $n$-link robotic manipulator in where $n$ is an even number, and the desired sliding manifold can be designed as
+Consider a $n$-link robotic manipulator in which $n$ is an even number, and the desired sliding manifold follows
 \begin{align}
@@
 \end{align}\par
-Referring to Theorem \ref{theorem:4}, one can obtain the DTSM input for the even $n$-link manipulator.
+Referring to Theorem \ref{theorem:4}, it's easy to obtain the DTSM input for the even $n$-link manipulator.
 Essentially, this technique requires that the sliding mode manifold has to consist of $n/2$ pairs of individual sliding surfaces, in another words, this design for the manifold can be regarded as a work for yielding manifolds of the $n/2$ sub-systems.\par
-Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension can be excluded by using conventional terminal sliding mode control, which results in that the remained $n-1$-link manipulator can be controlled by the proposed DTSM scheme.
+Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension is able to be excluded by using conventional terminal sliding mode control, which results in that the remained $n-1$-link manipulator can be controlled by the proposed DTSM scheme.
 \end{myrem}
 \begin{myrem}
-The singularity of the DTSM scheme for the robotic manipulator can be eliminated by using the technique introduced in Theorem \ref{theorem:3}.
+The singularity of the DTSM scheme for the robotic manipulator can be removed by using the technique introduced in Theorem \ref{theorem:3}.
 \end{myrem}
 \begin{myrem}
-One can use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the DTSM control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically.
-For handling the chattering, the $sign(x)$ can be replaced with $sat(x,\delta)$, and the bounded value $\delta$ is determined according to actual needs.
+One can also use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the DTSM control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically.
+For handling the chattering, the $sign(x)$ is replaced with $sat(x,\delta)$, and the bounded value $\delta$ is determined according to actual needs.
 \end{myrem}
@@
 \end{align}
-and one can produce a MDTSM control scheme conveniently.
-It is obvious that the disturbance in the system~(\ref{eq:simulation two order system}) behaves bounded, which is said to be the following uncertainty terms:
+and a MDTSM control scheme is produced conveniently.
+It's obvious that the disturbance in the system~(\ref{eq:simulation two order system}) behaves bounded, which is said to be the following uncertainty terms:
 \begin{align*}
@@
 \end{align*}
-and hence, based on the analysis in Theorem~\ref{theorem:1}, $l_1>0.1$ and $l_2>0.8$ can be determined accordingly to guarantee the reaching condition of the desired sliding manifold.
+and hence, based on the analysis in Theorem~\ref{theorem:1}, $l_1>0.1$ and $l_2>0.8$ are determined accordingly to guarantee the reaching condition of the desired sliding manifold.
 Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation two order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
@@
 Comparatively speaking, $q_1$ reaches the desired state at about $3s$ with the MDTSM scheme, the reaching time of which is approximating $0.8s$ less than of the TSM scheme, and $q_2$ performs similar behaviors with a reasonable variable range of the angular rates.
-One can concentrate on the mission time of the entire motion, and inductively the time is decided by the manipulator finishing the final motion, i.e., for the manipulator controlled by utilizing the MDTSM scheme, one can obtain the mission time $3s$ approximately, comparing with $3.25s$ for the TSM control.
+Concentrate on the mission time of the entire motion, and inductively the time is decided by the manipulator finishing the final motion, i.e., for the manipulator controlled by utilizing the MDTSM scheme, one can obtain the mission time $3s$ approximately, comparing with $3.25s$ for the TSM control.
 More notably, the control parameters of the TSM scheme have been optimally selected, whereas if using the parameters for the MDTSM scheme, one can only get a fairy poor performance in the regulation, which leads to meaningless comparison.
-Therefore these results show that the MDTSM control scheme can achieve the regulation of the manipulator effectively.
+Therefore these results show that the MDTSM control scheme is able to achieve the regulation of the manipulator effectively.
 \begin{figure}
@@
 The more general case, the robotic manipulator is usually required to track variable signal, is discussed in this section.
-Particularly, one can continue to use the parameters of the controller mentioned above, and the mission condition is changed as follows:
+Particularly, we continue to use the parameters of the controller mentioned above, and the mission condition is changed as follows:
 \begin{align*}
@@
 The method integrates two individual subsystem as a unity, then builds the manifold and input for it to complete the controller design.
-The control scheme can guarantee the reaching condition of the desired sliding manifold, meanwhile the system states can converge to the origin along the desired manifold.
+The control scheme is able to guarantee the reaching condition of the desired sliding manifold, meanwhile the system states converge to the origin along the desired manifold.
 Also, the entire convergent time can be calculated accordingly.

### 2016-05-21 paper3_manuscript.tex
20160521

@@
 This nature makes the TSM scheme become an individual control subsystem, which leads to the complicity of global convergent time in some extent.
-In this paper, an integral sliding mode manifold technique is proposed for finite time stability of the two-order system, and the novel manifold involves two variables to guarantee the integral finite time convergence, and the convergent time is obtained easily.
+In this paper, an integral sliding mode manifold technique is proposed for finite time stability of the second-order system, and the novel manifold involves two variables to guarantee the integral finite time convergence, and the convergent time is obtained easily.
 Also, the nonsingularity and chattering suppression are available in the scheme.
 \par
-In this paper, a dual sliding mode (DTSM) controller is proposed for a class of two-order nonlinear systems with disturbances and uncertainties.
+In this paper, a dual sliding mode (DTSM) controller is proposed for a class of second-order nonlinear systems with disturbances and uncertainties.
 A novel DTSM manifold is exploited to fulfill the finite time convergence, and the approaching and sliding time are both able to be calculated directly.
 A modified DTSM (MDTSM) control scheme is presented to stabilize the motion of the $n$-link robotic manipulators.
-The remained paper is organized as follows: Section~\ref{sec:2} introduces a DTSM scheme for a class of two-order system, and the finite time convergence of the approaching and sliding is verified.
+The remained paper is organized as follows: Section~\ref{sec:2} introduces a DTSM scheme for a class of second-order system, and the finite time convergence of the approaching and sliding is verified.
 In addition, we add performance parameters for improving the DTSM scheme to obtain the MDTSM scheme, and the newly presented method has a better performance in theoretical analysis.
@@
 \section{Dual terminal sliding mode control}\label{sec:2}
-Consider a two-order nominal nonlinear system:
+Consider a second-order nominal nonlinear system:
 \begin{align}
@@
 \dot x_3(t) &= x_4(t)\\
-\dot x_4(t) &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)u_2(t),\label{eq:two order system}
+\dot x_4(t) &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)u_2(t),\label{eq:second-order system}
 \end{split}
@@
 \begin{mylem}
-Consider a two-order system:
+Consider a second-order system:
 \begin{align}
@@
 \end{mylem}
-For stabilization of the two-order system shown as~Eq. (\ref{eq:two order system}), DTSM control inputs are addressed according the following theorem.
+For stabilization of the second-order system shown as~Eq. (\ref{eq:second-order system}), DTSM control inputs are addressed according the following theorem.
 \begin{mythm}\label{theorem:1}Dual Terminal Sliding Mode Control Design.
-The two-order system (\ref{eq:two order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq.
+The second-order system (\ref{eq:second-order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq.
 (\ref{eq:dual sliding manifold}) in finite time.
@@
 \end{align*}
-Hence, the system (\ref{eq:two order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergent time is calculated according to the finite time convergence theory.\par
-Once the system (\ref{eq:two order system}) reaches the desired manifold~(\ref{eq:dual sliding manifold}), the whole system is handled by the reduced system:
+Hence, the system (\ref{eq:second-order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergent time is calculated according to the finite time convergence theory.\par
+Once the system (\ref{eq:second-order system}) reaches the desired manifold~(\ref{eq:dual sliding manifold}), the whole system is handled by the reduced system:
 \begin{align*}
@@
 \end{align*}\par
-The total convergent time can be calculated by dividing the convergence into two phase with respect to the relation between the system and the manifold, namely, the approaching phase and the sliding phase, and specifically, according to Lemma \ref{lemma:2}, the total finite convergent time $t_f$ is calculated from:
+The total convergent time can be calculated by dividing the convergence into two phases with respect to the relation between the system and the manifold, namely, the approaching phase and the sliding phase, and specifically, according to Lemma \ref{lemma:2}, the total finite convergent time $t_f$ is calculated from:
 \begin{align}
@@
 \end{proof}
-On the basis of Theorem \ref{theorem:1}, we proceed to develop the parameters in the manifold to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:two order system}), and furthermore this method makes the design of the manifold more flexible.
-Consider the system~(\ref{eq:two order system}) with the manifold manifold $\bm s = [s_1,s_2]^T$, the details of which are described by following expressions:
+On the basis of Theorem \ref{theorem:1}, we proceed to develop the parameters in the manifold to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:second-order system}), and furthermore this method makes the design of the manifold more flexible.
+Consider the system~(\ref{eq:second-order system}) with the manifold manifold $\bm s = [s_1,s_2]^T$, the details of which are described by following expressions:
 \begin{align}
@@
 \begin{mythm}\label{theorem:2}Modified Dual Terminal Sliding Mode Control Design.
-The two-order system (\ref{eq:two order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq.
+The second-order system (\ref{eq:second-order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq.
 (\ref{eq:modified dual sliding manifold}) in finite time.
@@
 \begin{mylem}\label{lemma:3}
-Considering the two-order system (\ref{eq:two order system}), the terminal sliding mode manifold is designed as:
+Considering the second-order system (\ref{eq:second-order system}), the terminal sliding mode manifold is designed as:
 \begin{align*}
@@
 and $u_s>0$ is determined according to the requirements of the performance.\par
-Adopting the control scheme mentioned above, the system~(\ref{eq:two order system}) will converge to zero in finite time without any singularity occurring during the regulation process.
+Adopting the control scheme mentioned above, the system~(\ref{eq:second-order system}) will converge to zero in finite time without any singularity occurring during the regulation process.
 \end{mylem}
 \begin{mythm}\label{theorem:3}
-Consider a two-order system (\ref{eq:two order system}), and for eliminating the singularity in inputs of the MDTSM scheme, select new inputs to complete the nonsingular MDTSM scheme.
+Consider a second-order system (\ref{eq:second-order system}), and for eliminating the singularity in inputs of the MDTSM scheme, select new inputs to complete the nonsingular MDTSM scheme.
 Introducing the saturation terms into the original inputs yields:
@@
 \end{align}
-one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:two order system}), providing the finite time convergence by using sliding mode technique.
+one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:second-order system}), providing the finite time convergence by using sliding mode technique.
 \end{mythm}
@@
 \end{proof}
+When the input $u_1$ equals to $u_2$ in system.~(\ref{eq:second-order system}), the number of the inputs is fewer than the degrees of the freedom, resulting in that the issue transforms to be an underactuated stabilization.
+These underactuated systems are frequently used in the scientific field, such as flexible manipulators, overhead crane and underwater robots, because fewer actuators may decrease the mass and save the energy as well.
+Cooperating with the hierarchical sliding mode methodology, the manifold design scheme proposed above is able to control this kind of systems.
+We give the hierarchical dual terminal sliding mode design directly.
+\begin{mythm}
+Consider a nonlinear system described as:
+\begin{align}
+\begin{split}
+&\dot x_1 = x_2\\
+&\dot x_2 = f_1(\bm x) + g_1(\bm x)+b_1(\bm x)u\\
+&\dot x_3 = x_4\\
+&\dot x_4 = f_2(\bm x) + g_2(\bm x)+b_2(\bm x)u,
+\end{split}
+\end{align}
+where the condition of variables is same to the system~(\ref{eq:second-order system}). Construct the manifold as:
+\begin{align}
+S = c_1s_1+c_2s_2,
+\end{align}
+where $c_1$ and $c_2$ are suitable positive constants, and $s_1$ and $s_2$ has been defined in the MDSM design. Adopting the equivalent control design method deduces the individual equivalent inputs:
+\begin{align}
+u_{eq1} = -b_1^{-1}(\bm x)(f_1(\bm x)+\gamma\alpha\vert x_1\vert^{\alpha-1}x_2+3\gamma x_1^2x_2-\lambda x_4)\\
+u_{eq2} = -b_2^{-1}(\bm x)(f_2(\bm x)+\gamma\alpha\vert x_3\vert^{\alpha-1}x_4+3\gamma x_3^2x_4+\lambda x_2)
+\end{align}
+\end{mythm}
 \section{Dual terminal sliding mode control for rigid manipulators}\label{sec:3}
@@
 \subsection{Effectiveness study}
-For verifying the effectiveness of the proposed control scheme, consider the following two-order nonlinear system with the disturbance:
+For verifying the effectiveness of the proposed control scheme, consider the following second-order nonlinear system with the disturbance:
 \begin{align}
@@
 \dot x_3 &= x_4\\
-\dot x_4 &= 0.3\sin(3t)+0.5e^{-3t}+u_2,\label{eq:simulation two order system}
+\dot x_4 &= 0.3\sin(3t)+0.5e^{-3t}+u_2,\label{eq:simulation second-order system}
 \end{split}
@@
 and a MDTSM control scheme is produced conveniently.
-It's obvious that the disturbance in the system~(\ref{eq:simulation two order system}) behaves bounded, which is said to be the following uncertainty terms:
+It's obvious that the disturbance in the system~(\ref{eq:simulation second-order system}) behaves bounded, which is said to be the following uncertainty terms:
 \begin{align*}
@@
 and hence, based on the analysis in Theorem~\ref{theorem:1}, $l_1>0.1$ and $l_2>0.8$ are determined accordingly to guarantee the reaching condition of the desired sliding manifold.
-Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation two order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
+Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation second-order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
 The system is supposed to be conducted to the desired state $\bm x_d=(0,0,0,0)$ from a prescript state $\bm x_0=(1.2,1.2,1.2,1.2)$.
@@
 Besides the large approaching speed selected, $\gamma$ accelerates the sliding phase indirectly.
-Therefore the design of the MDTSM controller for the system~(\ref{eq:simulation two order system}) is finished, and the corresponding simulation results are illustrated in Figure~\ref{Figure:2} and Figure~\ref{Figure:3}.\par
+Therefore the design of the MDTSM controller for the system~(\ref{eq:simulation second-order system}) is finished, and the corresponding simulation results are illustrated in Figure~\ref{Figure:2} and Figure~\ref{Figure:3}.\par
 From Figure~\ref{Figure:2}, it's apparent that the states converge to their desired states.
@@
 \end{align*}\par
-The simulation results are demonstrated in Figure~\ref{Figure:6} and Figure~\ref{Figure:7}, which plot the curves of states of the system~(\ref{eq:simulation two order system}) regulated by adopting the MDTSM scheme.
+The simulation results are demonstrated in Figure~\ref{Figure:6} and Figure~\ref{Figure:7}, which plot the curves of states of the system~(\ref{eq:simulation second-order system}) regulated by adopting the MDTSM scheme.
 The control system completes the tracking mission at about $3.2s$ from a prescript initial condition, which performs a fairly small overshoot in the angle regulation.
@@
 A DTSM control for n-link robotic manipulator has been presented.
-The method integrates two individual subsystem as a unity, then builds the manifold and input for it to complete the controller design.
+The method integrates two individual subsystems as a unity, then builds the manifold and input for it to complete the controller design.
 The control scheme is able to guarantee the reaching condition of the desired sliding manifold, meanwhile the system states converge to the origin along the desired manifold.

### 2016-05-22 paper3_manuscript.tex
20160522

@@
 &\dot x_3 = x_4\\
-&\dot x_4 = f_2(\bm x) + g_2(\bm x)+b_2(\bm x)u,
+&\dot x_4 = f_2(\bm x) + g_2(\bm x)+b_2(\bm x)u,\label{eq:underactuated system}
 \end{split}
@@
 \end{align}
-where $c_1$ and $c_2$ are suitable positive constants, and $s_1$ and $s_2$ has been defined in the MDSM design. Adopting the equivalent control design method deduces the individual equivalent inputs:
+where $c_1$ and $c_2$ are suitable positive constants, and $s_1$ and $s_2$ have been defined in the MDSM design. Adopting the equivalent control design method deduces the individual equivalent inputs:
 \begin{align}
-u_{eq1} = -b_1^{-1}(\bm x)(f_1(\bm x)+\gamma\alpha\vert x_1\vert^{\alpha-1}x_2+3\gamma x_1^2x_2-\lambda x_4)\\
-u_{eq2} = -b_2^{-1}(\bm x)(f_2(\bm x)+\gamma\alpha\vert x_3\vert^{\alpha-1}x_4+3\gamma x_3^2x_4+\lambda x_2)
+\begin{split}
+&u_{eq1} = -b_1^{-1}(\bm x)(f_1(\bm x)+\gamma\alpha\vert x_1\vert^{\alpha-1}x_2+3\gamma x_1^2x_2-\lambda x_4)\\
+&u_{eq2} = -b_2^{-1}(\bm x)(f_2(\bm x)+\gamma\alpha\vert x_3\vert^{\alpha-1}x_4+3\gamma x_3^2x_4+\lambda x_2),
+\end{split}
 \end{align}
+and the control law $u$ has the following formula:
+\begin{align}
+u = (c_1b_1(\bm x)+c_2b_2(\bm x))^{-1}(c_1b_1(\bm x)u_{eq1}+c_2b_2(\bm x)u_{eq2}-\eta_u sign(S)-k_u S)\label{eq:underactuated input}
+\end{align}
+to regulate all states of the underactuated system~(\ref{eq:underactuated system}) as desired in finite time.
 \end{mythm}
+\begin{proof}
+Select a Lyapunov function candidate $V=\frac{1}{2}S^2$, and differentiate it with respect to time $t$:
+\begin{align}
+\begin{split}
+\dot V &= S\dot S = S(c_1\dot s_1+c_2\dot s_2)\\
+&=S(c_1(f_1(\bm x)+g_1(\bm x)+b_1(\bm x)u+\gamma\alpha\vert x_1\vert^{\alpha-1}x_2+3\gamma x_1^2x_2-\lambda x_4)\\
+&\quad+c_2(f_2(\bm x)+g_2(\bm x)+b_2(\bm x)u+\gamma\alpha\vert x_3\vert^{\alpha-1}x_4+3\gamma x_3^2x_4+\lambda x_2))\\
+&=S(c_1(f_1(\bm x)+g_1(\bm x)+\gamma\alpha\vert x_1\vert^{\alpha-1}x_2+3\gamma x_1^2x_2-\lambda x_4)\\
+&\quad+c_2(f_2(\bm x)+g_2(\bm x)+\gamma\alpha\vert x_3\vert^{\alpha-1}x_4+3\gamma x_3^2x_4+\lambda x_2)+(c_1b_1(\bm x)+c_2b_2(\bm x))u).\label{eq:underactuated Lyapunov}
+\end{split}
+\end{align}
+Substituting the input~(\ref{eq:underactuated input}) into Eq.~(\ref{eq:underactuated Lyapunov}) one can obtain
+\begin{align}
+\begin{split}
+\dot V &= S(c_1(f_1(\bm x)+g_1(\bm x)+\gamma\alpha\vert x_1\vert^{\alpha-1}x_2+3\gamma x_1^2x_2-\lambda x_4)\\
+&\quad+c_2(f_2(\bm x)+g_2(\bm x)+\gamma\alpha\vert x_3\vert^{\alpha-1}x_4+3\gamma x_3^2x_4+\lambda x_2)\\
+&\quad+(c_1b_1(\bm x)u_{eq1}+c_2b_2(\bm x)u_{eq2}-\eta_u sign(S)-k_u S))\\
+&= S(c_1g_1(\bm x)+c_2g_2(\bm x)-\eta_u sign(S)-k_u S)\\
+&\le -(\eta_u -\vert c_1g_1(\bm x)+c_2g_2(\bm x)\vert)\vert S\vert-k_u S^2.
+\end{split}
+\end{align}
+As $\vert g_i(\bm x)\vert<l_i$ exists, a big enough $\eta_u$ may be chosen to guarantee the reaching condition of the manifold $S$.
+The proof of the stability of the desired sliding surfaces $s_1$ and $s_2$ is same to the one in \cite{wang2004design}, and omitted here.
+This completes the proof.
+\end{proof}
 \section{Dual terminal sliding mode control for rigid manipulators}\label{sec:3}

### 2016-05-22 paper3_manuscript.tex
20160522

@@
 A new terminal sliding mode manifold design technique is addressed to achieve finite time convergence of the sliding phase, and furthermore utilizing the involved dual variables combines the individual sliding mode surfaces to obtain a integral sliding mode dynamics, the convergent time of which is also integral for the entire system.
-The newly proposed method also has the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motion of the rigid robotic manipulator.
+The underactuated issue is coped with by introducing the hierarchical sliding mode methodology into the basis dual sliding mode design.
+These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the rigid robotic manipulator.
 Simulation results validate the theoretical analysis about the proposed method.
@@
 A novel DTSM manifold is exploited to fulfill the finite time convergence, and the approaching and sliding time are both able to be calculated directly.
+For coping with the underacutated issue, cooperating with the hierarchical sliding surface design methodology, we develop a hierarchical dual terminal sliding mode (HDTSM) control.
 A modified DTSM (MDTSM) control scheme is presented to stabilize the motion of the $n$-link robotic manipulators.
 The remained paper is organized as follows: Section~\ref{sec:2} introduces a DTSM scheme for a class of second-order system, and the finite time convergence of the approaching and sliding is verified.
-In addition, we add performance parameters for improving the DTSM scheme to obtain the MDTSM scheme, and the newly presented method has a better performance in theoretical analysis.
+In addition, we add performance parameters for improving the DTSM scheme to obtain the MDTSM scheme, and the newly presented method has a better performance in theoretical analysis; for stabilizing the underactuated system, the HDTSM design is developed as well in this section.
 In Section~\ref{sec:3}, the MDTSM is applied to the motion regulation of the $n$-link robotic  manipulator, and the stability analysis is also carried out.
@@
 These underactuated systems are frequently used in the scientific field, such as flexible manipulators, overhead crane and underwater robots, because fewer actuators may decrease the mass and save the energy as well.
-Cooperating with the hierarchical sliding mode methodology, the manifold design scheme proposed above is able to control this kind of systems.
+Cooperating with the hierarchical sliding mode methodology, the manifold design scheme proposed above is able to control this kind of systems \cite{wang2004design}.
 We give the hierarchical dual terminal sliding mode design directly.
@@
 \section{Simulation studies}\label{sec:4}
-In this section, two studies will be presented, namely, a verification on the effectiveness of the proposed DTSM and MDTSM schemes and an application to a manipulator stabilization evaluating the performance of the control schemes.
+In this section, three studies will be presented, namely, a verification on the effectiveness of the proposed DTSM and MDTSM schemes, an underactuated example and an application to a manipulator stabilization evaluating the performance of the control schemes.
 \subsection{Effectiveness study}
@@
 \end{figure}
+\subsection{Uneractuated example}
+Figure~\ref{Figure:8} shows an overhead crane system, the state space equations of which is same with the formula in Eq.~(\ref{eq:underactuated system}) with state variables selected as $\bm x=(x,\dot x,q,\dot q)$, and the details are listed:
+\begin{align}
+\begin{split}
+f_1&=(M+m\sin^2q)^{-1}(mL\dot q^2\sin q+mg\sin q\cos q)\\
+b_1&=(M+m\sin^2q)^{-1}\\
+f_2&=-(ML+mL\sin^2q)^{-1}((M+m)g\sin q+mL\dot q^2\sin q\cos q)\\
+b_2&=-(ML+mL\sin^2q)^{-1}\cos q,
+\end{split}
+\end{align}
+where $x$ is defined as the displacement of the horizontal direction, and $q$ stands for the swing angle from the vertical line.
+$M=1kg$ and $m=0.8kg$ donate the masses of the trolley and the load in Figure~\ref{Figure:8}, respectively, and $g=9.8m/s^2$ refers to as the acceleration of gravity.
+$L=0.305m$ represents the length of the rope.
+In this simulation, the disturbances are also introduced:
+\begin{align} 
+g_1(\bm x)&= 0.02\sin t\\
+g_2(\bm x)&=0.07e^{-4t},
+\end{align}
+and those boundaries are easy to obtain.
+The initial condition of the overhead crane system is $\bm x_0 = (0.1,0,0.1,0)$, while the desired status is $\bm x_d = (2,0,0,0)$.
+The HDSM controller can be designed with the following set of parameters:
+$c_1=1$, $c_2=4$, $\eta_u = 0.1$, $k_u=1$, $\gamma = 1$, $\lambda = 3$, $\alpha = 0.6$.\par
+Figure~\ref{Figure:8} shows the state response curves of the overhead crane system controlled using the HDSM control scheme, and the results show that the controller stabilize the displacement at $6s$ approximately, though the disturbance exists in the system.
+One can find that the swing angle is fluctuating in a fairly small range, the boundary of which is not more than $1\times 10^-3rad$, hence this phenomena is reasonable and also occurs in the stable hierarchical sliding mode control \cite{wang2004design}.
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{paper3_fig8.eps}
+\caption{Overhead crane schematic}
+\label{Figure:8}
+\end{figure}
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth]{paper3_fig9.eps}
+\caption{Overhead crane schematic}
+\label{Figure:9}
+\end{figure}
 \subsection{Performance of the robotic manipulator}
@@
 Figure~\ref{Figure:1} is the $2$-link manipulator schematic, the dynamics of which can be explained by the dynamic equations in following forms:
-
 \begin{figure}
 \centering
-\includegraphics[width=0.4\textwidth]{paper3_fig1.eps}
+\includegraphics[width=0.3\textwidth]{paper3_fig1.eps}
 \caption{$2$-link manipulator schematic}
@@
 Developing the basic DTSM yields the MDTSM control, providing a solution to eliminating chattering, avoiding singularity and fast convergence.
-For dealing with the under actuated characteristics which may appear in the system, the hierachical sliding mode technique will be considered to introduce into the control scheme, however, the control parameters selection is still a challenge.
+For dealing with the under actuated characteristics which may appear in the system, the HDTSM control is derived, and the overhead crane example verifies its effectiveness.
+However, the control parameters selection is still a challenge especially in the HDTSM scheme, and we will effort to excavate a full order dual terminal sliding mode methodology in the future for removing the obstacle caused by parameters essentially.
 \section{Acknowledgment}

### 2016-05-29 paper3_manuscript.tex
20160529

@@
 This paper proposes a novel dual terminal sliding mode control for rigid robotic manipulator.
-A new terminal sliding mode manifold design technique is addressed to achieve finite time convergence of the sliding phase, and furthermore utilizing the involved dual variables combines the individual sliding mode surfaces to obtain a integral sliding mode dynamics, the convergent time of which is also integral for the entire system.
-The underactuated issue is coped with by introducing the hierarchical sliding mode methodology into the basis dual sliding mode design.
+A new terminal sliding mode manifold design technique is addressed to achieve finite time convergence of the sliding phase, and furthermore utilizing the involved dual variables combines the individual sliding mode surfaces to obtain an integral sliding mode dynamics, the convergent time of which is also integral for the entire system.
+The underactuated issue is coped with by introducing the hierarchical sliding mode methodology into the basic dual sliding mode design.
 These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the rigid robotic manipulator.
@@
 Variable structure systems (VSS) are best known due to their insensitivity to parameter variations and uncertainties~\cite{slotine1991applied}.
-Its widely utilization in practice case, such as DC and AC motors, process control, aircrafts, satellites, robots and so on, has validated robustness of VSS.
+Its widely utilization in reality, such as DC and AC motors, process control, aircrafts, satellites, robots and so on, has validated robustness of VSS.
 As one of the most important branch of the VSS, the sliding mode control (SMC) has become a popular solution to the issue about various control and signal process missions in recent years~\cite{zhao2015nonlinear,zhang2015attitude}.
 Meza-S{\'a}nchez et al.
-applied the second order sliding mode controller to a 3-DOF helicopter prototype, and verified the effectiveness via the experimental test bed~\cite{meza2015output}.
+applied the second-order sliding mode controller to a 3-DOF helicopter prototype, and verified the effectiveness via the experimental test bed~\cite{meza2015output}.
 Zheng et al.
@@
 For alleviating the side effects, many researchers addressed remarkable approaches to improve the performance of the SMC scheme in last decade~\cite{zong2013quasi,santiesteban2013time,mu2015continuous,evangelista2013lyapunov,gonzalez2014chattering,dadras2012fractional,zhao2013output}.
-Among these methods, the high order sliding mode control and super-twisting sliding mode control efforts to generate the continuous inputs~\cite{castillo2015higher,palosz2015laser,edwards2016adaptive,zhao2015finite,liu2015second}, which eliminate the chattering by hiding the switching in high-order terms or absorbing the switching via some techniques.
+Among these methods, the high-order sliding mode control and super-twisting sliding mode control effort to generate the continuous inputs~\cite{castillo2015higher,palosz2015laser,edwards2016adaptive,zhao2015finite,liu2015second}, which eliminate the chattering by hiding the switching in high-order terms or absorbing the switching via some techniques.
 \par
@@
 Normal linear sliding mode control takes two steps to solve a problem about the stability, namely, conducting the system states onto the prescript sliding manifold and driving these states to the origin along the manifold, and some accelerating operations usually occur in this two phases.
-The first step is said to be the approaching phase which usually requires the states converge to the desired manifold in finite time, and selecting suitable Lyapunov function and control parameters may accelerate this process; the second step is the sliding phase which is related to the designed manifold closely, and normal manifold design techniques are able to guarantee the asymptotically convergence.
+The first step is said to be the approaching phase which usually requires the states converge to the desired manifold in finite time, and selecting suitable Lyapunov function and control parameters may accelerate this process; the second step is the sliding phase which is related to the designed manifold closely, and trivial manifold design techniques are able to guarantee the asymptotically convergence.
 For achieving a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and comparing with the sliding mode control design mentioned above, the most significant contributions of the terminal sliding mode is introducing the finite time convergence to the sliding phase to complete the global finite time convergence.
@@
 \par
-In this paper, a dual sliding mode (DTSM) controller is proposed for a class of second-order nonlinear systems with disturbances and uncertainties.
+In this paper, a dual terminal sliding mode (DTSM) controller is proposed for a class of second-order nonlinear systems with disturbances and uncertainties.
 A novel DTSM manifold is exploited to fulfill the finite time convergence, and the approaching and sliding time are both able to be calculated directly.
@@
 A modified DTSM (MDTSM) control scheme is presented to stabilize the motion of the $n$-link robotic manipulators.
-The remained paper is organized as follows: Section~\ref{sec:2} introduces a DTSM scheme for a class of second-order system, and the finite time convergence of the approaching and sliding is verified.
+The remained paper is organized as follows: Section~\ref{sec:2} introduces a DTSM scheme for a class of second-order system, and the finite time convergence of the approaching and sliding phase is verified.
 In addition, we add performance parameters for improving the DTSM scheme to obtain the MDTSM scheme, and the newly presented method has a better performance in theoretical analysis; for stabilizing the underactuated system, the HDTSM design is developed as well in this section.
 In Section~\ref{sec:3}, the MDTSM is applied to the motion regulation of the $n$-link robotic  manipulator, and the stability analysis is also carried out.
-Section~\ref{sec:4} exhibited the simulation results, and finally the conclusion is assigned in Section~\ref{sec:5}.
+Section~\ref{sec:4} exhibits the simulation results, and finally the conclusion is assigned in Section~\ref{sec:5}.
 \section{Dual terminal sliding mode control}\label{sec:2}
@@
 \end{align}
-where $\bm x = [x_1,x_2,x_3,x_4]^T$ is the system vector state; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$; $u_i(t)$, $i=1,2$ stands for the scalar input; $g_i(\bm x,t)$, $i=1,2$  is defined as a bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0$, meaning the uncertainty and disturbance of the system.
+where $\bm x = [x_1,x_2,x_3,x_4]^T$ is the system vector state; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$; $u_i(t)$, $i=1,2$ stands for the scalar input; $g_i(\bm x,t)$, $i=1,2$  is defined as a bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0, i=1,2$, meaning the uncertainty and disturbance of the system.
 For the system mentioned above, we can establish a desired dual terminal sliding manifold as:
@@
 where $sgn(x)$ is the sign function, and $0<\alpha<1$ is a positive constant.
-For the sake of simplicity, the symbol $t$ is usually omitting in this paper, which does not cause any confusion, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding manifold $\bm s(t)$ is often abbreviated to $\bm s$.\par
+For the sake of simplicity, the symbol $t$ is usually omitted in this paper, which does not cause any confusion, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding manifold $\bm s(t)$ is often abbreviated to $\bm s$.\par
 There exist two lemmas about the finite convergence theory, providing convergent forms which contribute to the verification of the finite time convergence about the DTSM control.
@@
 \end{split}
-\end{align}\par
+\end{align}
 and selecting $V(t) = \frac{x_1^2+x_2^2}{2}$ obtains the finite convergent time as follows~\cite{moulay2006finite}:
@@
 On the basis of Theorem \ref{theorem:1}, we proceed to develop the parameters in the manifold to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:second-order system}), and furthermore this method makes the design of the manifold more flexible.
-Consider the system~(\ref{eq:second-order system}) with the manifold manifold $\bm s = [s_1,s_2]^T$, the details of which are described by following expressions:
+Consider the system~(\ref{eq:second-order system}) with the manifold $\bm s = [s_1,s_2]^T$, the details of which are described by following expressions:
 \begin{align}
@@
 \end{proof}
-\section{Dual terminal sliding mode control for rigid manipulators}\label{sec:3}
-In this section, a DTSM control is proposed for the rigid $2$-link robotic manipulator
+\section{Modified Dual terminal sliding mode control for rigid manipulators}\label{sec:3}
+In this section, the MDTSM control is proposed for the rigid $2$-link robotic manipulator
 \begin{align}
@@
 \begin{align}
-\bm \varepsilon = \bm q -\bm q_d
+\bm \varepsilon = \bm q -\bm q_d.
 \end{align}
@@
 \begin{myrem}
-At this point, the DTSM scheme for $2$-link robotic manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator.
+At this point, the MDTSM scheme for $2$-link robotic manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator.
 Consider a $n$-link robotic manipulator in which $n$ is an even number, and the desired sliding manifold follows
@@
 \end{align}\par
-Referring to Theorem \ref{theorem:4}, it's easy to obtain the DTSM input for the even $n$-link manipulator.
+Referring to Theorem \ref{theorem:4}, it's easy to obtain the MDTSM input for the even $n$-link manipulator.
 Essentially, this technique requires that the sliding mode manifold has to consist of $n/2$ pairs of individual sliding surfaces, in another words, this design for the manifold can be regarded as a work for yielding manifolds of the $n/2$ sub-systems.\par
-Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension is able to be excluded by using conventional terminal sliding mode control, which results in that the remained $n-1$-link manipulator can be controlled by the proposed DTSM scheme.
+Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension is able to be excluded by using conventional terminal sliding mode control, which results in that the remained $n-1$-link manipulator can be controlled by the proposed MDTSM scheme.
 \end{myrem}
 \begin{myrem}
-The singularity of the DTSM scheme for the robotic manipulator can be removed by using the technique introduced in Theorem \ref{theorem:3}.
+The singularity of the MDTSM scheme for the robotic manipulator can be removed by using the technique introduced in Theorem \ref{theorem:3}.
 \end{myrem}
@@
 \end{align}
-and a MDTSM control scheme is produced conveniently.
+and an MDTSM control scheme is produced conveniently.
 It's obvious that the disturbance in the system~(\ref{eq:simulation second-order system}) behaves bounded, which is said to be the following uncertainty terms:
@@
 Figure~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely related to $\eta$, for the purpose of avoiding the largely chattering caused by $\eta$, the saturation function $sat()$ is applied to take place of $sign()$ to absorb it.
-Also, although the states have be adjusted to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range.
+Also, although the states have been adjusted to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range.
 The nature of the situation mentioned above is the input compensating the error caused by the distance.\par
-At this point, some effectiveness of the MDTSM control scheme proposed above has been verified, and in the next section, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.
+At this point, some effectiveness of the MDTSM control scheme proposed above has been verified, and in Section \ref{sec:robotica manipulator}, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.
 \begin{figure}
@@
 \end{figure}
-\subsection{Performance of the robotic manipulator}
+\subsection{Performance of the robotic manipulator}\label{sec:robotica manipulator}
 In order to evaluate the performance of the proposed control scheme, a simulation about the $2$-link robotic manipulator is presented in the following context.

### 2016-11-08 paper3_manuscript.tex
20160529
20161108

@@
 This paper proposes a novel dual terminal sliding mode control for rigid robotic manipulator.
-A new terminal sliding mode manifold design technique is addressed to achieve finite time convergence of the sliding phase, and furthermore utilizing the involved dual variables combines the individual sliding mode surfaces to obtain an integral sliding mode dynamics, the convergent time of which is also integral for the entire system.
+A new terminal sliding mode manifold design technique is addressed to achieve finite time convergence of the sliding phase, and furthermore utilizing the involved dual variables combines the individual sliding mode surfaces to obtain an integral sliding mode dynamics, the convergence time of which is also integral for the entire system.
 The underactuated issue is coped with by introducing the hierarchical sliding mode methodology into the basic dual sliding mode design.
@@
 designed a robust adaptive sliding mode method to guarantee the asymptotically stability of a boost converter~\cite{oucheriah2013pwm}.
-Roughly speaking, the SMC scheme is competent for normal scientific mission, due to its insensitivity of parameters and uncertainties in system, however, there still exist some obstacles, such as noncontinuous switching input in high frequency and convergent speed design~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some practical engineering cases~\cite{fridman2011sliding}.
+Roughly speaking, the SMC scheme is competent for normal scientific mission, due to its insensitivity of parameters and uncertainties in system, however, there still exist some obstacles, such as noncontinuous switching input in high frequency and convergence speed design~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some practical engineering cases~\cite{fridman2011sliding}.
 \par
@@
 According to the achievements mentioned above, one can find that the conventional terminal sliding mode manifold design techniques are similar, since they are all based on the single variable finite time control, in another words, the sliding mode dynamics only involves the individual variable and its derivative essentially~\cite{mu2016switching}.
-This nature makes the TSM scheme become an individual control subsystem, which leads to the complicity of global convergent time in some extent.
-In this paper, an integral sliding mode manifold technique is proposed for finite time stability of the second-order system, and the novel manifold involves two variables to guarantee the integral finite time convergence, and the convergent time is obtained easily.
+This nature makes the TSM scheme become an individual control subsystem, which leads to the complicity of global convergence time in some extent.
+In this paper, an integral sliding mode manifold technique is proposed for finite time stability of the second-order system, and the novel manifold involves two variables to guarantee the integral finite time convergence, and the convergence time is obtained easily.
 Also, the nonsingularity and chattering suppression are available in the scheme.
@@
 For the sake of simplicity, the symbol $t$ is usually omitted in this paper, which does not cause any confusion, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding manifold $\bm s(t)$ is often abbreviated to $\bm s$.\par
-There exist two lemmas about the finite convergence theory, providing convergent forms which contribute to the verification of the finite time convergence about the DTSM control.
+There exist two lemmas about the finite convergence theory, providing convergence forms which contribute to the verification of the finite time convergence about the DTSM control.
 \begin{mylem}
@@
 \end{align}
-where $d$ is a positive scalar, and $0<\beta<1$. Then the function $V(t)$ converges to the origin for any given $t_0$, and typically the finite convergent time $t_r$ can be given as follows:
+where $d$ is a positive scalar, and $0<\beta<1$. Then the function $V(t)$ converges to the origin for any given $t_0$, and typically the finite convergence time $t_r$ can be given as follows:
 \begin{align}
@@
 \end{align}
-and selecting $V(t) = \frac{x_1^2+x_2^2}{2}$ obtains the finite convergent time as follows~\cite{moulay2006finite}:
+and selecting $V(t) = \frac{x_1^2+x_2^2}{2}$ obtains the finite convergence time as follows~\cite{moulay2006finite}:
 %since $\vert x\vert-x^\alpha+\vert x\vert \ge 0,0<\alpha<1$
@@
 \end{align}
-the convergent time of which is
+the convergence time of which is
 \begin{align}
@@
 \begin{proof}
+According to the equivalent control technique and the sliding surface reaching condition~\cite{Arie1993sliding}, the inputs can be design as
+\begin{align}\begin{split}
+u_1 &= u_{eq1}+u_{sw1}\\
+u_2 &= u_{eq2}+u_{sw2}\notag
+\end{split}\end{align}
+where
+\begin{align}\begin{split}
+u_{eq1} &= -b_1^{-1}(\bm x)(f_1(\bm x)+\alpha\vert x_1\vert^{\alpha-1}x_2+3x_1^2x_2-x_4)\\
+u_{eq2} &= -b_2^{-1}(\bm x)(f_2(\bm x)+\alpha\vert x_3\vert^{\alpha-1}x_4+3x_3^2x_4+x_2)\notag
+\end{split}\end{align}
+are the eauivalent control inputs to ensure $\dot s_1 = 0$ and $\dot s_2=0$, respectively, with $u_i = u_{eqi}$, $i=1,2$.
+The switching inputs are designed as $u_{swi}=-b_i^{-1}k_isgn(s_i)$, $i=1,2$ to guarantee the finite time reaching conditions of the ideal sliding surface.
+
 Consider the Lyapunov function $V=\frac{1}{2}{\bm s}^T\bm s$, the derivative of which with respect to time $\dot V = {\bm s}^T \bm {\dot s}$ follows
@@
 \end{align*}
-Hence, the system (\ref{eq:second-order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergent time is calculated according to the finite time convergence theory.\par
+Hence, the system (\ref{eq:second-order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergence time is calculated according to the finite time convergence theory.\par
 Once the system (\ref{eq:second-order system}) reaches the desired manifold~(\ref{eq:dual sliding manifold}), the whole system is handled by the reduced system:
@@
 \end{align*}\par
-The total convergent time can be calculated by dividing the convergence into two phases with respect to the relation between the system and the manifold, namely, the approaching phase and the sliding phase, and specifically, according to Lemma \ref{lemma:2}, the total finite convergent time $t_f$ is calculated from:
+The total convergence time can be calculated by dividing the convergence into two phases with respect to the relation between the system and the manifold, namely, the approaching phase and the sliding phase, and specifically, according to Lemma \ref{lemma:2}, the total finite convergence time $t_f$ is calculated from:
 \begin{align}
@@
 \end{align}
-where $\hat V(t) = \frac{x_1^2+x_3^2}{2}$ is the Lyapunov function describing the convergent motion of the reduced system.
+where $\hat V(t) = \frac{x_1^2+x_3^2}{2}$ is the Lyapunov function describing the convergence motion of the reduced system.
 The approaching and sliding time are defined as $t_r$ and $t_s$, respectively.
@@
 \end{align}
-where $k_i = l_i+\eta_i$, $i=1,2$; $\eta_i>0$ is a positive scalar value. The total finite convergent time is calculated from:
+where $k_i = l_i+\eta_i$, $i=1,2$; $\eta_i>0$ is a positive scalar value. The total finite convergence time is calculated from:
 \begin{align}
-t_f = \underbrace{t_0+\frac{\sqrt{2}V^{\frac{1}{2}}(t_0)}{\min(\eta_1,\eta_2)}}_{t_r}+\underbrace{\frac{(2\hat V(t_r))^{\frac{1-\alpha}{2}}}{\gamma(1-\alpha)}}_{t_s}<\infty,\label{eq:total convergent time}
+t_f = \underbrace{t_0+\frac{\sqrt{2}V^{\frac{1}{2}}(t_0)}{\min(\eta_1,\eta_2)}}_{t_r}+\underbrace{\frac{(2\hat V(t_r))^{\frac{1-\alpha}{2}}}{\gamma(1-\alpha)}}_{t_s}<\infty,\label{eq:total convergence time}
 \end{align}
@@
 \end{proof}
-After introducing the parameters $\lambda$ and $\gamma$ into the DTSM scheme, the performances of the approaching and sliding phases become regulatable, meaning that these parameters can adjust the convergent time analytically.
-Although $\lambda$ does not appear in Eq.~(\ref{eq:total convergent time}), the establishment of $V(t_0)$ involves it when the state $\bm x(t_0)$ has been fixed.
+After introducing the parameters $\lambda$ and $\gamma$ into the DTSM scheme, the performances of the approaching and sliding phases become regulatable, meaning that these parameters can adjust the convergence time analytically.
+Although $\lambda$ does not appear in Eq.~(\ref{eq:total convergence time}), the establishment of $V(t_0)$ involves it when the state $\bm x(t_0)$ has been fixed.
 Strictly speaking, it affects the approaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V(t)=\bm s^T(t)\bm s(t) = 0,\forall t\ge t_r$.
@@
 \begin{myrem}
-For the proposed designs, the parameter $\gamma$ may be defined as different scalar for the individual input, if so, one can produce the total convergent time as:
+For the proposed designs, the parameter $\gamma$ may be defined as different scalar for the individual input, if so, one can produce the total convergence time as:
 \begin{align}
-t_f = \underbrace{t_0+\frac{\sqrt{2}V^{\frac{1}{2}}(t_0)}{\min(\eta_1,\eta_2)}}_{t_r}+\underbrace{\frac{(2\hat V(t_r))^{\frac{1-\alpha}{2}}}{\min(\gamma_1,\gamma_2)(1-\alpha)}}_{t_s}<\infty,\label{eq:normal total convergent time}
+t_f = \underbrace{t_0+\frac{\sqrt{2}V^{\frac{1}{2}}(t_0)}{\min(\eta_1,\eta_2)}}_{t_r}+\underbrace{\frac{(2\hat V(t_r))^{\frac{1-\alpha}{2}}}{\min(\gamma_1,\gamma_2)(1-\alpha)}}_{t_s}<\infty,\label{eq:normal total convergence time}
 \end{align}
@@
 Besides the large approaching speed selected, $\gamma$ accelerates the sliding phase indirectly.
-Therefore the design of the MDTSM controller for the system~(\ref{eq:simulation second-order system}) is finished, and the corresponding simulation results are illustrated in Figure~\ref{Figure:2} and Figure~\ref{Figure:3}.\par
+Therefore the design of the MDTSM controller for the system~(\ref{eq:simulation second-order system}) is finished, and the corresponding simulation results are illustrated from Figure~\ref{Figure:2} to Figure~\ref{Figure:3}.\par
 From Figure~\ref{Figure:2}, it's apparent that the states converge to their desired states.
-Figure~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely related to $\eta$, for the purpose of avoiding the largely chattering caused by $\eta$, the saturation function $sat()$ is applied to take place of $sign()$ to absorb it.
+\textcolor{red}{For the nominal system~(\ref{eq:simulation second-order system}) handled by utilizing the MDTSM controller, accrording to Eq.~(\ref{eq:total convergence time}) and simulation datas, we can calculate the maximum theoretical finite convergence time $t_f=5.2609s$ directly.
+The system states, in other words, can be stable in no more than $5.609s$ theoretically.
+However, the system response results in Figure~\ref{Figure:2_20161108} indicate that all the states have been stable after about $1.5s$, which is far less than $t_f$.
+Hence, from the view of the convergence time, the simulation results are in accordance with the theoretical analyses.} Figure~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely related to $\eta$, for the purpose of avoiding the largely chattering caused by $\eta$, the saturation function $sat()$ is applied to take place of $sign()$ to absorb it.
 Also, although the states have been adjusted to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range.
@@
 \label{Figure:2}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth]{paper3_fig2_20161108.eps}
+\caption{system response}
+\label{Figure:2_20161108}
 \end{figure}
@@
 $c_1=1$, $c_2=4$, $\eta_u = 0.1$, $k_u=1$, $\gamma = 1$, $\lambda = 3$, $\alpha = 0.6$.\par
-Figure~\ref{Figure:8} shows the state response curves of the overhead crane system controlled using the HDSM control scheme, and the results show that the controller stabilize the displacement at $6s$ approximately, though the disturbance exists in the system.
+Figure~\ref{Figure:9} shows the state response curves of the overhead crane system controlled using the HDSM control scheme, and the results show that the controller stabilize the displacement at $6s$ approximately, though the disturbance exists in the system.
 One can find that the swing angle is fluctuating in a fairly small range, the boundary of which is not more than $1\times 10^-3rad$, hence this phenomena is reasonable and also occurs in the stable hierarchical sliding mode control \cite{wang2004design}.
@@
 \includegraphics[width=0.7\textwidth]{paper3_fig9.eps}
-\caption{Overhead crane schematic}
+\caption{Overhead crane dynamics}
 \label{Figure:9}
@@
 The behavior of the manipulator should fulfill the initial and desired condition, namely, $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$.
-In order to ensure the stability and a fast convergent speed, the control parameters are chosen conservatively to make the manipulator track the desired attitude in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $k = 100$.
+In order to ensure the stability and a fast convergence speed, the control parameters are chosen conservatively to make the manipulator track the desired attitude in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $k = 150$.
 The terminal sliding mode control (TSM) scheme, as a comparison, is also implemented to regulate the behavior of the manipulator:
@@
 Comparatively speaking, $q_1$ reaches the desired state at about $3s$ with the MDTSM scheme, the reaching time of which is approximating $0.8s$ less than of the TSM scheme, and $q_2$ performs similar behaviors with a reasonable variable range of the angular rates.
-Concentrate on the mission time of the entire motion, and inductively the time is decided by the manipulator finishing the final motion, i.e., for the manipulator controlled by utilizing the MDTSM scheme, one can obtain the mission time $3s$ approximately, comparing with $3.25s$ for the TSM control.
+\textcolor{red}{From the results shown in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}, we can find that the maximum theoretical finite convergence time $t_f=3.0843s$, which can be obtained directly accoring to Eq.~(\ref{eq:total convergence time}) and simulation datas, is more than $2.5s$, the convergence time of the simulation result.
+Hence, we can conclude that the results have verified the analyses about the convergence time in Section~\ref{sec:2}.} Concentrate on the mission time of the entire motion, and inductively the time is decided by the manipulator finishing the final motion, i.e., for the manipulator controlled by utilizing the MDTSM scheme, one can obtain the mission time $3s$ approximately, comparing with $3.25s$ for the TSM control.
 More notably, the control parameters of the TSM scheme have been optimally selected, whereas if using the parameters for the MDTSM scheme, one can only get a fairy poor performance in the regulation, which leads to meaningless comparison.
@@
 The control scheme is able to guarantee the reaching condition of the desired sliding manifold, meanwhile the system states converge to the origin along the desired manifold.
-Also, the entire convergent time can be calculated accordingly.
+Also, the entire convergence time can be calculated accordingly.
 Developing the basic DTSM yields the MDTSM control, providing a solution to eliminating chattering, avoiding singularity and fast convergence.
@@
 \section{Acknowledgment}
-This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61503097).
+This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61503101).
 \section{References}

### 2016-11-09 paper3_manuscript.tex
20161109

@@
 \end{proof}
+\textcolor{red}{
+In practice, the control input can not be very large due to the input limitation, such as the tension limitation in the deployment of the tethered satellite system~\cite{Ma201667}, and hence it is meaningful to adapt the proposed controllers for the system subjected to the input limitation.
+Consider a nominal second-order system subjected to the input limitation:
+\begin{align}
+\begin{split}
+\dot x_1(t) &= x_2(t)\\
+\dot x_2(t) &= f_1(\bm x,t)+g_1(\bm x,t)+b_1(\bm x,t)f_b(u_1(t))\\
+\dot x_3(t) &= x_4(t)\\
+\dot x_4(t) &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)f_b(u_2(t)),\label{eq:second-order system subjected to limitation}
+\end{split}
+\end{align}
+whree $f_b(u) = R(u)u$ is a bounded function, which owns the properties as follows:
+\begin{align}\begin{split}
+  R(u)=\begin{cases}
+  u_{max}/u &u>u_{max}\\
+  1&u_{min}\le u\le u_{max}\\
+  u_{min}/u& u<u_{min}.
+\end{cases}\end{split}
+\end{align}
+\begin{myas}~\cite{Ma201667}
+For guaranteeing $0<R(u)\le 1$, $u_{max}$ and $u_{min}$ satisfy $u_{min}<0<u_{max}$.
+The external disturbance $g_i(\bm x,t)$, $i=1,2$ inputs $u_i$, $i=1,2$ and system state variables are all bounded, accordingly,
+\begin{align}\begin{split}
+  \varpi_1 &\ge \Vert f_1(\bm x)+\gamma\alpha\vert x_1\vert^{\alpha-1}x_2+3\gamma x_1^2x_2-\lambda x_4\Vert\\
+  \varpi_2 &\ge \Vert f_2(\bm x)+\gamma\alpha\vert x_3\vert^{\alpha-1}x_4+3\gamma x_3^2x_4+\lambda x_2\Vert\\
+  0&<\varphi\le R(u) \le 1
+\end{split}\end{align}
+\end{myas}
+Thanks to the above assumption, we give out the adaptive dual terminal sliding mode control scheme.
+\begin{mythm}
+Considering the nominal second-order system subjected to the input limitation~\ref{eq:second-order system subjected to limitation}, the inputs $u_i$,$i=1,2$ can be designed as
+\begin{align}
+  u_i &= -\varpi_i\nu\omega_i(t) b_i^{-1}sgn(s_i)\\
+  \dot\omega_i(t)&= \varpi_i\nu\varphi e^{-2\varphi^{-1}\omega_i^{-1}(t)}sgn(s_i)
+\end{align}
+\end{mythm}
+}
+
 When the input $u_1$ equals to $u_2$ in system.~(\ref{eq:second-order system}), the number of the inputs is fewer than the degrees of the freedom, resulting in that the issue transforms to be an underactuated stabilization.
@@
 \textcolor{red}{For the nominal system~(\ref{eq:simulation second-order system}) handled by utilizing the MDTSM controller, accrording to Eq.~(\ref{eq:total convergence time}) and simulation datas, we can calculate the maximum theoretical finite convergence time $t_f=5.2609s$ directly.
-The system states, in other words, can be stable in no more than $5.609s$ theoretically.
+The system states, in other words, can be stable in no more than $5.2609s$ theoretically.
 However, the system response results in Figure~\ref{Figure:2_20161108} indicate that all the states have been stable after about $1.5s$, which is far less than $t_f$.
-Hence, from the view of the convergence time, the simulation results are in accordance with the theoretical analyses.} Figure~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely related to $\eta$, for the purpose of avoiding the largely chattering caused by $\eta$, the saturation function $sat()$ is applied to take place of $sign()$ to absorb it.
-Also, although the states have been adjusted to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range.
-The nature of the situation mentioned above is the input compensating the error caused by the distance.\par
-At this point, some effectiveness of the MDTSM control scheme proposed above has been verified, and in Section \ref{sec:robotica manipulator}, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.
+Hence, from the view of the convergence time, the simulation results are in accordance with the theoretical analyses.} Figure~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely related to $\eta$, for the purpose of avoiding the large chattering, the boundary layer technique is adopted.
+Although the states have been adjusted to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range.
+The nature of the situation mentioned above means that the fluctuating inputs compensate the error caused by the disturbance.\par
+At this point, some effectiveness of the proposed MDTSM control scheme has been verified, and in Section \ref{sec:robotica manipulator}, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.
 \begin{figure}
@@
 \end{figure}
-\subsection{Uneractuated example}
+\subsection{Underactuated example}
 Figure~\ref{Figure:8} shows an overhead crane system, the state space equations of which is same with the formula in Eq.~(\ref{eq:underactuated system}) with state variables selected as $\bm x=(x,\dot x,q,\dot q)$, and the details are listed:
@@
 Comparatively speaking, $q_1$ reaches the desired state at about $3s$ with the MDTSM scheme, the reaching time of which is approximating $0.8s$ less than of the TSM scheme, and $q_2$ performs similar behaviors with a reasonable variable range of the angular rates.
-\textcolor{red}{From the results shown in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}, we can find that the maximum theoretical finite convergence time $t_f=3.0843s$, which can be obtained directly accoring to Eq.~(\ref{eq:total convergence time}) and simulation datas, is more than $2.5s$, the convergence time of the simulation result.
-Hence, we can conclude that the results have verified the analyses about the convergence time in Section~\ref{sec:2}.} Concentrate on the mission time of the entire motion, and inductively the time is decided by the manipulator finishing the final motion, i.e., for the manipulator controlled by utilizing the MDTSM scheme, one can obtain the mission time $3s$ approximately, comparing with $3.25s$ for the TSM control.
-More notably, the control parameters of the TSM scheme have been optimally selected, whereas if using the parameters for the MDTSM scheme, one can only get a fairy poor performance in the regulation, which leads to meaningless comparison.
-Therefore these results show that the MDTSM control scheme is able to achieve the regulation of the manipulator effectively.
+\textcolor{red}{From the results shown in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}, we can find that the maximum theoretical finite convergence time $t_f=3.0843s$, which can be obtained directly accoring to Eq.~(\ref{eq:total convergence time}) and simulation datas, is more than $2.3s$, the convergence time of the simulation result.
+Hence, we can conclude that the results have verified the analyses about the convergence time in Section~\ref{sec:2}.
+For the MDTSM controller, the jiont~1 finishes its desired behaviour at about $2.3s$, and meanwhile the joint~2 spends about $1.6s$ completing the desired mission.
+Also, by observing the results, we can find that the stabilization time of the proposed method is less  than the TSM controller's, and the regulating process of the manipulators is steady and reasonable.} Therefore these results show that the MDTSM control scheme is able to achieve the regulation of the manipulator effectively.
 \begin{figure}

### 2016-11-10 paper3_manuscript.tex
20161110

@@
 \begin{split}
-\dot x_1(t) &= x_2(t)\\
-\dot x_2(t) &= f_1(\bm x,t)+g_1(\bm x,t)+b_1(\bm x,t)u_1(t)\\
-\dot x_3(t) &= x_4(t)\\
-\dot x_4(t) &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)u_2(t),\label{eq:second-order system}
+\dot x_1 &= x_2\\
+\dot x_2 &= f_1(\bm x,t)+g_1(\bm x,t)+b_1(\bm x,t)u_1\\
+\dot x_3 &= x_4\\
+\dot x_4 &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)u_2,\label{eq:second-order system}
 \end{split}
@@
 \begin{align}
-\bm s(t) = [s_1(t),s_2(t)]^T,
+\bm s = [s_1,s_2]^T,
 \end{align}
@@
 \begin{split}
-s_1(t) &= x_2(t)+\vert x_1(t)\vert^{\alpha} sgn(x_1(t))+x_1^3(t)-x_3(t)\\
-s_2(t) &= x_4(t)+\vert x_3(t)\vert^{\alpha} sgn(x_3(t))+x_3^3(t)+x_1(t),\label{eq:dual sliding manifold}
+s_1 &= x_2+\vert x_1\vert^{\alpha} sgn(x_1)+x_1^3(t)-x_3\\
+s_2 &= x_4+\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3(t)+x_1,\label{eq:dual sliding manifold}
 \end{split}
@@
 where $sgn(x)$ is the sign function, and $0<\alpha<1$ is a positive constant.
-For the sake of simplicity, the symbol $t$ is usually omitted in this paper, which does not cause any confusion, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding manifold $\bm s(t)$ is often abbreviated to $\bm s$.\par
+For the sake of simplicity, the symbol $t$ is usually omitted in this paper, which does not cause any confusion, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding manifold $\bm s$ is often abbreviated to $\bm s$.\par
 There exist two lemmas about the finite convergence theory, providing convergence forms which contribute to the verification of the finite time convergence about the DTSM control.
@@
 \begin{proof}
-According to the equivalent control technique and the sliding surface reaching condition~\cite{Arie1993sliding}, the inputs can be design as
+\textcolor{red}{According to the equivalent control technique and the sliding surface reaching condition~\cite{Arie1993sliding}, the inputs can be design as
 \begin{align}\begin{split}
@@
 are the eauivalent control inputs to ensure $\dot s_1 = 0$ and $\dot s_2=0$, respectively, with $u_i = u_{eqi}$, $i=1,2$.
-The switching inputs are designed as $u_{swi}=-b_i^{-1}k_isgn(s_i)$, $i=1,2$ to guarantee the finite time reaching conditions of the ideal sliding surface.
+The switching inputs are designed as $u_{swi}=-b_i^{-1}k_isgn(s_i)$, $i=1,2$ to guarantee the finite time reaching conditions of the ideal sliding surface.}
 
@@
 \begin{split}
-s_1(t) &= x_2(t)+\gamma(\vert x_1(t)\vert^{\alpha} sgn(x_1(t))+x_1^3(t))-\lambda x_3(t)\\
-s_2(t) &= x_4(t)+\gamma(\vert x_3(t)\vert^{\alpha} sgn(x_3(t))+x_3^3(t))+\lambda x_1(t),\label{eq:modified dual sliding manifold}
+s_1 &= x_2+\gamma(\vert x_1\vert^{\alpha} sgn(x_1)+x_1^3(t))-\lambda x_3\\
+s_2 &= x_4+\gamma(\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3(t))+\lambda x_1,\label{eq:modified dual sliding manifold}
 \end{split}
@@
 Although $\lambda$ does not appear in Eq.~(\ref{eq:total convergence time}), the establishment of $V(t_0)$ involves it when the state $\bm x(t_0)$ has been fixed.
-Strictly speaking, it affects the approaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V(t)=\bm s^T(t)\bm s(t) = 0,\forall t\ge t_r$.
+Strictly speaking, it affects the approaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V(t)=\bm s^T(t)\bm s = 0,\forall t\ge t_r$.
 Admittedly, the variety of $\lambda$ is only modestly helpful in this approaching time regulation due to its limited effect on $V(t_0)$.
@@
 \begin{align*}
-s_1(t) &= x_2(t)+\gamma_1\vert x_1\vert^{\alpha_1}sgn(x_1)\\
-s_2(t) &= x_4(t)+\gamma_2\vert x_3\vert^{\alpha_2}sgn(x_3),
+s_1 &= x_2+\gamma_1\vert x_1\vert^{\alpha_1}sgn(x_1)\\
+s_2 &= x_4+\gamma_2\vert x_3\vert^{\alpha_2}sgn(x_3),
 \end{align*}
@@
 \begin{split}
-\dot x_1(t) &= x_2(t)\\
-\dot x_2(t) &= f_1(\bm x,t)+g_1(\bm x,t)+b_1(\bm x,t)f_b(u_1(t))\\
-\dot x_3(t) &= x_4(t)\\
-\dot x_4(t) &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)f_b(u_2(t)),\label{eq:second-order system subjected to limitation}
+\dot x_1 &= x_2\\
+\dot x_2 &= f_1(\bm x,t)+g_1(\bm x,t)+b_1(\bm x,t)f_b(u_1)\\
+\dot x_3 &= x_4\\
+\dot x_4 &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)f_b(u_2),\label{eq:second-order system subjected to limitation}
 \end{split}
@@
 \end{align}
-\begin{myas}~\cite{Ma201667}
+\begin{myas}~\cite{Ma201667}\label{myas:1}
 For guaranteeing $0<R(u)\le 1$, $u_{max}$ and $u_{min}$ satisfy $u_{min}<0<u_{max}$.
@@
 \begin{align}\begin{split}
-  \varpi_1 &\ge \Vert f_1(\bm x)+\gamma\alpha\vert x_1\vert^{\alpha-1}x_2+3\gamma x_1^2x_2-\lambda x_4\Vert\\
-  \varpi_2 &\ge \Vert f_2(\bm x)+\gamma\alpha\vert x_3\vert^{\alpha-1}x_4+3\gamma x_3^2x_4+\lambda x_2\Vert\\
+  \varpi_1 &\ge \Vert f_1(\bm x)+\gamma\alpha\vert x_1\vert^{\alpha-1}x_2+3\gamma x_1^2x_2-\lambda x_4+g_1(\bm x)\Vert\\
+  \varpi_2 &\ge \Vert f_2(\bm x)+\gamma\alpha\vert x_3\vert^{\alpha-1}x_4+3\gamma x_3^2x_4+\lambda x_2+g_2(\bm x)\Vert\\
   0&<\varphi\le R(u) \le 1
@@
 \begin{mythm}
-Considering the nominal second-order system subjected to the input limitation~\ref{eq:second-order system subjected to limitation}, the inputs $u_i$,$i=1,2$ can be designed as
+Considering the nominal second-order system subjected to the input limitation~(\ref{eq:second-order system subjected to limitation}), the inputs $u_i$,$i=1,2$ can be designed as
 \begin{align}
-  u_i &= -\varpi_i\nu\omega_i(t) b_i^{-1}sgn(s_i)\\
-  \dot\omega_i(t)&= \varpi_i\nu\varphi e^{-2\varphi^{-1}\omega_i^{-1}(t)}sgn(s_i)
+  u_i &= -\varpi_i\nu_i\omega_i b_i^{-1}sgn(s_i)\\
+  \dot\omega_i&= \varpi_i\nu_i\varphi_i e^{-2\varphi_i^{-1}\omega_i^{-1}}\vert s_i\vert
 \end{align}
+with $\nu_i>1$ and $\omega_i(0)>0$, such that the trajectories of the system states can converge to the sliding surfaces in Eq.~(\ref{eq:modified dual sliding manifold}).
 \end{mythm}
+\begin{proof}
+Consider the Lyapunov function
+$$V=\frac{1}{2}\bm s^T\bm s+\frac{1}{2}v_1^2+\frac{1}{2}v_2^2$$
+with
+$$v_i = \omega_ie^{\varphi_i^{-1}\omega_i^{-1}}$$
+and hence we can proceed to obtain the derivative of the Lyapunov function
+\begin{align}\begin{split}
+\dot V &=s_1\dot s_1+s_2\dot s_2+v_1\dot v_1+v_2\dot v_2\\
+&=s_1(f_1(\bm x)+\gamma\alpha\vert x_1\vert^{\alpha-1}x_2+3\gamma x_1^2x_2-\lambda x_4+g_1(\bm x)+b_1(\bm x)u_1)\\
+&\quad +s_2(f_2(\bm x)+\gamma\alpha\vert x_3\vert^{\alpha-1}x_4+3\gamma x_3^2x_4+\lambda x_2+g_2(\bm x)+b_2(\bm x)u_2)\\
+&\quad+\varpi_1\nu_1(\omega_1-1)\vert s_1\vert+\varpi_2\nu_2(\omega_2-1)\vert s_2\vert\\
+&\le \varpi_1\vert s_1\vert+\varpi_2\vert s_2\vert-\varpi_1\nu_1\omega_1\vert s_1\vert-\varpi_2\nu_2\omega_2\vert s_2\vert\\
+&\quad + \varpi_1\nu_1(\omega_1-1)\vert s_1\vert+\varpi_2\nu_2(\omega_2-1)\vert s_2\vert\\
+&\le -\varpi_1(\nu_1-1)\vert s_1\vert-\varpi_2(\nu_2-1)\vert s_2\vert\le 0
+\end{split}\end{align}\label{V linmitation}
+$\dot V$ is therefore negative semi-deﬁnite while $V_1$ is positive deﬁnite.
+Since  $s_i$ is bounded according to assumption~\ref{myas:1}, we can have $\lim_{t\to\infty}V<\infty$ and proceed to deduce the integration of inequality~(\ref{V linmitation}) to obtain foloowing results
+\begin{align}\begin{split}
+V(0)&\ge V(t)+\int_0^t(\nu_1-1)\varpi_1\vert s_1(\varsigma)\vert+(\nu_2-1)\varpi_2\vert s_2(\varsigma)\vert d\varsigma\\
+&\ge\int_0^t(\nu_1-1)\varpi_1\vert s_1(\varsigma)\vert+(\nu_2-1)\varpi_2\vert s_2(\varsigma)\vert d\varsigma.
+\end{split}\end{align}
+Hence we can conclude the sliding dynamics are asymptotically stable in the light of Barbalat’s lemmas.
+Here the proof completes, and the system states can converge to origins by referring to the analyses in Theorem~\ref{theorem:1}.
+\end{proof}
 }
-
 When the input $u_1$ equals to $u_2$ in system.~(\ref{eq:second-order system}), the number of the inputs is fewer than the degrees of the freedom, resulting in that the issue transforms to be an underactuated stabilization.
@@
 \tau_2
-\end{pmatrix},
+\end{pmatrix},\label{eq:manipulator}
 \end{align}
@@
 For the MDTSM controller, the jiont~1 finishes its desired behaviour at about $2.3s$, and meanwhile the joint~2 spends about $1.6s$ completing the desired mission.
-Also, by observing the results, we can find that the stabilization time of the proposed method is less  than the TSM controller's, and the regulating process of the manipulators is steady and reasonable.} Therefore these results show that the MDTSM control scheme is able to achieve the regulation of the manipulator effectively.
+Also, by observing the results, we can find that the stabilization time of the proposed method is less  than the TSM controller's, and the regulating process of the manipulators is steady and reasonable.
+The control torques of the joints are depicted in Figure~\ref{Figure:torque}.
+It is obvious that the torques of the two jionts are both switching dramatically at the beginning, and this phenomenon is caused directly by the rapidly changing sliding mode dynamics $s_i$.
+Moreover, at about $1.7s$, all the joint states are regulated to locate in the vicinity of the origin, and the boundary layer technique works to generate a continuous torque in the subsequent time.} Therefore these results show that the MDTSM control scheme is able to achieve the regulation of the manipulator effectively.
 \begin{figure}
@@
 \end{figure}
-The more general case, the robotic manipulator is usually required to track variable signal, is discussed in this section.
-Particularly, we continue to use the parameters of the controller mentioned above, and the mission condition is changed as follows:
+
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth]{paper3_torque.eps}
+\caption{Joint torques}
+\label{Figure:torque}
+\end{figure}
+
+\textcolor{red}{At this point, we have verifed the feasibility of the MDTSM controller on step responses of the joints of the manipulator, and in mostly engineering applications, manipulators are required to track the variable desied signals, which own the actual physical meanings, such as polish, machine tools and laser beam cutting.
+Accordingly, the tracking performance of the robotic manipulator controlled by the proposed methods is studied in this section, and we continue to use the parameters of the controller mentioned above, and the mission condition is changed as follows:}
 \begin{align*}
@@
 \end{align*}\par
-The simulation results are demonstrated in Figure~\ref{Figure:6} and Figure~\ref{Figure:7}, which plot the curves of states of the system~(\ref{eq:simulation second-order system}) regulated by adopting the MDTSM scheme.
-The control system completes the tracking mission at about $3.2s$ from a prescript initial condition, which performs a fairly small overshoot in the angle regulation.
+ \textcolor{red}{The simulation results are demonstrated in Figure~\ref{Figure:6} and Figure~\ref{Figure:7}, which plot the trajectories of joints of the manipulator~(\ref{eq:manipulator}) regulated by adopting the MDTSM controller.
+In Figure~\ref{Figure:6}, we can find that the error between the variable desired signal and the joint angle $q_1$ keeps decreasing frome the initial state, and the two trajectories reach a confluence at about $3s$, which means that $q_1$ has absolutely tracked the variable desired signal, and the similar conclusion about $q_2$ can also be obtained from the results in Figure~\ref{Figure:7}.
+Taken as a whole, the control system completes the tracking mission at about $3.2s$ from the prescript initial conditions, which performs the smoothly tracking motion subjected to the variable desired signals.}
 \begin{figure}
@@
 \end{figure}
+Another important issue that we always meet in engineering applications, is the actuator constrains 
 \section{Conclusion}\label{sec:5}

### 2016-11-11 paper3_manuscript.tex
20161111

@@
 \begin{frontmatter}
-\title{A New Dual Terminal Sliding Mode Control Design For Rigid Robotic Manipulator}
+\title{A New Dual Terminal SMC Design For Rigid Robotic Manipulator}
 \author{Zhiqiang Ma}
@@
 \begin{abstract}
-This paper proposes a novel dual terminal sliding mode control for rigid robotic manipulator.
-A new terminal sliding mode manifold design technique is addressed to achieve finite time convergence of the sliding phase, and furthermore utilizing the involved dual variables combines the individual sliding mode surfaces to obtain an integral sliding mode dynamics, the convergence time of which is also integral for the entire system.
-The underactuated issue is coped with by introducing the hierarchical sliding mode methodology into the basic dual sliding mode design.
-These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the rigid robotic manipulator.
-Simulation results validate the theoretical analysis about the proposed method.
+This paper proposes a dual terminal SMC scheme for the rigid robotic manipulator.
+\textcolor{red}{As a signiﬁcant novelty, the presented design technique integates the individual sliding mode surfaces to achieve the finite time convergence of overall system states by utilizing specially designed construct, and accordingly the convergence time for the entire system is easily obtained due to the integral design.
+The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue are solved by introducing the hierarchical methodology into the basic dual SMC scheme.
+We combine the adaptive technique with the proposed method to eliminate the bad effect caused by the input limitation in the rigious stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the rigid robotic manipulator.
+Simulation results validate the theoretical analyses about the proposed method.
 \end{abstract}
 \begin{keyword}
-Finite time control; Robotic manipulator control; Terminal sliding mode; Sliding mode manifold design; Stability analysis
+Finite time control; Robotic manipulator control; TSM; Input limitation; Stability analysis
 \end{keyword}
@@
 \section{Introduction}
-Variable structure systems (VSS) are best known due to their insensitivity to parameter variations and uncertainties~\cite{slotine1991applied}.
-Its widely utilization in reality, such as DC and AC motors, process control, aircrafts, satellites, robots and so on, has validated robustness of VSS.
-As one of the most important branch of the VSS, the sliding mode control (SMC) has become a popular solution to the issue about various control and signal process missions in recent years~\cite{zhao2015nonlinear,zhang2015attitude}.
+\textcolor{red}{Variable structure systems (VSS) are best known due to their insensitivity to parametric uncertainties~\cite{slotine1991applied}, and have been widely used in engineering applications, such as DC and DC converters~\cite{Tan2008General}, network control schemes~\cite{Hou2016}, aircrafts~\cite{Loza2015Sensor}, tethered satellite systems~\cite{Ma201667}, robotic manipulators~\cite{Beak2016A} and so on.
+As one important branch of the VSS, the sliding mode control (SMC) has become a popular solution to different kinds of control and signal process issues in recent years~\cite{zhao2015nonlinear,zhang2015attitude}.
 Meza-S{\'a}nchez et al.
-applied the second-order sliding mode controller to a 3-DOF helicopter prototype, and verified the effectiveness via the experimental test bed~\cite{meza2015output}.
+applied the second-order SMC scheme to a 3-DOF helicopter prototype based on the experimental test bed~\cite{meza2015output}.
 Zheng et al.
-implemented the SMC to eliminate the effect of the input quantization generated between the coder and the decoder~\cite{zheng2016sliding}.
+implemented the SMC law to eliminate the bad effect of the input quantization in the coding and decoding process~\cite{zheng2016sliding}.
 Guzman et al.
-investigated the application of a SMC in a power factor rectifier with constant switching frequency~\cite{guzman2016sliding}.
+investigated the application of a SMC in a power factor rectifier with the constant switching frequency~\cite{guzman2016sliding}.
 Said et al.
-designed a robust adaptive sliding mode method to guarantee the asymptotically stability of a boost converter~\cite{oucheriah2013pwm}.
-Roughly speaking, the SMC scheme is competent for normal scientific mission, due to its insensitivity of parameters and uncertainties in system, however, there still exist some obstacles, such as noncontinuous switching input in high frequency and convergence speed design~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some practical engineering cases~\cite{fridman2011sliding}.
-\par
-For alleviating the side effects, many researchers addressed remarkable approaches to improve the performance of the SMC scheme in last decade~\cite{zong2013quasi,santiesteban2013time,mu2015continuous,evangelista2013lyapunov,gonzalez2014chattering,dadras2012fractional,zhao2013output}.
-Among these methods, the high-order sliding mode control and super-twisting sliding mode control effort to generate the continuous inputs~\cite{castillo2015higher,palosz2015laser,edwards2016adaptive,zhao2015finite,liu2015second}, which eliminate the chattering by hiding the switching in high-order terms or absorbing the switching via some techniques.
-\par
-Besides the issue on repressing the chattering, the fast convergence of the SMC scheme is also a hot subject.
-Normal linear sliding mode control takes two steps to solve a problem about the stability, namely, conducting the system states onto the prescript sliding manifold and driving these states to the origin along the manifold, and some accelerating operations usually occur in this two phases.
-The first step is said to be the approaching phase which usually requires the states converge to the desired manifold in finite time, and selecting suitable Lyapunov function and control parameters may accelerate this process; the second step is the sliding phase which is related to the designed manifold closely, and trivial manifold design techniques are able to guarantee the asymptotically convergence.
-For achieving a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and comparing with the sliding mode control design mentioned above, the most significant contributions of the terminal sliding mode is introducing the finite time convergence to the sliding phase to complete the global finite time convergence.
-Owing to the global finite time convergence, the terminal sliding mode control has been utilized to achieve the high precise control, i.e., in~\cite{li2015robust}, an adaptive TSM scheme controlled a $2$-link robotic manipulator to track the variable signal.
+designed a robust adaptive sliding mode method to ensure the asymptotically stability of a boost converter~\cite{oucheriah2013pwm}.
+Roughly speaking, the SMC scheme is competent for normal scientific missions, due to its insensitivity to parameteric uncertainties and external disturbances, however, there still exist some obstacles, such as noncontinuous switching inputs in high frequency and convergence speed design schemes~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some practical engineering applications~\cite{fridman2011sliding}.}
+
+\textcolor{red}{For alleviating the mentioned bad effects, many scientific researchers have presented remarkable achievements to promote the performance of the SMC scheme in last decade~\cite{zong2013quasi,santiesteban2013time,mu2015continuous,evangelista2013lyapunov,gonzalez2014chattering,dadras2012fractional,zhao2013output}.
+Among these methods, the high-order SMC and super-twisting SMC work in reducing the chattering to generate continuous inputs~\cite{castillo2015higher,palosz2015laser,edwards2016adaptive,zhao2015finite,liu2015second}.
+Besides the issue on repressing the chattering, the fast convergence of the SMC scheme becomes a hot subject recently.
+The normal linear SMC scheme completes the stabilization of the system dynamics.
+In the first step, the control inputs drive the system states onto the prescript sliding surfaces, and this stage is also called the reaching phase.
+Then the sliding mode dynamics work to drive the system states to the origins along the ideal surfaces in the second step, and this stage is usually called the sliding phase.
+The reaching phase  usually requires the states converge to the ideal sliding mode surfaces in finite time, and suitably selected Lyapunov function and control parameters may accelerate this process; the sliding phaseis related to the designed ideal sliding surfaces closely, and trivial design techniques are can guarantee the asymptotically stability.
+To achieve a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and comparing with the SMC design mentioned above, the most significant contributions of the TSM are introducing the finite time convergence to the sliding phase to complete the global finite time convergence.
+Moreover, the terminal SMC schemes have been utilized to achieve the high precise control, i.e., in~\cite{li2015robust}, an adaptive TSM scheme controlled a $2$-link robotic manipulator to track the variable signals.
 Feng et al.
-presented a global terminal sliding mode algorithm for manipulating the rigid robot, and produced the control design by using Lagrangian dynamic expression~\cite{feng2002non}.
-In~\cite{kamal2016continuous}, Kamal addressed a continuous homogeneous sliding mode algorithm for a perturbed second-order plant, and the algorithm could be regarded as a combination of terminal and super-twisting sliding-mode, providing a convergence control in finite time.
-\par
-According to the achievements mentioned above, one can find that the conventional terminal sliding mode manifold design techniques are similar, since they are all based on the single variable finite time control, in another words, the sliding mode dynamics only involves the individual variable and its derivative essentially~\cite{mu2016switching}.
+presented a novel Lagrangian dynamic expression for the the rigid robot, and applied the global TSM control law to manipulate the robotic dynamics ~\cite{feng2002non}.
+In~\cite{kamal2016continuous}, Kamal addressed a continuous homogeneous sliding mode algorithm for a perturbed second-order plant, and the algorithm could be regarded as a combination of TSM and super-twisting sliding mode schemes.}
+
+\textcolor{red}{Notably, the conventional TSM surface design techniques are similar, since the surfaces are all designed for the single variable based on the finite time control theory, in another words, only the individual variable and its derivative are concerned on by most designers~\cite{mu2016switching}.
 This nature makes the TSM scheme become an individual control subsystem, which leads to the complicity of global convergence time in some extent.
-In this paper, an integral sliding mode manifold technique is proposed for finite time stability of the second-order system, and the novel manifold involves two variables to guarantee the integral finite time convergence, and the convergence time is obtained easily.
-Also, the nonsingularity and chattering suppression are available in the scheme.
-\par
-In this paper, a dual terminal sliding mode (DTSM) controller is proposed for a class of second-order nonlinear systems with disturbances and uncertainties.
-A novel DTSM manifold is exploited to fulfill the finite time convergence, and the approaching and sliding time are both able to be calculated directly.
-For coping with the underacutated issue, cooperating with the hierarchical sliding surface design methodology, we develop a hierarchical dual terminal sliding mode (HDTSM) control.
-A modified DTSM (MDTSM) control scheme is presented to stabilize the motion of the $n$-link robotic manipulators.
-The remained paper is organized as follows: Section~\ref{sec:2} introduces a DTSM scheme for a class of second-order system, and the finite time convergence of the approaching and sliding phase is verified.
-In addition, we add performance parameters for improving the DTSM scheme to obtain the MDTSM scheme, and the newly presented method has a better performance in theoretical analysis; for stabilizing the underactuated system, the HDTSM design is developed as well in this section.
-In Section~\ref{sec:3}, the MDTSM is applied to the motion regulation of the $n$-link robotic  manipulator, and the stability analysis is also carried out.
-Section~\ref{sec:4} exhibits the simulation results, and finally the conclusion is assigned in Section~\ref{sec:5}.
-\section{Dual terminal sliding mode control}\label{sec:2}
+In this paper, an integral sliding mode surface design technique breaks the barriers mentioned above, and the novel surface includes two designed variables to guarantee the integral finite time convergence.
+Moreover, nonsingularities of the TSM scheme, chattering suppressions, underactuated applications and input limitations are also considered in the scheme.}
+
+\textcolor{red}{In this paper, a dual TSM (DTSM) controller is proposed for a class of second-order nonlinear systems with disturbances and uncertainties.
+A novel DTSM surface is exploited to achieve the finite time convergence, and the reaching and sliding times can both be calculated directly.
+For coping with the underacutated issue, cooperating with the hierarchical sliding surface design methodology, we develop a hierarchical dual TSM (HDTSM) control to ensure the rigorous stability analyses.
+A modified DTSM (MDTSM) control scheme is presented to regulate the motion of the $n$-link robotic manipulators, and the case subjected to input limitations is also taken into consideration.
+The remained paper is organized as follows: Section~\ref{sec:2} introduces a DTSM scheme for a class of second-order system, and the finite time convergences of the reaching and sliding phase are verified.
+Furthermore, we design extra performance parameters to obtain the MDTSM scheme, and the newly presented method has a better performance in theoretical analyses; for stabilizing the underactuated system, the HDTSM design is also developed in this section.
+In Section~\ref{sec:3}, the MDTSM is applied to the motion control system of the $n$-link robotic  manipulator, and the stability analysis is also carried out.
+Section~\ref{sec:4} exhibits the simulation results, and finally the conclusion is assigned in Section~\ref{sec:5}.}
+\section{Dual terminal SMC}\label{sec:2}
 Consider a second-order nominal nonlinear system:
@@
 where $\bm x = [x_1,x_2,x_3,x_4]^T$ is the system vector state; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$; $u_i(t)$, $i=1,2$ stands for the scalar input; $g_i(\bm x,t)$, $i=1,2$  is defined as a bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0, i=1,2$, meaning the uncertainty and disturbance of the system.
-For the system mentioned above, we can establish a desired dual terminal sliding manifold as:
+For the system mentioned above, we can establish a desired dual terminal sliding surface as:
 \begin{align}
@@
 s_1 &= x_2+\vert x_1\vert^{\alpha} sgn(x_1)+x_1^3(t)-x_3\\
-s_2 &= x_4+\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3(t)+x_1,\label{eq:dual sliding manifold}
+s_2 &= x_4+\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3(t)+x_1,\label{eq:dual sliding surface}
 \end{split}
@@
 where $sgn(x)$ is the sign function, and $0<\alpha<1$ is a positive constant.
-For the sake of simplicity, the symbol $t$ is usually omitted in this paper, which does not cause any confusion, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding manifold $\bm s$ is often abbreviated to $\bm s$.\par
+For the sake of simplicity, the symbol $t$ is usually omitted in this paper, which does not cause any confusion, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding surface $\bm s$ is often abbreviated to $\bm s$.\par
 There exist two lemmas about the finite convergence theory, providing convergence forms which contribute to the verification of the finite time convergence about the DTSM control.
@@
 \dot x_1&=-\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2\\
-\dot x_2&=-\vert x_2\vert^\alpha sgn(x_3)-x_2^3-x_1,\label{eq:normal sliding manifold}
+\dot x_2&=-\vert x_2\vert^\alpha sgn(x_3)-x_2^3-x_1,\label{eq:normal sliding surface}
 \end{split}
@@
 \end{align}
-where the definitions of  $t_s$, $t_0$, $\alpha$ are similar to Lemma \ref{lemma:1}. Introducing the amplitude scalar $d$ into the Eqs.~(\ref{eq:normal sliding manifold}) obtains  more normal forms:
+where the definitions of  $t_s$, $t_0$, $\alpha$ are similar to Lemma \ref{lemma:1}. Introducing the amplitude scalar $d$ into the Eqs.~(\ref{eq:normal sliding surface}) obtains  more normal forms:
 \begin{align}
 \dot x_1&=-d(\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2)\\
-\dot x_2&=-d(\vert x_2\vert^\alpha sgn(x_2)-x_2^3-x_1),\label{eq:more normal sliding manifold}
+\dot x_2&=-d(\vert x_2\vert^\alpha sgn(x_2)-x_2^3-x_1),\label{eq:more normal sliding surface}
 \end{align}
@@
 For stabilization of the second-order system shown as~Eq. (\ref{eq:second-order system}), DTSM control inputs are addressed according the following theorem.
-\begin{mythm}\label{theorem:1}Dual Terminal Sliding Mode Control Design.
-The second-order system (\ref{eq:second-order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq.
-(\ref{eq:dual sliding manifold}) in finite time.
-The states of the system will converge to zero along the manifold $\bm s=0$ in finite time, if the inputs are designed as follows:
+\begin{mythm}\label{theorem:1}Dual Terminal SMC Design.
+The second-order system (\ref{eq:second-order system}) will reach the desired surface $\bm s = 0$ shown in~Eq.
+(\ref{eq:dual sliding surface}) in finite time.
+The states of the system will converge to zero along the surface $\bm s=0$ in finite time, if the inputs are designed as follows:
 \begin{align}
@@
 \end{align*}
-Hence, the system (\ref{eq:second-order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergence time is calculated according to the finite time convergence theory.\par
-Once the system (\ref{eq:second-order system}) reaches the desired manifold~(\ref{eq:dual sliding manifold}), the whole system is handled by the reduced system:
+Hence, the system (\ref{eq:second-order system}) asymptotically converges to the desired surface (\ref{eq:dual sliding surface}), and incidentally the convergence time is calculated according to the finite time convergence theory.\par
+Once the system (\ref{eq:second-order system}) reaches the desired surface~(\ref{eq:dual sliding surface}), the whole system is handled by the reduced system:
 \begin{align*}
@@
 \end{align*}\par
-The total convergence time can be calculated by dividing the convergence into two phases with respect to the relation between the system and the manifold, namely, the approaching phase and the sliding phase, and specifically, according to Lemma \ref{lemma:2}, the total finite convergence time $t_f$ is calculated from:
+The total convergence time can be calculated by dividing the convergence into two phases with respect to the relation between the system and the surface, namely, the reaching phase and the sliding phase, and specifically, according to Lemma \ref{lemma:2}, the total finite convergence time $t_f$ is calculated from:
 \begin{align}
@@
 where $\hat V(t) = \frac{x_1^2+x_3^2}{2}$ is the Lyapunov function describing the convergence motion of the reduced system.
-The approaching and sliding time are defined as $t_r$ and $t_s$, respectively.
+The reaching and sliding time are defined as $t_r$ and $t_s$, respectively.
 This completes the proof.
 \end{proof}
-On the basis of Theorem \ref{theorem:1}, we proceed to develop the parameters in the manifold to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:second-order system}), and furthermore this method makes the design of the manifold more flexible.
-Consider the system~(\ref{eq:second-order system}) with the manifold $\bm s = [s_1,s_2]^T$, the details of which are described by following expressions:
+On the basis of Theorem \ref{theorem:1}, we proceed to develop the parameters in the surface to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:second-order system}), and furthermore this method makes the design of the surface more flexible.
+Consider the system~(\ref{eq:second-order system}) with the surface $\bm s = [s_1,s_2]^T$, the details of which are described by following expressions:
 \begin{align}
@@
 s_1 &= x_2+\gamma(\vert x_1\vert^{\alpha} sgn(x_1)+x_1^3(t))-\lambda x_3\\
-s_2 &= x_4+\gamma(\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3(t))+\lambda x_1,\label{eq:modified dual sliding manifold}
+s_2 &= x_4+\gamma(\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3(t))+\lambda x_1,\label{eq:modified dual sliding surface}
 \end{split}
 \end{align}
-where $\gamma$ is a positive constant and $\lambda\in R$ is a regulable parameter. Hence, the modified dual terminal sliding mode control inputs are formed in the following theorem.
-\begin{mythm}\label{theorem:2}Modified Dual Terminal Sliding Mode Control Design.
-The second-order system (\ref{eq:second-order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq.
-(\ref{eq:modified dual sliding manifold}) in finite time.
-The states of the system will converge to zero along the manifold $\bm s=0$ in finite time, if the inputs are designed as follows:
+where $\gamma$ is a positive constant and $\lambda\in R$ is a regulable parameter. Hence, the modified dual terminal SMC inputs are formed in the following theorem.
+\begin{mythm}\label{theorem:2}Modified Dual Terminal SMC Design.
+The second-order system (\ref{eq:second-order system}) will reach the desired surface $\bm s = 0$ shown in~Eq.
+(\ref{eq:modified dual sliding surface}) in finite time.
+The states of the system will converge to zero along the surface $\bm s=0$ in finite time, if the inputs are designed as follows:
 \begin{align}
@@
 \end{proof}
-After introducing the parameters $\lambda$ and $\gamma$ into the DTSM scheme, the performances of the approaching and sliding phases become regulatable, meaning that these parameters can adjust the convergence time analytically.
+After introducing the parameters $\lambda$ and $\gamma$ into the DTSM scheme, the performances of the reaching and sliding phases become regulatable, meaning that these parameters can adjust the convergence time analytically.
 Although $\lambda$ does not appear in Eq.~(\ref{eq:total convergence time}), the establishment of $V(t_0)$ involves it when the state $\bm x(t_0)$ has been fixed.
-Strictly speaking, it affects the approaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V(t)=\bm s^T(t)\bm s = 0,\forall t\ge t_r$.
-Admittedly, the variety of $\lambda$ is only modestly helpful in this approaching time regulation due to its limited effect on $V(t_0)$.
-$\eta$ is said to be an ''approaching speed'' according to its function, a suitable selection of which will adjust the approaching time as desired in some extent.
-Hence, $\lambda$ cooperates with $\eta$ to manage the approaching status, and by utilizing the similar analysis, owing to $\gamma$ adjusting the speed of sliding phase, it's able to be defined as the management parameter of the sliding status.
+Strictly speaking, it affects the reaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V(t)=\bm s^T(t)\bm s = 0,\forall t\ge t_r$.
+Admittedly, the variety of $\lambda$ is only modestly helpful in this reaching time regulation due to its limited effect on $V(t_0)$.
+$\eta$ is said to be an ''reaching speed'' according to its function, a suitable selection of which will adjust the reaching time as desired in some extent.
+Hence, $\lambda$ cooperates with $\eta$ to manage the reaching status, and by utilizing the similar analysis, owing to $\gamma$ adjusting the speed of sliding phase, it's able to be defined as the management parameter of the sliding status.
 \begin{myrem}
@@
 \end{myrem}
-The finite convergence of the DTSM and MDTSM scheme has been verified clearly, but similar to the conventional terminal sliding mode control, there exists another obstacle in the design mentioned above, namely, the issue of the singularity in control inputs.
+The finite convergence of the DTSM and MDTSM scheme has been verified clearly, but similar to the conventional terminal SMC, there exists another obstacle in the design mentioned above, namely, the issue of the singularity in control inputs.
 Essentially, the singularity occurs in Eq.~(\ref{eq:modified input}) when $x_1=0$ but $x_2\neq 0$ in $u_1$ (the phenomena happens to $u_2$ under the same condition).
@@
 \begin{mylem}\label{lemma:3}
-Considering the second-order system (\ref{eq:second-order system}), the terminal sliding mode manifold is designed as:
+Considering the second-order system (\ref{eq:second-order system}), the TSM surface is designed as:
 \begin{align*}
@@
 \end{myas}
-Thanks to the above assumption, we give out the adaptive dual terminal sliding mode control scheme.
-\begin{mythm}
+Thanks to the above assumption, we give out the adaptive dual terminal SMC scheme.
+\begin{mythm}\label{thm:4}
 Considering the nominal second-order system subjected to the input limitation~(\ref{eq:second-order system subjected to limitation}), the inputs $u_i$,$i=1,2$ can be designed as
@@
 \end{align}
-with $\nu_i>1$ and $\omega_i(0)>0$, such that the trajectories of the system states can converge to the sliding surfaces in Eq.~(\ref{eq:modified dual sliding manifold}).
+with $\nu_i>1$ and $\omega_i(0)>0$, such that the trajectories of the system states can converge to the sliding surfaces in Eq.~(\ref{eq:modified dual sliding surface}).
 \end{mythm}
@@
 These underactuated systems are frequently used in the scientific field, such as flexible manipulators, overhead crane and underwater robots, because fewer actuators may decrease the mass and save the energy as well.
-Cooperating with the hierarchical sliding mode methodology, the manifold design scheme proposed above is able to control this kind of systems \cite{wang2004design}.
-We give the hierarchical dual terminal sliding mode design directly.
+Cooperating with the hierarchical sliding mode methodology, the surface design scheme proposed above is able to control this kind of systems \cite{wang2004design}.
+We give the hierarchical dual TSM design directly.
 \begin{mythm}
@@
 \end{align}
-where the condition of variables is same to the system~(\ref{eq:second-order system}). Construct the manifold as:
+where the condition of variables is same to the system~(\ref{eq:second-order system}). Construct the surface as:
 \begin{align}
@@
 \end{align}
-As $\vert g_i(\bm x)\vert<l_i$ exists, a big enough $\eta_u$ may be chosen to guarantee the reaching condition of the manifold $S$.
+As $\vert g_i(\bm x)\vert<l_i$ exists, a big enough $\eta_u$ may be chosen to guarantee the reaching condition of the surface $S$.
 The proof of the stability of the desired sliding surfaces $s_1$ and $s_2$ is same to the one in \cite{wang2004design}, and omitted here.
@@
 \end{proof}
-\section{Modified Dual terminal sliding mode control for rigid manipulators}\label{sec:3}
+\section{Modified Dual terminal SMC for rigid manipulators}\label{sec:3}
 In this section, the MDTSM control is proposed for the rigid $2$-link robotic manipulator
@@
 \begin{mythm}\label{theorem:4}
-For the rigid $2$-link manipulator~(\ref{eq:lagrangian system}), if the dual terminal sliding mode manifold is selected as
+For the rigid $2$-link manipulator~(\ref{eq:lagrangian system}), if the dual TSM surface is selected as
 \begin{align}
-\bm s = \dot{\bm \varepsilon}+C_\gamma\lceil\bm{sgn}^\alpha(\bm \varepsilon)+\bm\varepsilon^3\rfloor+C_\lambda{\bm\varepsilon},\label{eq:lagrangian manifold}
+\bm s = \dot{\bm \varepsilon}+C_\gamma\lceil\bm{sgn}^\alpha(\bm \varepsilon)+\bm\varepsilon^3\rfloor+C_\lambda{\bm\varepsilon},\label{eq:lagrangian surface}
 \end{align}
@@
 \end{align}
-and $\Vert\bm s\Vert\neq 0$, hence, the Lyapunov stability has been proved, meaning that the system will reach the desired manifold~(\ref{eq:lagrangian manifold}) in finite time.
+and $\Vert\bm s\Vert\neq 0$, hence, the Lyapunov stability has been proved, meaning that the system will reach the desired surface~(\ref{eq:lagrangian surface}) in finite time.
 Once the reaching condition is satisfied, one can achieve a reduced system by substituting $\bm s = 0$ into the system~(\ref{eq:lagrangian system}).
-It owns the form, similar to Eq.~(\ref{eq:normal sliding manifold}), and therefore, adopting Theorem \ref{theorem:2} drives the reduced system converging to the origin in finite time.
+It owns the form, similar to Eq.~(\ref{eq:normal sliding surface}), and therefore, adopting Theorem \ref{theorem:2} drives the reduced system converging to the origin in finite time.
 The proof is completed.
@@
 At this point, the MDTSM scheme for $2$-link robotic manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator.
-Consider a $n$-link robotic manipulator in which $n$ is an even number, and the desired sliding manifold follows
+Consider a $n$-link robotic manipulator in which $n$ is an even number, and the desired sliding surface follows
 \begin{align}
@@
 Referring to Theorem \ref{theorem:4}, it's easy to obtain the MDTSM input for the even $n$-link manipulator.
-Essentially, this technique requires that the sliding mode manifold has to consist of $n/2$ pairs of individual sliding surfaces, in another words, this design for the manifold can be regarded as a work for yielding manifolds of the $n/2$ sub-systems.\par
-Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension is able to be excluded by using conventional terminal sliding mode control, which results in that the remained $n-1$-link manipulator can be controlled by the proposed MDTSM scheme.
+Essentially, this technique requires that the sliding mode surface has to consist of $n/2$ pairs of individual sliding surfaces, in another words, this design for the surface can be regarded as a work for yielding surfaces of the $n/2$ sub-systems.\par
+Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension is able to be excluded by using conventional terminal SMC, which results in that the remained $n-1$-link manipulator can be controlled by the proposed MDTSM scheme.
 \end{myrem}
@@
 For handling the chattering, the $sign(x)$ is replaced with $sat(x,\delta)$, and the bounded value $\delta$ is determined according to actual needs.
+\textcolor{red}{Incorporating the adaptive MDTSM technique, the manipulator dynamics subjected to the input limitation can also been stabilized as desired.}
 \end{myrem}
@@
 \end{align*}
-and hence, based on the analysis in Theorem~\ref{theorem:1}, $l_1>0.1$ and $l_2>0.8$ are determined accordingly to guarantee the reaching condition of the desired sliding manifold.
+and hence, based on the analysis in Theorem~\ref{theorem:1}, $l_1>0.1$ and $l_2>0.8$ are determined accordingly to guarantee the reaching condition of the desired sliding surface.
 Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation second-order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
 The system is supposed to be conducted to the desired state $\bm x_d=(0,0,0,0)$ from a prescript state $\bm x_0=(1.2,1.2,1.2,1.2)$.
-Admittedly, this prescript condition leads to a lager initial approaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding manifold, therefore a large approaching speed $k_i$ is required correspondingly.
+Admittedly, this prescript condition leads to a lager initial reaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding surface, therefore a large reaching speed $k_i$ is required correspondingly.
 The control parameters are chosen as: $\alpha = 0.6$, $\lambda = 0.5$, $\gamma = 3$ and $k = 20$.
-Besides the large approaching speed selected, $\gamma$ accelerates the sliding phase indirectly.
+Besides the large reaching speed selected, $\gamma$ accelerates the sliding phase indirectly.
 Therefore the design of the MDTSM controller for the system~(\ref{eq:simulation second-order system}) is finished, and the corresponding simulation results are illustrated from Figure~\ref{Figure:2} to Figure~\ref{Figure:3}.\par
@@
 Figure~\ref{Figure:9} shows the state response curves of the overhead crane system controlled using the HDSM control scheme, and the results show that the controller stabilize the displacement at $6s$ approximately, though the disturbance exists in the system.
-One can find that the swing angle is fluctuating in a fairly small range, the boundary of which is not more than $1\times 10^-3rad$, hence this phenomena is reasonable and also occurs in the stable hierarchical sliding mode control \cite{wang2004design}.
+One can find that the swing angle is fluctuating in a fairly small range, the boundary of which is not more than $1\times 10^-3rad$, hence this phenomena is reasonable and also occurs in the stable hierarchical SMC \cite{wang2004design}.
 \begin{figure}
@@
 In order to ensure the stability and a fast convergence speed, the control parameters are chosen conservatively to make the manipulator track the desired attitude in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $k = 150$.
-The terminal sliding mode control (TSM) scheme, as a comparison, is also implemented to regulate the behavior of the manipulator:
+The terminal SMC (TSM) scheme, as a comparison, is also implemented to regulate the behavior of the manipulator:
 \begin{align}
@@
  \textcolor{red}{The simulation results are demonstrated in Figure~\ref{Figure:6} and Figure~\ref{Figure:7}, which plot the trajectories of joints of the manipulator~(\ref{eq:manipulator}) regulated by adopting the MDTSM controller.
-In Figure~\ref{Figure:6}, we can find that the error between the variable desired signal and the joint angle $q_1$ keeps decreasing frome the initial state, and the two trajectories reach a confluence at about $3s$, which means that $q_1$ has absolutely tracked the variable desired signal, and the similar conclusion about $q_2$ can also be obtained from the results in Figure~\ref{Figure:7}.
+In Figure~\ref{Figure:6}, the error between the variable desired signal and the joint angle $q_1$ keeps decreasing frome the initial state, and the two trajectories reach a confluence at about $3s$, which means that $q_1$ has absolutely tracked the variable desired signal, and the similar conclusion about $q_2$ can also be obtained from the results in Figure~\ref{Figure:7}.
 Taken as a whole, the control system completes the tracking mission at about $3.2s$ from the prescript initial conditions, which performs the smoothly tracking motion subjected to the variable desired signals.}
@@
 \end{figure}
-Another important issue that we always meet in engineering applications, is the actuator constrains 
+\textcolor{red}{Another important issue that we always meet in engineering applications, is the actuator constraint due to the physical limitation, which can be regarded as the input limitation problem shown in Eq.~(\ref{eq:second-order system subjected to limitation}).
+Consider the case that there exist the input limitation in the manipulator model~(\ref{eq:manipulator}), and without loss of generality, the maximum torque of the joint is $50Nm$.
+Reviewing the joint 1 torque shown in enlarged details of  Figure~\ref{Figure:torque}, we can find that the torque exceeds the reasonable torque upper limit $50Nm$ around $2.3s$.
+Hence, to overcom this issue, the adaptive MDTSM controller is applied to eliminate the effect of the input limitation and to guarantee the rigorous stability analyses of the manipulator dynamics.
+The results shown in Figure~\ref{Figure:limitation_torque} indicate that the joint torques are limited in the region $[-50,50]Nm$ from $0.2s$ to $0.4s$, while in the Figure~\ref{Figure:limitation_q} the trajectories of the manipulator dynamics are still under control.
+Moveover the boundary layer technique works after $0.4$ and generates continuous torques in the subsequent time.
+In particular, compared to the results from Figure~\ref{Figure:4} and Figure~\ref{Figure:torque}, we can see that the rise time of the adaptive MDTSM controller is less, and the incontinuous joint torques disappear earlier.
+Hence, we can conclude that the proposed adaptive MDTSM controller can regulate the joints of the manipulator subjectd to the input limitation.}
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth]{paper3_fig_limitation_q.eps}
+\caption{Trajectories of manipulator dynamics subjected to the input limitation}
+\label{Figure:limitation_q}
+\end{figure}
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth]{paper3_fig_limitation_torque.eps}
+\caption{Trajectories of joint torques subjected to the input limitation}
+\label{Figure:limitation_torque}
+\end{figure}
 \section{Conclusion}\label{sec:5}
 A DTSM control for n-link robotic manipulator has been presented.
-The method integrates two individual subsystems as a unity, then builds the manifold and input for it to complete the controller design.
-The control scheme is able to guarantee the reaching condition of the desired sliding manifold, meanwhile the system states converge to the origin along the desired manifold.
+The method integrates two individual subsystems as a unity, then builds the surface and input for it to complete the controller design.
+The control scheme is able to guarantee the reaching condition of the desired sliding surface, meanwhile the system states converge to the origin along the desired surface.
 Also, the entire convergence time can be calculated accordingly.
@@
 For dealing with the under actuated characteristics which may appear in the system, the HDTSM control is derived, and the overhead crane example verifies its effectiveness.
-However, the control parameters selection is still a challenge especially in the HDTSM scheme, and we will effort to excavate a full order dual terminal sliding mode methodology in the future for removing the obstacle caused by parameters essentially.
+However, the control parameters selection is still a challenge especially in the HDTSM scheme, and we will effort to excavate a full order dual TSM methodology in the future for removing the obstacle caused by parameters essentially.
 \section{Acknowledgment}

### 2016-11-12 paper3_manuscript.tex
20161112

@@
 
-\textcolor{red}{In this paper, a dual TSM (DTSM) controller is proposed for a class of second-order nonlinear systems with disturbances and uncertainties.
-A novel DTSM surface is exploited to achieve the finite time convergence, and the reaching and sliding times can both be calculated directly.
-For coping with the underacutated issue, cooperating with the hierarchical sliding surface design methodology, we develop a hierarchical dual TSM (HDTSM) control to ensure the rigorous stability analyses.
+\textcolor{red}{In this paper, the dual TSM (DTSM) control scheme is proposed for a class of second-order nonlinear systems with disturbances and uncertainties.
+The novel DTSM surface is exploited to achieve the finite time convergence, and the reaching and sliding times can both be calculated directly.
+For coping with the underacutated issue, cooperating with the hierarchical sliding surface design methodology, we combine the hierarchical SMC scheme with the DTSM scheme to develop a hierarchical dual TSM (HDTSM) control law to ensure the rigorous stability analyses.
 A modified DTSM (MDTSM) control scheme is presented to regulate the motion of the $n$-link robotic manipulators, and the case subjected to input limitations is also taken into consideration.
-The remained paper is organized as follows: Section~\ref{sec:2} introduces a DTSM scheme for a class of second-order system, and the finite time convergences of the reaching and sliding phase are verified.
-Furthermore, we design extra performance parameters to obtain the MDTSM scheme, and the newly presented method has a better performance in theoretical analyses; for stabilizing the underactuated system, the HDTSM design is also developed in this section.
-In Section~\ref{sec:3}, the MDTSM is applied to the motion control system of the $n$-link robotic  manipulator, and the stability analysis is also carried out.
+The remained paper is organized as follows: Section~\ref{sec:2} introduces the DTSM scheme, and the finite time convergences of the reaching and sliding phase are discussed.
+Furthermore, we provide the DTSM scheme with extra design parameters to obtain the MDTSM scheme, which performs better in theoretical analyses; for stabilizing underactuated systems, the HDTSM design is also developed in this section.
+In Section~\ref{sec:3}, the MDTSM is applied to the motion control system of the $n$-link robotic  manipulator, and the stability analyses are also carried out.
 Section~\ref{sec:4} exhibits the simulation results, and finally the conclusion is assigned in Section~\ref{sec:5}.}
@@
 \end{align}
-where $\bm x = [x_1,x_2,x_3,x_4]^T$ is the system vector state; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$; $u_i(t)$, $i=1,2$ stands for the scalar input; $g_i(\bm x,t)$, $i=1,2$  is defined as a bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0, i=1,2$, meaning the uncertainty and disturbance of the system.
-For the system mentioned above, we can establish a desired dual terminal sliding surface as:
+where $\bm x = [x_1,x_2,x_3,x_4]^T$ is the system state vector ; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$ and $t$; $u_i(t)$, $i=1,2$ stands for the system input; $g_i(\bm x,t)$, $i=1,2$  is defined as the bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0, i=1,2$, meaning uncertainties and disturbances.
+For the system mentioned above, we can design the desired DTSM surface as:
 \begin{align}
@@
 s_1 &= x_2+\vert x_1\vert^{\alpha} sgn(x_1)+x_1^3(t)-x_3\\
-s_2 &= x_4+\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3(t)+x_1,\label{eq:dual sliding surface}
+s_2 &= x_4+\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3(t)+x_1.\label{eq:dual sliding surface}
 \end{split}
 \end{align}
-where $sgn(x)$ is the sign function, and $0<\alpha<1$ is a positive constant.
-For the sake of simplicity, the symbol $t$ is usually omitted in this paper, which does not cause any confusion, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding surface $\bm s$ is often abbreviated to $\bm s$.\par
-There exist two lemmas about the finite convergence theory, providing convergence forms which contribute to the verification of the finite time convergence about the DTSM control.
+\textcolor{red}{}$sgn(x)$ is the sign function, and $0<\alpha<1$ is a positive scalar.
+For the sake of simplicity, the symbol $t$ is usually omitted in this paper, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding surface $\bm s(t)$ is often abbreviated as $\bm s$.}
+
+There exist two lemmas facilitating the derivation of the finite time convergence about the DTSM scheme.
 \begin{mylem}
-As described in~\cite{moulay2006finite}, it's assumed that the continuous function $V(t)$ is positive-define, satisfying the following condition:
+As described in~\cite{moulay2006finite}, it's assumed that the continuous function $V(t)$ is positive definite, satisfying following conditions:
 \begin{align}
@@
 \end{align}
-and selecting $V(t) = \frac{x_1^2+x_2^2}{2}$ obtains the finite convergence time as follows~\cite{moulay2006finite}:
+and oen can select the Lyapunov function $V(t) = \frac{x_1^2+x_2^2}{2}$ to obtain the finite convergence time as follows~\cite{moulay2006finite}:
 %since $\vert x\vert-x^\alpha+\vert x\vert \ge 0,0<\alpha<1$
@@
 \end{align}
-where the definitions of  $t_s$, $t_0$, $\alpha$ are similar to Lemma \ref{lemma:1}. Introducing the amplitude scalar $d$ into the Eqs.~(\ref{eq:normal sliding surface}) obtains  more normal forms:
+where the definitions of  $t_s$, $t_0$, $\alpha$ are similar to Lemma \ref{lemma:1}. Introducing the scalar $d$ into the Eq.~(\ref{eq:normal sliding surface}) obtains:
 \begin{align}
@@
 \end{mylem}
-For stabilization of the second-order system shown as~Eq. (\ref{eq:second-order system}), DTSM control inputs are addressed according the following theorem.
-\begin{mythm}\label{theorem:1}Dual Terminal SMC Design.
-The second-order system (\ref{eq:second-order system}) will reach the desired surface $\bm s = 0$ shown in~Eq.
-(\ref{eq:dual sliding surface}) in finite time.
-The states of the system will converge to zero along the surface $\bm s=0$ in finite time, if the inputs are designed as follows:
+\textcolor{red}{For stabilization of the second-order system shown as~Eq. (\ref{eq:second-order system}), DTSM control inputs are addressed according the following to theorem.}
+\begin{mythm}\label{theorem:1}DTSM Controller Design.
+The states of the system~(\ref{eq:second-order system}) will converge to origins along the surface $\bm s=0$ in finite time, if the inputs are designed as follows:
 \begin{align}
@@
 
-Consider the Lyapunov function $V=\frac{1}{2}{\bm s}^T\bm s$, the derivative of which with respect to time $\dot V = {\bm s}^T \bm {\dot s}$ follows
+Considering the Lyapunov function $V=\frac{1}{2}{\bm s}^T\bm s$, its derivative $\dot V$ can be written as
 \begin{align}
@@
 \end{align*}
-Hence, the system (\ref{eq:second-order system}) asymptotically converges to the desired surface (\ref{eq:dual sliding surface}), and incidentally the convergence time is calculated according to the finite time convergence theory.\par
-Once the system (\ref{eq:second-order system}) reaches the desired surface~(\ref{eq:dual sliding surface}), the whole system is handled by the reduced system:
+Hence, the system (\ref{eq:second-order system}) converges to the desired surface (\ref{eq:dual sliding surface}), and incidentally the convergence time can be calculated according to the finite time convergence theory.\par
+Once the system (\ref{eq:second-order system}) reaches the desired surface~(\ref{eq:dual sliding surface}), the entire system states are handled by the reduced system:
 \begin{align*}
@@
 \end{align*}\par
-The total convergence time can be calculated by dividing the convergence into two phases with respect to the relation between the system and the surface, namely, the reaching phase and the sliding phase, and specifically, according to Lemma \ref{lemma:2}, the total finite convergence time $t_f$ is calculated from:
+\textcolor{red}{The total convergence time can be calculated by dividing the convergence into two phases with respect to the relation of the system states and the DTSM surface, namely, the reaching phase and the sliding phase.
+Hence, according to Lemma \ref{lemma:2}, the theoretical total finite convergence time $t_f$ can be calculated from:
 \begin{align}
@@
 \end{align}
-where $\hat V(t) = \frac{x_1^2+x_3^2}{2}$ is the Lyapunov function describing the convergence motion of the reduced system.
-The reaching and sliding time are defined as $t_r$ and $t_s$, respectively.
-This completes the proof.
+where $\hat V(t) = \frac{x_1^2+x_3^2}{2}$ is the Lyapunov function selected for the reduced system.
+$t_r$ and $t_s$ stand for the reaching time and the sliding time, respectively.
+This completes the proof.}
 \end{proof}
-On the basis of Theorem \ref{theorem:1}, we proceed to develop the parameters in the surface to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:second-order system}), and furthermore this method makes the design of the surface more flexible.
+On the basis of Theorem \ref{theorem:1}, we proceed to develop the parameters in the surface design to improve the performance, and furthermore this modified method makes the design process more flexible.
 Consider the system~(\ref{eq:second-order system}) with the surface $\bm s = [s_1,s_2]^T$, the details of which are described by following expressions:

### 2016-11-13 paper3_manuscript.tex
20161113

@@
 \begin{frontmatter}
-\title{A New Dual Terminal SMC Design For Rigid Robotic Manipulator}
+\title{A New Dual Terminal Sliding Mode Control Design For Rigid Robotic Manipulator}
 \author{Zhiqiang Ma}
@@
 This paper proposes a dual terminal SMC scheme for the rigid robotic manipulator.
-\textcolor{red}{As a signiﬁcant novelty, the presented design technique integates the individual sliding mode surfaces to achieve the finite time convergence of overall system states by utilizing specially designed construct, and accordingly the convergence time for the entire system is easily obtained due to the integral design.
+\textcolor{red}{As a signiﬁcant novelty, the presented design technique integates the individual SM surfaces to achieve the finite time convergence of overall system states by utilizing specially designed construct, and accordingly the convergence time for the entire system is easily obtained due to the integral design.
 The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue are solved by introducing the hierarchical methodology into the basic dual SMC scheme.
-We combine the adaptive technique with the proposed method to eliminate the bad effect caused by the input limitation in the rigious stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the rigid robotic manipulator.
+Combining the adaptive technique with the proposed method eliminates the adverse effect caused by the input limitation in the rigious stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the rigid robotic manipulator.
 Simulation results validate the theoretical analyses about the proposed method.
@@
 Then the sliding mode dynamics work to drive the system states to the origins along the ideal surfaces in the second step, and this stage is usually called the sliding phase.
-The reaching phase  usually requires the states converge to the ideal sliding mode surfaces in finite time, and suitably selected Lyapunov function and control parameters may accelerate this process; the sliding phaseis related to the designed ideal sliding surfaces closely, and trivial design techniques are can guarantee the asymptotically stability.
+The reaching phase  usually requires the states converge to the ideal sliding mode (SM) surfaces in finite time, and suitably selected Lyapunov function and control parameters may accelerate this process; the sliding phaseis related to the designed ideal sliding surfaces closely, and trivial design techniques are can guarantee the asymptotically stability.
 To achieve a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and comparing with the SMC design mentioned above, the most significant contributions of the TSM are introducing the finite time convergence to the sliding phase to complete the global finite time convergence.
@@
 This nature makes the TSM scheme become an individual control subsystem, which leads to the complicity of global convergence time in some extent.
-In this paper, an integral sliding mode surface design technique breaks the barriers mentioned above, and the novel surface includes two designed variables to guarantee the integral finite time convergence.
+In this paper, an integral SM surface design technique breaks the barriers mentioned above, and the novel surface includes two designed variables to guarantee the integral finite time convergence.
 Moreover, nonsingularities of the TSM scheme, chattering suppressions, underactuated applications and input limitations are also considered in the scheme.}
@@
 \section{Dual terminal SMC}\label{sec:2}
-Consider a second-order nominal nonlinear system:
+Consider a nominal second-order nonlinear system:
 \begin{align}
@@
 \end{align}
-where $\bm x = [x_1,x_2,x_3,x_4]^T$ is the system state vector ; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$ and $t$; $u_i(t)$, $i=1,2$ stands for the system input; $g_i(\bm x,t)$, $i=1,2$  is defined as the bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0, i=1,2$, meaning uncertainties and disturbances.
+where $\bm x = [x_1,x_2,x_3,x_4]^T$ is the system state vector ; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$ and $t$; $u_i$, $i=1,2$ stands for the system input; $g_i(\bm x,t)$, $i=1,2$  is defined as the bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0, i=1,2$, meaning uncertainties and disturbances.
 For the system mentioned above, we can design the desired DTSM surface as:
@@
 \begin{split}
-s_1 &= x_2+\vert x_1\vert^{\alpha} sgn(x_1)+x_1^3(t)-x_3\\
-s_2 &= x_4+\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3(t)+x_1.\label{eq:dual sliding surface}
+s_1 &= x_2+\vert x_1\vert^{\alpha} sgn(x_1)+x_1^3-x_3\\
+s_2 &= x_4+\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3+x_1.\label{eq:dual sliding surface}
 \end{split}
 \end{align}
-\textcolor{red}{}$sgn(x)$ is the sign function, and $0<\alpha<1$ is a positive scalar.
+\textcolor{red}{$sgn(x)$ is the sign function, and $0<\alpha<1$ is a positive scalar.
 For the sake of simplicity, the symbol $t$ is usually omitted in this paper, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding surface $\bm s(t)$ is often abbreviated as $\bm s$.}
@@
 \begin{mylem}
-As described in~\cite{moulay2006finite}, it's assumed that the continuous function $V(t)$ is positive definite, satisfying following conditions:
+As described in~\cite{moulay2006finite}, it's assumed that the continuous function $V$ is positive definite, satisfying following conditions:
 \begin{align}
-\dot V(t)\le -dV^\beta(t)\quad\forall t\ge t_0, V(t_0)\ge 0,
+\dot V\le -dV^\beta\quad\forall t\ge t_0, V(t_0)\ge 0,
 \end{align}
-where $d$ is a positive scalar, and $0<\beta<1$. Then the function $V(t)$ converges to the origin for any given $t_0$, and typically the finite convergence time $t_r$ can be given as follows:
+where $d$ is a positive scalar, and $0<\beta<1$. Then the function $V$ converges to the origin for any given $t_0$, and typically the finite convergence time $t_r$ can be given as follows:
 \begin{align}
@@
 \end{align}
-and oen can select the Lyapunov function $V(t) = \frac{x_1^2+x_2^2}{2}$ to obtain the finite convergence time as follows~\cite{moulay2006finite}:
+and oen can select the function $V = \frac{x_1^2+x_2^2}{2}$ to obtain the finite convergence time as follows~\cite{moulay2006finite}:
 %since $\vert x\vert-x^\alpha+\vert x\vert \ge 0,0<\alpha<1$
@@
 \end{mylem}
-\textcolor{red}{For stabilization of the second-order system shown as~Eq. (\ref{eq:second-order system}), DTSM control inputs are addressed according the following to theorem.}
+\textcolor{red}{For stabilization of the second-order system shown as~Eq.~(\ref{eq:second-order system}), DTSM control inputs are addressed according the following to theorem.}
 \begin{mythm}\label{theorem:1}DTSM Controller Design.
@@
 \begin{proof}
-\textcolor{red}{According to the equivalent control technique and the sliding surface reaching condition~\cite{Arie1993sliding}, the inputs can be design as
+\textcolor{red}{For the system~(\ref{eq:second-order system}) with the SM surface~(\ref{eq:dual sliding surface}), according to the equivalent control technique and the sliding surface reaching condition~\cite{Arie1993sliding}, the inputs can be designed as
 \begin{align}\begin{split}
@@
 \end{split}\end{align}
-are the eauivalent control inputs to ensure $\dot s_1 = 0$ and $\dot s_2=0$, respectively, with $u_i = u_{eqi}$, $i=1,2$.
-The switching inputs are designed as $u_{swi}=-b_i^{-1}k_isgn(s_i)$, $i=1,2$ to guarantee the finite time reaching conditions of the ideal sliding surface.}
+are the eauivalent control inputs, which ensure $\dot s_1 = 0$ and $\dot s_2=0$ with $u_i = u_{eqi}$, $i=1,2$.
+The switching inputs are designed as $u_{swi}=-b_i^{-1}k_isgn(s_i)$, $i=1,2$ to guarantee the finite time reaching conditions of the sliding surface.}
 
-Considering the Lyapunov function $V=\frac{1}{2}{\bm s}^T\bm s$, its derivative $\dot V$ can be written as
+Considering the Lyapunov function $V=\frac{1}{2}{\bm s}^T\bm s$, its derivative can be written as
 \begin{align}
@@
 \end{align}
-Substituting inputs (\ref{eq:DSM input}) in~Eq. (\ref{eq:V_1}) yields
+Substituting inputs (\ref{eq:DSM input}) in~Eq.~(\ref{eq:V_1}) yields
 \begin{align*}
@@
 \end{align*}
-Hence, the system (\ref{eq:second-order system}) converges to the desired surface (\ref{eq:dual sliding surface}), and incidentally the convergence time can be calculated according to the finite time convergence theory.\par
-Once the system (\ref{eq:second-order system}) reaches the desired surface~(\ref{eq:dual sliding surface}), the entire system states are handled by the reduced system:
+Hence, the system (\ref{eq:second-order system}) converges to the desired SM surface (\ref{eq:dual sliding surface}), and incidentally the convergence time can be calculated according to the finite time convergence theory.
+Once the system (\ref{eq:second-order system}) satisfies $\bm s = \bm 0$, the entire system states will be handled by the reduced system:
 \begin{align*}
@@
 \end{align}
-where $\hat V(t) = \frac{x_1^2+x_3^2}{2}$ is the Lyapunov function selected for the reduced system.
+where $\hat V = \frac{x_1^2+x_3^2}{2}$ is the Lyapunov function selected for the reduced system.
 $t_r$ and $t_s$ stand for the reaching time and the sliding time, respectively.
@@
 \end{proof}
-On the basis of Theorem \ref{theorem:1}, we proceed to develop the parameters in the surface design to improve the performance, and furthermore this modified method makes the design process more flexible.
-Consider the system~(\ref{eq:second-order system}) with the surface $\bm s = [s_1,s_2]^T$, the details of which are described by following expressions:
+On the basis of Theorem \ref{theorem:1}, we proceed to develop the parameters in the SM surface design to improve the performance of the reaching phase, and furthermore this modified method makes the design process more flexible.
+Consider the system~(\ref{eq:second-order system}) with the surface $\bm s = [s_1,s_2]^T$ described by following expressions:
 \begin{align}
 \begin{split}
-s_1 &= x_2+\gamma(\vert x_1\vert^{\alpha} sgn(x_1)+x_1^3(t))-\lambda x_3\\
-s_2 &= x_4+\gamma(\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3(t))+\lambda x_1,\label{eq:modified dual sliding surface}
+s_1 &= x_2+\gamma(\vert x_1\vert^{\alpha} sgn(x_1)+x_1^3)-\lambda x_3\\
+s_2 &= x_4+\gamma(\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3)+\lambda x_1,\label{eq:modified dual sliding surface}
 \end{split}
 \end{align}
-where $\gamma$ is a positive constant and $\lambda\in R$ is a regulable parameter. Hence, the modified dual terminal SMC inputs are formed in the following theorem.
-\begin{mythm}\label{theorem:2}Modified Dual Terminal SMC Design.
-The second-order system (\ref{eq:second-order system}) will reach the desired surface $\bm s = 0$ shown in~Eq.
-(\ref{eq:modified dual sliding surface}) in finite time.
-The states of the system will converge to zero along the surface $\bm s=0$ in finite time, if the inputs are designed as follows:
+where $\gamma$ is a positive constant and $\lambda\in R$ is a design parameter. Accordingly, the modified DTSM control inputs are formed in the following theorem.
+\begin{mythm}\label{theorem:2}Modified DTSM Controller Design.
+The second-order system (\ref{eq:second-order system}) will reach the desired SM surface $\bm s = \bm 0$ shown in~Eq.~(\ref{eq:modified dual sliding surface}) in finite time, and then the system states will converge to zero along the surface $\bm s=\bm 0$ in finite time, if the inputs are designed as follows:
 \begin{align}
@@
 \end{proof}
-After introducing the parameters $\lambda$ and $\gamma$ into the DTSM scheme, the performances of the reaching and sliding phases become regulatable, meaning that these parameters can adjust the convergence time analytically.
-Although $\lambda$ does not appear in Eq.~(\ref{eq:total convergence time}), the establishment of $V(t_0)$ involves it when the state $\bm x(t_0)$ has been fixed.
-Strictly speaking, it affects the reaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V(t)=\bm s^T(t)\bm s = 0,\forall t\ge t_r$.
-Admittedly, the variety of $\lambda$ is only modestly helpful in this reaching time regulation due to its limited effect on $V(t_0)$.
-$\eta$ is said to be an ''reaching speed'' according to its function, a suitable selection of which will adjust the reaching time as desired in some extent.
-Hence, $\lambda$ cooperates with $\eta$ to manage the reaching status, and by utilizing the similar analysis, owing to $\gamma$ adjusting the speed of sliding phase, it's able to be defined as the management parameter of the sliding status.
+In the MDTSM scheme, the performances of the reaching and sliding phases can benefit from suitably selected $\lambda$ and $\gamma$ analytically.
+The establishment of $V(t_0)$ is depended on $\lambda$, if the state $\bm x(t_0)$ has been fixed.
+Exactly, $\lambda$ affects the reaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V=\bm s^T\bm s = \bm 0,\forall t\ge t_r$.
+$\eta$ is definied as the reaching speed, because a suitable $\eta$ can adjust the reaching time as desired in some extent.
+Hence, $\lambda$ cooperates with $\eta$ to manage the reaching phase dynamics, and similarly $\gamma$ is defined as the management parameter of the sliding phase dynamics.
 \begin{myrem}
-For the proposed designs, the parameter $\gamma$ may be defined as different scalar for the individual input, if so, one can produce the total convergence time as:
+For the proposed designs, the parameter $\gamma$ may be defined as different scalars for the inputs, if so, one can produce the total convergence time as:
 \begin{align}
@@
 \end{myrem}
-The finite convergence of the DTSM and MDTSM scheme has been verified clearly, but similar to the conventional terminal SMC, there exists another obstacle in the design mentioned above, namely, the issue of the singularity in control inputs.
+\subsection{Nonsingular MDTSM controller design}
+
+The finite convergence of the DTSM and MDTSM scheme has been verified clearly, but similar to the conventional terminal SMC, there exists another obstacle in the design mentioned above, i.e., the issue of the singularity in control inputs.
 Essentially, the singularity occurs in Eq.~(\ref{eq:modified input}) when $x_1=0$ but $x_2\neq 0$ in $u_1$ (the phenomena happens to $u_2$ under the same condition).
-For coping with the singularity, a nonsingular MDTSM scheme is presented after introducing an analytical technique into the MDTSM scheme based on the following lemma~\cite{feng2013nonsingular}.
+For coping with the singularity, the nonsingular MDTSM scheme is presented after introducing an analytical technique into the MDTSM scheme based on the following lemma~\cite{feng2013nonsingular}.
 \begin{mylem}\label{lemma:3}
-Considering the second-order system (\ref{eq:second-order system}), the TSM surface is designed as:
+Considering the second-order system (\ref{eq:second-order system}), the TSM surfaces are designed as:
 \begin{align*}
@@
 \end{align*}
-and nonsingular inputs are given out directly as follows:
+and nonsingular inputs can be given out directly as follows:
 \begin{align*}
@@
 \end{align*}
-where $sat(u_f,u_s)$ is a saturation function:
+$sat(u_f,u_s)$ is a saturation function:
 \begin{align}
@@
 u_f\quad &-u_s\le u_f< u_s\\
--u_s\quad &u_f\le -u_s
+-u_s\quad &u_f\le -u_s\label{eq:saturation}
 \end{cases},
 \end{align}
-and $u_s>0$ is determined according to the requirements of the performance.\par
-Adopting the control scheme mentioned above, the system~(\ref{eq:second-order system}) will converge to zero in finite time without any singularity occurring during the regulation process.
+with $u_s>0$. Adopting the control scheme mentioned above, the system~(\ref{eq:second-order system}) will be stabilized in finite time without any singularity occurring during the regulation process.
 \end{mylem}
 \begin{mythm}\label{theorem:3}
-Consider a second-order system (\ref{eq:second-order system}), and for eliminating the singularity in inputs of the MDTSM scheme, select new inputs to complete the nonsingular MDTSM scheme.
-Introducing the saturation terms into the original inputs yields:
+Consider a second-order system (\ref{eq:second-order system}), and for eliminating the singularity, the inputs are selected to complete the nonsingular MDTSM scheme.
+Introducing the saturation terms~\ref{eq:saturation} into the original inputs yields:
 \begin{align}
@@
 \end{align}
-one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:second-order system}), providing the finite time convergence by using sliding mode technique.
+and one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:second-order system}), providing the finite time convergence by using MDTSM technique.
 \end{mythm}
@@
 \end{proof}
+\subsection{MDTSM controller design for systems subjected to input limitations}
 \textcolor{red}{
-In practice, the control input can not be very large due to the input limitation, such as the tension limitation in the deployment of the tethered satellite system~\cite{Ma201667}, and hence it is meaningful to adapt the proposed controllers for the system subjected to the input limitation.
+Besides singularity issue, in practice, the control input can not be very large due to the input limitation, such as the tension limitation in the deployment of the tethered satellite system~\cite{Ma201667}, and hence it is meaningful to adapt the proposed controllers for the system subjected to the input limitation.
 Consider a nominal second-order system subjected to the input limitation:
@@
 \end{myas}
-Thanks to the above assumption, we give out the adaptive dual terminal SMC scheme.
+Thanks to the above assumption, we give out the adaptive DTSM scheme.
 \begin{mythm}\label{thm:4}
@@
 }
-When the input $u_1$ equals to $u_2$ in system.~(\ref{eq:second-order system}), the number of the inputs is fewer than the degrees of the freedom, resulting in that the issue transforms to be an underactuated stabilization.
-These underactuated systems are frequently used in the scientific field, such as flexible manipulators, overhead crane and underwater robots, because fewer actuators may decrease the mass and save the energy as well.
-Cooperating with the hierarchical sliding mode methodology, the surface design scheme proposed above is able to control this kind of systems \cite{wang2004design}.
-We give the hierarchical dual TSM design directly.
+\subsection{MDTSM controller design for underactuated systems}
+When the input $u_1$ equals to $u_2$ in system~(\ref{eq:second-order system}), the number of the inputs is fewer than the degree of the freedom, which leads to the underactuated issue.
+These underactuated systems are ubiquitous in the scientific field, because fewer actuators may decrease the mass and save the energy.
+Cooperating with the hierarchical sliding mode methodology, the presented MDTSM scheme can control this kind of systems~\cite{wang2004design}.
+We give the hierarchical MDTSM controller directly.
 \begin{mythm}
-Consider a nonlinear system described as:
+Consider the nonlinear system described as:
 \begin{align}
@@
 \end{align}
-where the condition of variables is same to the system~(\ref{eq:second-order system}). Construct the surface as:
+where the conditions of variables are same to the system~(\ref{eq:second-order system}). Construct the SM surfaces as:
 \begin{align}
@@
 \end{align}
-where $c_1$ and $c_2$ are suitable positive constants, and $s_1$ and $s_2$ have been defined in the MDSM design. Adopting the equivalent control design method deduces the individual equivalent inputs:
+where $c_1$ and $c_2$ are suitable positive constants, and $s_1$ and $s_2$ have been defined in Eq.~(\ref{eq:dual sliding surface}).
+Adopting the equivalent control design method deduces the individual equivalent inputs:
 \begin{align}
@@
 \end{align}
-to regulate all states of the underactuated system~(\ref{eq:underactuated system}) as desired in finite time.
+which can stabilize the underactuated system~(\ref{eq:underactuated system}) as desired in finite time.
 \end{mythm}
@@
 \begin{split}
-\dot V &= S\dot S = S(c_1\dot s_1+c_2\dot s_2)\\
+\dot V &= S\dot S\\ &= S(c_1\dot s_1+c_2\dot s_2)\\
 &=S(c_1(f_1(\bm x)+g_1(\bm x)+b_1(\bm x)u+\gamma\alpha\vert x_1\vert^{\alpha-1}x_2+3\gamma x_1^2x_2-\lambda x_4)\\
@@
 \end{proof}
-\section{Modified Dual terminal SMC for rigid manipulators}\label{sec:3}
-In this section, the MDTSM control is proposed for the rigid $2$-link robotic manipulator
+\section{MDTSM controller design for rigid manipulators}\label{sec:3}
+In this section, the MDTSM scheme designed for the stabilization of the rigid $n$-link robotic manipulator is discussed.
+Firstly, we consider the $2$-link robotic manipulator dynamics described using Eular Lagrange equation~\cite{feng2002non}:
 \begin{align}
-M(\bm q)\ddot {\bm q}+C(\bm q,\dot {\bm q})+g(\bm q)= \bm\tau(t)+{\bm d}(t),\label{eq:lagrangian system}
+M(\bm q)\ddot {\bm q}+C(\bm q,\dot {\bm q})+g(\bm q)= \bm\tau+{\bm d},\label{eq:lagrangian system}
 \end{align}
-where $\bm q(t) = $ is the $2\times 1$ vector of joint angular position; ${M(\bm q)}$ is the $2\times 2$ inertia matrix; ${C(\bm q,\dot{\bm q})}$ denotes the Coriolis and centrifugal forces by using the $n\times1$ vector; ${g(\bm q)}$ stands for the $n\times 1$ gravitational torque; $\bm{\tau}(t)$ is referred to as the joint torques which are the inputs practically; $\bm d(t)$ expresses the $n\times 1$ bounded input disturbances vector.
+where $\bm q\in R^{2} $ is the joint angular position vector; ${M(\bm q)}\in R^{2\times 2}$ is the inertia matrix; ${C(\bm q,\dot{\bm q})}\in R^{2\times 1}$ denotes Coriolis and centrifugal forces; ${g(\bm q)}\in R^{2\times 1}$ stands for the gravitational torque; $\bm{\tau}\in R^{2\times 1}$ is referred to as the joint torques; $\bm d\in R^{2\times 1}$ expresses the bounded disturbance vector.
 Normally, there exist some uncertainties in the manipulator, producing the dynamic equations:
 \begin{align}
-(M_0(\bm q)+\Delta {M(\bm q))\ddot {\bm q}}+{C_0(\bm q,\dot {\bm q})+\Delta C(\bm q,\dot {\bm q})}+g_0(\bm q)+\Delta g(\bm q)=\bm {\tau}(t)+\bm{d}(t),
+(M_0(\bm q)+\Delta {M(\bm q))\ddot {\bm q}}+({C_0(\bm q,\dot {\bm q})+\Delta C(\bm q,\dot {\bm q})})+g_0(\bm q)+\Delta g(\bm q)=\bm {\tau}+\bm{d},
 \end{align}
-where $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$ and $g_0(\bm q)$ are the estimated terms affected by the the uncertainties including $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$, $g_0(\bm q)$, and the disturbance $\bm{d}(t)$.
-Particularly, the following assumption is exhibited to explain the bounded characteristics of the robotic dynamics~\cite{feng2002non}:
+where $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$ and $g_0(\bm q)$ are the estimated terms, while $\Delta M_0(\bm q)$, $\Delta C_0(\bm q,\dot {\bm q})$, $\Delta g_0(\bm q)$ denotes the uncertainties in the manipulator dynamics.
+Particularly, the following assumptions exist to explain the bounded characteristics of the dynamics~\cite{feng2002non}:
 \begin{align}
@@
 &\Vert g(\bm q)\Vert< \psi_0+\psi_1\Vert\bm q\notag\Vert\\
-&\Vert \bm {\rho}(t)\Vert< \mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2,\label{eq:manipulator uncertainty}
+&\Vert \bm {\rho}\Vert< \mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2,\label{eq:manipulator uncertainty}
 \end{align}
-where $\bm {\rho}(t) = -\Delta M(\bm q)-\Delta C(\bm q,\dot {\bm q})-\Delta g(\bm q)$, and $\theta_0$, $\phi_0$, $\phi_1$, $\phi_2$, $\psi_0$, $\psi_1$, $\mu_0$, $\mu_1$, $\mu_2$ are positive constants.\par
-Select $\bm q_d$ as the desired state of the Lagrangian system~(\ref{eq:lagrangian system}), and the derivative of $\bm q_d$ is designated as $\dot {\bm q}_d$. Hence the state error is stated as:
+where $\bm {\rho} = -\Delta M(\bm q)-\Delta C(\bm q,\dot {\bm q})-\Delta g(\bm q)$, and $\theta_0$, $\phi_0$, $\phi_1$, $\phi_2$, $\psi_0$, $\psi_1$, $\mu_0$, $\mu_1$, $\mu_2$ are positive constants.\par
+Select $\bm q_d$ as the desired state vector of the manipulator dynamics~(\ref{eq:lagrangian system}), and the derivative of $\bm q_d$ is designated as $\dot {\bm q}_d$.
+Hence the state error is stated as:
 \begin{align}
@@
 \begin{align*}
-\lceil\bm h(t)\bm p(t)+\bm v(t)\rfloor = (h_1(t)p_1(t)+v_1(t),h_2(t)p_2(t)+v_2(t),\ldots,h_n(t)p_n(t)+v_n(t))^T.
+\lceil\bm h\bm p+\bm v\rfloor = (h_1p_1+v_1,h_2p_2+v_2,\ldots,h_np_n+v_n)^T.
 \end{align*}
-On the basis of the above results, one can design the DTSM scheme for $2$-link robotic manipulator by utilizing the following theorem.
+On the basis of the above results, one can design the DTSM scheme for the $2$-link robotic manipulator by utilizing the following theorem.
 \begin{mythm}\label{theorem:4}
-For the rigid $2$-link manipulator~(\ref{eq:lagrangian system}), if the dual TSM surface is selected as
+For the rigid $2$-link manipulator~(\ref{eq:lagrangian system}), if the DTSM surface is selected as
 \begin{align}
@@
 \dot V &= \bm s^T\dot{\bm s}=\bm s^T(\ddot{\bm \varepsilon}+C_r\lceil\alpha\vert\bm\varepsilon\vert^{\alpha-1}\dot{\bm \varepsilon}+3\bm \varepsilon^2\dot{\bm \varepsilon}\rfloor+C_\lambda\dot{\bm \varepsilon})\\
-&=\bm s^T(M_0^{-1}(\bm q)(-M_0(\bm q)\ddot {\bm q}_d-C_0(\bm q,\dot {\bm q})-g_0(\bm q)+\bm\tau+\bm\rho(t))\\
+&=\bm s^T(M_0^{-1}(\bm q)(-M_0(\bm q)\ddot {\bm q}_d-C_0(\bm q,\dot {\bm q})-g_0(\bm q)+\bm\tau+\bm\rho)\\
 &\quad+C_r\lceil\alpha\vert\bm\varepsilon\vert^{\alpha-1}\dot{\bm \varepsilon}+3\bm \varepsilon^2\dot{\bm \varepsilon}\rfloor+C_\lambda\dot{\bm \varepsilon})\\
-&=\bm s^T(M_0^{-1}(\bm q)(\bm u_0+\bm u_2+\bm\rho(t))+C_r\lceil\alpha\vert\bm\varepsilon\vert^{\alpha-1}\dot{\bm \varepsilon}+3\bm \varepsilon^2\dot{\bm \varepsilon}\rfloor+C_\lambda\dot{\bm \varepsilon})\\
-&=\bm s^TM_0^{-1}(\bm q)(-k\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}+\bm\rho(t))\\
-&\le -(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2)\Vert M_0^{-1}(\bm q)\Vert\Vert \bm s\Vert+\Vert\bm\rho(t)\Vert\Vert M_0^{-1}(\bm q)\Vert\Vert \bm s\Vert\\
-&\le -(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2-\Vert\bm\rho(t)\Vert)\Vert M_0^{-1}(\bm q)\Vert\Vert \bm s\Vert.
+&=\bm s^T(M_0^{-1}(\bm q)(\bm u_0+\bm u_2+\bm\rho)+C_r\lceil\alpha\vert\bm\varepsilon\vert^{\alpha-1}\dot{\bm \varepsilon}+3\bm \varepsilon^2\dot{\bm \varepsilon}\rfloor+C_\lambda\dot{\bm \varepsilon})\\
+&=\bm s^TM_0^{-1}(\bm q)(-k\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}+\bm\rho)\\
+&\le -(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2)\Vert M_0^{-1}(\bm q)\Vert\Vert \bm s\Vert+\Vert\bm\rho\Vert\Vert M_0^{-1}(\bm q)\Vert\Vert \bm s\Vert\\
+&\le -(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2-\Vert\bm\rho\Vert)\Vert M_0^{-1}(\bm q)\Vert\Vert \bm s\Vert.
 \end{split}
@@
 \begin{align}
-\varrho=(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2-\Vert\bm\rho(t)\Vert)\Vert M_0^{-1}(\bm q)\Vert>0
+\varrho=(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2-\Vert\bm\rho\Vert)\Vert M_0^{-1}(\bm q)\Vert>0
 \end{align}
-and $\Vert\bm s\Vert\neq 0$, hence, the Lyapunov stability has been proved, meaning that the system will reach the desired surface~(\ref{eq:lagrangian surface}) in finite time.
-Once the reaching condition is satisfied, one can achieve a reduced system by substituting $\bm s = 0$ into the system~(\ref{eq:lagrangian system}).
-It owns the form, similar to Eq.~(\ref{eq:normal sliding surface}), and therefore, adopting Theorem \ref{theorem:2} drives the reduced system converging to the origin in finite time.
+and $\Vert\bm s\Vert\neq 0$, hence, the desired SM surface~(\ref{eq:lagrangian surface}) can be reached in finite time.
+Once the reaching condition is satisfied, one can get the reduced system by substituting $\bm s = \bm 0$ into the system~(\ref{eq:lagrangian system}).
+It owns the form similar to Eq.~(\ref{eq:normal sliding surface}), and therefore, adopting Theorem \ref{theorem:2} drives the reduced system converging to the origin in finite time.
 The proof is completed.
@@
 \begin{myrem}
-At this point, the MDTSM scheme for $2$-link robotic manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator.
-Consider a $n$-link robotic manipulator in which $n$ is an even number, and the desired sliding surface follows
+At this point, the MDTSM scheme for $2$-link robotic manipulator has been demonstrated.
+We proceed to consider a $n$-link robotic manipulator where $n$ is an even number, and the desired sliding surface is selected as
 \begin{align}
@@
 Referring to Theorem \ref{theorem:4}, it's easy to obtain the MDTSM input for the even $n$-link manipulator.
-Essentially, this technique requires that the sliding mode surface has to consist of $n/2$ pairs of individual sliding surfaces, in another words, this design for the surface can be regarded as a work for yielding surfaces of the $n/2$ sub-systems.\par
-Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension is able to be excluded by using conventional terminal SMC, which results in that the remained $n-1$-link manipulator can be controlled by the proposed MDTSM scheme.
+Essentially, this technique requires that the SM surface has to consist of $n/2$ pairs of individual sliding surfaces, in another words, this design for the surface can be regarded to design the SM surfaces for the $n/2$ sub-systems.\par
+Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension can be excluded by using conventional TSM scheme, which results in that the remained $n-1$-link manipulator can be controlled by the proposed MDTSM scheme.
 \end{myrem}
@@
 One can also use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the DTSM control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically.
-For handling the chattering, the $sign(x)$ is replaced with $sat(x,\delta)$, and the bounded value $\delta$ is determined according to actual needs.
+For handling the chattering, the $sign(x)$ is replaced with $sat(x,\delta)$, and the boundedness thickness can be selected as $\delta=1\times 10^{-4}$.
 \textcolor{red}{Incorporating the adaptive MDTSM technique, the manipulator dynamics subjected to the input limitation can also been stabilized as desired.}
@@
 \section{Simulation studies}\label{sec:4}
-In this section, three studies will be presented, namely, a verification on the effectiveness of the proposed DTSM and MDTSM schemes, an underactuated example and an application to a manipulator stabilization evaluating the performance of the control schemes.
+In this section, three simulations will be presented, namely, a verification on the effectiveness of the DTSM and MDTSM schemes, an underactuated example and the robotic manipulator stabilization evaluating the performance of the proposed control schemes.
 \subsection{Effectiveness study}
-For verifying the effectiveness of the proposed control scheme, consider the following second-order nonlinear system with the disturbance:
+For verifying the effectiveness of the proposed control scheme, consider the following second-order system with the external disturbances:
 \begin{align}
@@
 \end{align}
-and an MDTSM control scheme is produced conveniently.
-It's obvious that the disturbance in the system~(\ref{eq:simulation second-order system}) behaves bounded, which is said to be the following uncertainty terms:
+It's obvious that the disturbances in the system~(\ref{eq:simulation second-order system}) behave bounded:
 \begin{align*}
@@
 \end{align*}
-and hence, based on the analysis in Theorem~\ref{theorem:1}, $l_1>0.1$ and $l_2>0.8$ are determined accordingly to guarantee the reaching condition of the desired sliding surface.
+and hence, based on the analyses in Theorem~\ref{theorem:1}, $l_1>0.1$ and $l_2>0.8$ are determined accordingly to guarantee the reaching condition of the desired sliding surface.
 Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation second-order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
 The system is supposed to be conducted to the desired state $\bm x_d=(0,0,0,0)$ from a prescript state $\bm x_0=(1.2,1.2,1.2,1.2)$.
-Admittedly, this prescript condition leads to a lager initial reaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding surface, therefore a large reaching speed $k_i$ is required correspondingly.
+Admittedly, this prescript condition leads to a lager initial reaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding surface, therefore a large reaching speed $k$ is required correspondingly.
 The control parameters are chosen as: $\alpha = 0.6$, $\lambda = 0.5$, $\gamma = 3$ and $k = 20$.
-Besides the large reaching speed selected, $\gamma$ accelerates the sliding phase indirectly.
+Besides the large reaching speed selected, $\gamma$ accelerates the convergence in the sliding phase indirectly.
 Therefore the design of the MDTSM controller for the system~(\ref{eq:simulation second-order system}) is finished, and the corresponding simulation results are illustrated from Figure~\ref{Figure:2} to Figure~\ref{Figure:3}.\par
@@
 \subsection{Underactuated example}
-Figure~\ref{Figure:8} shows an overhead crane system, the state space equations of which is same with the formula in Eq.~(\ref{eq:underactuated system}) with state variables selected as $\bm x=(x,\dot x,q,\dot q)$, and the details are listed:
+Figure~\ref{Figure:8} shows an overhead crane system, the state space equation of which is same with the formula in Eq.~(\ref{eq:underactuated system}) with state variables selected as $\bm x=(x,\dot x,q,\dot q)$, and the details are listed:
 \begin{align}
@@
 Figure~\ref{Figure:9} shows the state response curves of the overhead crane system controlled using the HDSM control scheme, and the results show that the controller stabilize the displacement at $6s$ approximately, though the disturbance exists in the system.
-One can find that the swing angle is fluctuating in a fairly small range, the boundary of which is not more than $1\times 10^-3rad$, hence this phenomena is reasonable and also occurs in the stable hierarchical SMC \cite{wang2004design}.
+One can find that the swing angle is fluctuating in a fairly small range, the boundary of which is not more than $1\times 10^-3rad$, and this phenomena is reasonable and also occurs in the stable hierarchical SMC scheme~\cite{wang2004design}.
 \begin{figure}
@@
 In this model, the uncertainty is brought in by estimated terms, namely, $\bar m_1=0.4$ and $\bar m_2=1.2$ which are all not the actual value obviously.
-In addition, owing to that it sits on many terms in the dynamic equations, it's a severe challenge to guarantee the performance.
-Accordingly, the uncertainty parameters in Eq.~(\ref{eq:manipulator uncertainty}) are assumed to be $\mu_0=10$, $\mu_1=3$, $\mu_2=3$.\par
-This section will give a set of simulation to examine the performance of the MDTSM control in tracking the certain angle condition.
+In addition, owing to that it sits on many terms in the dynamic equations, it's a severe challenge to guarantee the stability of the system.
+Accordingly, the uncertainty parameters in Eq.~(\ref{eq:manipulator uncertainty}) are assumed to be $\mu_0=10$, $\mu_1=3$, $\mu_2=3$.
+
+This section will give a set of simulation to examine the performance of the MDTSM controller in tracking the certain angle condition.
 The behavior of the manipulator should fulfill the initial and desired condition, namely, $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$.
 In order to ensure the stability and a fast convergence speed, the control parameters are chosen conservatively to make the manipulator track the desired attitude in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $k = 150$.
-The terminal SMC (TSM) scheme, as a comparison, is also implemented to regulate the behavior of the manipulator:
+The TSM scheme, as a comparison, is also implemented to regulate the behavior of the manipulator:
 \begin{align}
@@
 \end{align}
-where the main control parameters of which are selected as $\alpha = 0.6$, $\gamma = 5$ and $k = 150$ to get a fairly good control performance.\par
+where the main control parameters of which are selected as $\alpha = 0.6$, $\gamma = 5$ and $k = 150$ to get a fairly good control performance.
+
 The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}.
-Comparatively speaking, $q_1$ reaches the desired state at about $3s$ with the MDTSM scheme, the reaching time of which is approximating $0.8s$ less than of the TSM scheme, and $q_2$ performs similar behaviors with a reasonable variable range of the angular rates.
+Comparatively speaking, $q_1$ reaches the desired state at about $2.3s$ with the MDTSM scheme, the reaching time of which is approximating $1s$ less than of the TSM scheme, and $q_2$ performs similar behaviors with a reasonable variable range of the angular rates.
 \textcolor{red}{From the results shown in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}, we can find that the maximum theoretical finite convergence time $t_f=3.0843s$, which can be obtained directly accoring to Eq.~(\ref{eq:total convergence time}) and simulation datas, is more than $2.3s$, the convergence time of the simulation result.
@@
 It is obvious that the torques of the two jionts are both switching dramatically at the beginning, and this phenomenon is caused directly by the rapidly changing sliding mode dynamics $s_i$.
-Moreover, at about $1.7s$, all the joint states are regulated to locate in the vicinity of the origin, and the boundary layer technique works to generate a continuous torque in the subsequent time.} Therefore these results show that the MDTSM control scheme is able to achieve the regulation of the manipulator effectively.
+Moreover, at about $1.7s$, all the joint states are regulated to locate in the vicinity of the origin, and the boundary layer technique works to generate a continuous torque in the subsequent time.} Therefore these results show that the MDTSM control scheme can achieve the regulation of the manipulator effectively.
 \begin{figure}
@@
 Reviewing the joint 1 torque shown in enlarged details of  Figure~\ref{Figure:torque}, we can find that the torque exceeds the reasonable torque upper limit $50Nm$ around $2.3s$.
-Hence, to overcom this issue, the adaptive MDTSM controller is applied to eliminate the effect of the input limitation and to guarantee the rigorous stability analyses of the manipulator dynamics.
+Hence, to overcom this issue, the adaptive MDTSM controller is applied to diminish the effect of the input limitation and to guarantee the rigorous stability analyses of the manipulator dynamics.
 The results shown in Figure~\ref{Figure:limitation_torque} indicate that the joint torques are limited in the region $[-50,50]Nm$ from $0.2s$ to $0.4s$, while in the Figure~\ref{Figure:limitation_q} the trajectories of the manipulator dynamics are still under control.
@@
 \section{Conclusion}\label{sec:5}
-A DTSM control for n-link robotic manipulator has been presented.
-The method integrates two individual subsystems as a unity, then builds the surface and input for it to complete the controller design.
-The control scheme is able to guarantee the reaching condition of the desired sliding surface, meanwhile the system states converge to the origin along the desired surface.
+A feasible MDTSM control for n-link robotic manipulator has been presented.
+The method integrates two individual subsystems as a unity, then builds the surfaces and inputs for it to complete the controller design.
+The control scheme can guarantee the reaching condition of the desired sliding surface, meanwhile the system states converge to the origin along the desired SM surface.
 Also, the entire convergence time can be calculated accordingly.
-Developing the basic DTSM yields the MDTSM control, providing a solution to eliminating chattering, avoiding singularity and fast convergence.
+Developing the basic DTSM yields the MDTSM controller, providing a solution to eliminating chattering, avoiding singularity and fast convergence.
 For dealing with the under actuated characteristics which may appear in the system, the HDTSM control is derived, and the overhead crane example verifies its effectiveness.

### 2016-11-14 paper3_manuscript.tex
20161114

@@
 \begin{abstract}
-This paper proposes a dual terminal SMC scheme for the rigid robotic manipulator.
-\textcolor{red}{As a signiﬁcant novelty, the presented design technique integates the individual SM surfaces to achieve the finite time convergence of overall system states by utilizing specially designed construct, and accordingly the convergence time for the entire system is easily obtained due to the integral design.
-The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue are solved by introducing the hierarchical methodology into the basic dual SMC scheme.
-Combining the adaptive technique with the proposed method eliminates the adverse effect caused by the input limitation in the rigious stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the rigid robotic manipulator.
+This paper proposes a dual terminal sliding mode scheme for tracking tasks of rigid robotic manipulators.
+\textcolor{red}{As a signiﬁcant novelty, the presented design technique integates the individual sliding mode surfaces to achieve the finite time convergence of tracking errors utilizing specially designed construct, and accordingly the convergence time is easily obtained due to the integral design.
+The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue is solved by introducing the hierarchical methodology into the basic dual sliding mode controller.
+Combining the adaptive technique with the proposed method eliminates the adverse effect caused by the input limitation in the rigious stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the tracking tasks of the rigid robotic manipulator.
 Simulation results validate the theoretical analyses about the proposed method.
@@
 \begin{keyword}
-Finite time control; Robotic manipulator control; TSM; Input limitation; Stability analysis
+Finite time control; Robotic manipulator control; Terminal sliding mode control; Input limitation; Stability analysis
 \end{keyword}
@@
 \end{align}
-and one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:second-order system}), providing the finite time convergence by using MDTSM technique.
+and one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:second-order system}), providing the finite time convergence using MDTSM technique.
 \end{mythm}
@@
 Essentially, this technique requires that the SM surface has to consist of $n/2$ pairs of individual sliding surfaces, in another words, this design for the surface can be regarded to design the SM surfaces for the $n/2$ sub-systems.\par
-Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension can be excluded by using conventional TSM scheme, which results in that the remained $n-1$-link manipulator can be controlled by the proposed MDTSM scheme.
+Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension can be excluded using conventional TSM scheme, which results in that the remained $n-1$-link manipulator can be controlled by the proposed MDTSM scheme.
 \end{myrem}
 \begin{myrem}
-The singularity of the MDTSM scheme for the robotic manipulator can be removed by using the technique introduced in Theorem \ref{theorem:3}.
+The singularity of the MDTSM scheme for the robotic manipulator can be removed using the technique introduced in Theorem \ref{theorem:3}.
 \end{myrem}

### 2016-11-15 paper3_manuscript.tex
20161115

@@
 \begin{frontmatter}
-\title{A New Dual Terminal Sliding Mode Control Design For Rigid Robotic Manipulator}
+\title{Dual Terminal Sliding Mode Control Design For Rigid Robotic Manipulator}
 \author{Zhiqiang Ma}
@@
 \begin{abstract}
-This paper proposes a dual terminal sliding mode scheme for tracking tasks of rigid robotic manipulators.
+This paper proposes a dual terminal sliding mode control scheme for tracking tasks of rigid robotic manipulators.
 \textcolor{red}{As a signiﬁcant novelty, the presented design technique integates the individual sliding mode  surfaces to achieve the finite time convergence of tracking errors utilizing specially designed construct, and accordingly the convergence time is easily obtained due to the integral design.
 The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue is solved by introducing the hierarchical methodology into the basic dual sliding mode controller.
-Combining the adaptive technique with the proposed method eliminates the adverse effect caused by the input limitation in the rigious stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the tracking tasks of the rigid robotic manipulator.
+The proposed method can easily combine with the adaptive technique to  eliminate the adverse effect caused by the input limitation in the rigious stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the tracking tasks of the rigid robotic manipulator.
 Simulation results validate the theoretical analyses about the proposed method.
@@
 Guzman et al.
-investigated the application of a SMC in a power factor rectifier with the constant switching frequency~\cite{guzman2016sliding}.
+investigated the SMC application in a power factor rectifier with the constant switching frequency~\cite{guzman2016sliding}.
 Said et al.
 designed a robust adaptive sliding mode method to ensure the asymptotically stability of a boost converter~\cite{oucheriah2013pwm}.
-Roughly speaking, the SMC scheme is competent for normal scientific missions, due to its insensitivity to parameteric uncertainties and external disturbances, however, there still exist some obstacles, such as noncontinuous switching inputs in high frequency and convergence speed design schemes~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some practical engineering applications~\cite{fridman2011sliding}.}
+Roughly speaking, the SMC scheme is competent for normal scientific missions, due to its insensitivity to parameteric uncertainties and external disturbances, however, there still exist some obstacles, such as noncontinuous switching inputs in high frequency and low convergence speed of the tracking errors~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some high-precision engineering applications~\cite{fridman2011sliding}.}
 
-\textcolor{red}{For alleviating the mentioned bad effects, many scientific researchers have presented remarkable achievements to promote the performance of the SMC scheme in last decade~\cite{zong2013quasi,santiesteban2013time,mu2015continuous,evangelista2013lyapunov,gonzalez2014chattering,dadras2012fractional,zhao2013output}.
-Among these methods, the high-order SMC and super-twisting SMC work in reducing the chattering to generate continuous inputs~\cite{castillo2015higher,palosz2015laser,edwards2016adaptive,zhao2015finite,liu2015second}.
+\textcolor{red}{For alleviating the mentioned bad effects, many scientific researchers have presented remarkable achievements to promote the performance of SMC in last decade~\cite{zong2013quasi,santiesteban2013time,mu2015continuous,evangelista2013lyapunov,gonzalez2014chattering,dadras2012fractional,zhao2013output}.
+Among these methods, the high-order SMC and super-twisting SMC work well in reducing the chattering to generate continuous inputs~\cite{castillo2015higher,palosz2015laser,edwards2016adaptive,zhao2015finite,liu2015second}.
 Besides the issue on repressing the chattering, the fast convergence of the SMC scheme becomes a hot subject recently.
-The normal linear SMC scheme completes the stabilization of the system dynamics.
-In the first step, the control inputs drive the system states onto the prescript sliding surfaces, and this stage is also called the reaching phase.
-Then the sliding mode dynamics work to drive the system states to the origins along the ideal surfaces in the second step, and this stage is usually called the sliding phase.
-The reaching phase  usually requires the states converge to the ideal sliding mode (SM) surfaces in finite time, and suitably selected Lyapunov function and control parameters may accelerate this process; the sliding phaseis related to the designed ideal sliding surfaces closely, and trivial design techniques are can guarantee the asymptotically stability.
-To achieve a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and comparing with the SMC design mentioned above, the most significant contributions of the TSM are introducing the finite time convergence to the sliding phase to complete the global finite time convergence.
-Moreover, the terminal SMC schemes have been utilized to achieve the high precise control, i.e., in~\cite{li2015robust}, an adaptive TSM scheme controlled a $2$-link robotic manipulator to track the variable signals.
+The normal linear SMC completes the stabilization of the system dynamics in two steps.
+In the first step, the control inputs drive the system states onto the prescript sliding mode  surfaces, and this stage is also called the reaching phase.
+Then the sliding mode dynamics function to drive the system states to the origins along the ideal surfaces in the second step, which is usually known as the sliding phase.
+The reaching phase usually requires the states reach the ideal sliding mode surfaces in finite time, and suitably selected Lyapunov function and control parameters may accelerate this process; the sliding phase is related to the designed ideal sliding mode  surfaces closely, and trivial design techniques can guarantee the asymptotically stability of the reduced system~\cite{mu2016switching}.
+To achieve a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and compared with the SMC design mentioned above, the most significant contributions of the TSM concept are introducing the finite time convergence to the sliding phase to complete the global finite time convergence~\cite{mu2016switching}.
+Moreover, the terminal SMC schemes have been utilized to achieve the high precise control, i.e., in~\cite{li2015robust}, an adaptive TSM controller regulated a $2$-link robotic manipulator to track the variable signals.
 Feng et al.
-presented a novel Lagrangian dynamic expression for the the rigid robot, and applied the global TSM control law to manipulate the robotic dynamics ~\cite{feng2002non}.
+stated a novel Lagrangian dynamic expression for the the rigid robot, and applied the global TSM control law to manipulate the robotic dynamics ~\cite{feng2002non}.
 In~\cite{kamal2016continuous}, Kamal addressed a continuous homogeneous sliding mode algorithm for a perturbed second-order plant, and the algorithm could be regarded as a combination of TSM and super-twisting sliding mode schemes.}
 
-\textcolor{red}{Notably, the conventional TSM surface design techniques are similar, since the surfaces are all designed for the single variable based on the finite time control theory, in another words, only the individual variable and its derivative are concerned on by most designers~\cite{mu2016switching}.
-This nature makes the TSM scheme become an individual control subsystem, which leads to the complicity of global convergence time in some extent.
-In this paper, an integral SM surface design technique breaks the barriers mentioned above, and the novel surface includes two designed variables to guarantee the integral finite time convergence.
-Moreover, nonsingularities of the TSM scheme, chattering suppressions, underactuated applications and input limitations are also considered in the scheme.}
+\textcolor{red}{Notably, the conventional TSM surface design techniques are similar, since the surfaces are all designed for the single variable based on the finite time stability theory, in another words, only the individual variable and its derivative are concerned on by most designers~\cite{mu2016switching}.
+This nature makes the TSM controller become an individual control subsystem, which leads to the complicity of global convergence time in some extent.
+In this paper, an integral sliding mode  surface design technique breaks the barriers mentioned above, and the novel surface includes two designed variables to guarantee the integral finite time convergence.
+Moreover, nonsingularities of the TSM control scheme, chattering suppressions, underactuated applications and input limitations are also considered in the controller design.}
 
@@
 The novel DTSM surface is exploited to achieve the finite time convergence, and the reaching and sliding times can both be calculated directly.
-For coping with the underacutated issue, cooperating with the hierarchical sliding surface design methodology, we combine the hierarchical SMC scheme with the DTSM scheme to develop a hierarchical dual TSM (HDTSM) control law to ensure the rigorous stability analyses.
+For coping with the underacutated issue, cooperating with the hierarchical sliding mode  surface design methodology, we combine the hierarchical SMC scheme with the DTSM controller to develop a hierarchical dual TSM (HDTSM) control law to ensure the rigorous stability analyses.
 A modified DTSM (MDTSM) control scheme is presented to regulate the motion of the $n$-link robotic manipulators, and the case subjected to input limitations is also taken into consideration.
-The remained paper is organized as follows: Section~\ref{sec:2} introduces the DTSM scheme, and the finite time convergences of the reaching and sliding phase are discussed.
-Furthermore, we provide the DTSM scheme with extra design parameters to obtain the MDTSM scheme, which performs better in theoretical analyses; for stabilizing underactuated systems, the HDTSM design is also developed in this section.
-In Section~\ref{sec:3}, the MDTSM is applied to the motion control system of the $n$-link robotic  manipulator, and the stability analyses are also carried out.
+The remained paper is organized as follows: Section~\ref{sec:2} introduces the DTSM controller, and the finite time convergences of the reaching and sliding phase are discussed.
+Furthermore, we provide the DTSM control scheme with extra design parameters to obtain the MDTSM controller, which performs better in theoretical analyses; for stabilizing underactuated systems, the HDTSM design is also developed in this section.
+In Section~\ref{sec:3}, the MDTSM control law is applied to the motion control system of the $n$-link robotic  manipulator, and the stability analyses are also carried out.
 Section~\ref{sec:4} exhibits the simulation results, and finally the conclusion is assigned in Section~\ref{sec:5}.}
@@
 s_1 &= x_2+\vert x_1\vert^{\alpha} sgn(x_1)+x_1^3-x_3\\
-s_2 &= x_4+\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3+x_1.\label{eq:dual sliding surface}
+s_2 &= x_4+\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3+x_1.\label{eq:dual sliding mode  surface}
 \end{split}
@@
 \textcolor{red}{$sgn(x)$ is the sign function, and $0<\alpha<1$ is a positive scalar.
-For the sake of simplicity, the symbol $t$ is usually omitted in this paper, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding surface $\bm s(t)$ is often abbreviated as $\bm s$.}
+For the sake of simplicity, the symbol $t$ is usually omitted in this paper, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding mode  surface $\bm s(t)$ is often abbreviated as $\bm s$.}
 
-There exist two lemmas facilitating the derivation of the finite time convergence about the DTSM scheme.
+There exist two lemmas facilitating the derivation of the finite time convergence about the DTSM controller.
 \begin{mylem}
@@
 \dot x_1&=-\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2\\
-\dot x_2&=-\vert x_2\vert^\alpha sgn(x_3)-x_2^3-x_1,\label{eq:normal sliding surface}
+\dot x_2&=-\vert x_2\vert^\alpha sgn(x_3)-x_2^3-x_1,\label{eq:normal sliding mode  surface}
 \end{split}
@@
 \end{align}
-where the definitions of  $t_s$, $t_0$, $\alpha$ are similar to Lemma \ref{lemma:1}. Introducing the scalar $d$ into the Eq.~(\ref{eq:normal sliding surface}) obtains:
+where the definitions of  $t_s$, $t_0$, $\alpha$ are similar to Lemma \ref{lemma:1}. Introducing the scalar $d$ into the Eq.~(\ref{eq:normal sliding mode  surface}) obtains:
 \begin{align}
 \dot x_1&=-d(\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2)\\
-\dot x_2&=-d(\vert x_2\vert^\alpha sgn(x_2)-x_2^3-x_1),\label{eq:more normal sliding surface}
+\dot x_2&=-d(\vert x_2\vert^\alpha sgn(x_2)-x_2^3-x_1),\label{eq:more normal sliding mode  surface}
 \end{align}
@@
 \end{mylem}
-\textcolor{red}{For stabilization of the second-order system shown as~Eq.~(\ref{eq:second-order system}), DTSM control inputs are addressed according the following to theorem.}
+\textcolor{red}{For stabilization of the second-order system shown as~Eq.~(\ref{eq:second-order system}), DTSM control inputs are stated according the following to theorem.}
 \begin{mythm}\label{theorem:1}DTSM Controller Design.
-The states of the system~(\ref{eq:second-order system}) will converge to origins along the surface $\bm s=0$ in finite time, if the inputs are designed as follows:
+The states of the system~(\ref{eq:second-order system}) will converge to origins along the surface $\bm s=0$ in finite time, if the inputs are designed as
 \begin{align}
@@
 \begin{proof}
-\textcolor{red}{For the system~(\ref{eq:second-order system}) with the SM surface~(\ref{eq:dual sliding surface}), according to the equivalent control technique and the sliding surface reaching condition~\cite{Arie1993sliding}, the inputs can be designed as
+\textcolor{red}{For the system~(\ref{eq:second-order system}) with the sliding mode  surface~(\ref{eq:dual sliding mode  surface}), according to the equivalent control technique and the sliding mode  surface reaching condition~\cite{Arie1993sliding}, the inputs can be designed as
 \begin{align}\begin{split}
@@
 are the eauivalent control inputs, which ensure $\dot s_1 = 0$ and $\dot s_2=0$ with $u_i = u_{eqi}$, $i=1,2$.
-The switching inputs are designed as $u_{swi}=-b_i^{-1}k_isgn(s_i)$, $i=1,2$ to guarantee the finite time reaching conditions of the sliding surface.}
+The switching inputs can be selected as $u_{swi}=-b_i^{-1}k_isgn(s_i)$, $i=1,2$ to guarantee the finite time reaching conditions of the sliding mode  surface.}
 
-Considering the Lyapunov function $V=\frac{1}{2}{\bm s}^T\bm s$, its derivative can be written as
+Considering the Lyapunov function $V=\frac{1}{2}{\bm s}^T\bm s$, it has
 \begin{align}
@@
 \end{align*}
-Hence, the system (\ref{eq:second-order system}) converges to the desired SM surface (\ref{eq:dual sliding surface}), and incidentally the convergence time can be calculated according to the finite time convergence theory.
+Hence, the system (\ref{eq:second-order system}) converges to the desired sliding mode  surface (\ref{eq:dual sliding mode  surface}), and incidentally the convergence time can be obtained according to the finite time convergence theory.
 Once the system (\ref{eq:second-order system}) satisfies $\bm s = \bm 0$, the entire system states will be handled by the reduced system:
-\begin{align*}
+\begin{align}
+  \begin{split}
 \dot x_1&=-\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_3\\
-\dot x_3&=-\vert x_3\vert^\alpha sgn(x_3)-x_3^3-x_1.
-\end{align*}\par
+\dot x_3&=-\vert x_3\vert^\alpha sgn(x_3)-x_3^3-x_1\label{eq:reduced system}
+\end{split}
+\end{align}
 \textcolor{red}{The total convergence time can be calculated by dividing the convergence into two phases with respect to the relation of the system states and the DTSM surface, namely, the reaching phase and the sliding phase.
@@
 \end{align}
-where $\hat V = \frac{x_1^2+x_3^2}{2}$ is the Lyapunov function selected for the reduced system.
+where $\hat V = \frac{x_1^2+x_3^2}{2}$ is the Lyapunov function selected for the reduced system~(\ref{eq:reduced system}).
 $t_r$ and $t_s$ stand for the reaching time and the sliding time, respectively.
@@
 \end{proof}
-On the basis of Theorem \ref{theorem:1}, we proceed to develop the parameters in the SM surface design to improve the performance of the reaching phase, and furthermore this modified method makes the design process more flexible.
+On the basis of Theorem \ref{theorem:1}, we proceed to develop the parameters in the sliding mode  surface design to improve the performance of the reaching phase, and furthermore this modified method makes the design process more flexible.
 Consider the system~(\ref{eq:second-order system}) with the surface $\bm s = [s_1,s_2]^T$ described by following expressions:
@@
 s_1 &= x_2+\gamma(\vert x_1\vert^{\alpha} sgn(x_1)+x_1^3)-\lambda x_3\\
-s_2 &= x_4+\gamma(\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3)+\lambda x_1,\label{eq:modified dual sliding surface}
+s_2 &= x_4+\gamma(\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3)+\lambda x_1,\label{eq:modified dual sliding mode  surface}
 \end{split}
@@
 \begin{mythm}\label{theorem:2}Modified DTSM Controller Design.
-The second-order system (\ref{eq:second-order system}) will reach the desired SM surface $\bm s = \bm 0$ shown in~Eq.~(\ref{eq:modified dual sliding surface}) in finite time, and then the system states will converge to zero along the surface $\bm s=\bm 0$ in finite time, if the inputs are designed as follows:
+The second-order system (\ref{eq:second-order system}) will reach the desired sliding mode  surface $\bm s = \bm 0$ shown in~Eq.~(\ref{eq:modified dual sliding mode  surface}) in finite time, and then the system states will converge to origins along the surface $\bm s=\bm 0$ in finite time, if the inputs are expressed as
 \begin{align}
@@
 \end{align}
-where $k_i = l_i+\eta_i$, $i=1,2$; $\eta_i>0$ is a positive scalar value. The total finite convergence time is calculated from:
+where $k_i = l_i+\eta_i$, $i=1,2$; $\eta_i>0$ is a positive scalar. The total finite convergence time is given out directly:
 \begin{align}
@@
 \end{proof}
-In the MDTSM scheme, the performances of the reaching and sliding phases can benefit from suitably selected $\lambda$ and $\gamma$ analytically.
+In the MDTSM control scheme, the performances of the reaching and sliding phases can benefit from suitably selected $\lambda$ and $\gamma$ analytically.
 The establishment of $V(t_0)$ is depended on $\lambda$, if the state $\bm x(t_0)$ has been fixed.
@@
 $\eta$ is definied as the reaching speed, because a suitable $\eta$ can adjust the reaching time as desired in some extent.
-Hence, $\lambda$ cooperates with $\eta$ to manage the reaching phase dynamics, and similarly $\gamma$ is defined as the management parameter of the sliding phase dynamics.
+Hence, $\lambda$ cooperates with $\eta$ to manage the reaching phase dynamics, and similarly the parameter $\gamma$ determine the convergent speed of the sliding phase dynamics.
 \begin{myrem}
-For the proposed designs, the parameter $\gamma$ may be defined as different scalars for the inputs, if so, one can produce the total convergence time as:
+For the proposed designs, the parameter $\gamma$ may be defined as different scalars $\gamma_1$ and $\gamma_2$ for $u_1$ and $u_2$ respectively, such that one can produce the total convergence time as:
 \begin{align}
-t_f = \underbrace{t_0+\frac{\sqrt{2}V^{\frac{1}{2}}(t_0)}{\min(\eta_1,\eta_2)}}_{t_r}+\underbrace{\frac{(2\hat V(t_r))^{\frac{1-\alpha}{2}}}{\min(\gamma_1,\gamma_2)(1-\alpha)}}_{t_s}<\infty,\label{eq:normal total convergence time}
+t_f = \underbrace{t_0+\frac{\sqrt{2}V^{\frac{1}{2}}(t_0)}{\min(\eta_1,\eta_2)}}_{t_r}+\underbrace{\frac{(2\hat V(t_r))^{\frac{1-\alpha}{2}}}{\min(\gamma_1,\gamma_2)(1-\alpha)}}_{t_s}<\infty.\label{eq:normal total convergence time}
 \end{align}
-with $\gamma_i$ corresponding to the original parameter $\gamma$ in input $u_i$.
 \end{myrem}
@@
 
-The finite convergence of the DTSM and MDTSM scheme has been verified clearly, but similar to the conventional terminal SMC, there exists another obstacle in the design mentioned above, i.e., the issue of the singularity in control inputs.
+The finite time convergences of the DTSM and MDTSM controllers have been verified clearly, but similar to the conventional TSM control scheme, there exists another obstacle in the design mentioned above, i.e., the issue of the singularity in control inputs.
 Essentially, the singularity occurs in Eq.~(\ref{eq:modified input}) when $x_1=0$ but $x_2\neq 0$ in $u_1$ (the phenomena happens to $u_2$ under the same condition).
-For coping with the singularity, the nonsingular MDTSM scheme is presented after introducing an analytical technique into the MDTSM scheme based on the following lemma~\cite{feng2013nonsingular}.
+To cope with the singularity, the nonsingular MDTSM control scheme is presented after introducing an analytical technique into the MDTSM controller based on the following lemma~\cite{feng2013nonsingular}.
 \begin{mylem}\label{lemma:3}
@@
 \begin{mythm}\label{theorem:3}
-Consider a second-order system (\ref{eq:second-order system}), and for eliminating the singularity, the inputs are selected to complete the nonsingular MDTSM scheme.
-Introducing the saturation terms~\ref{eq:saturation} into the original inputs yields:
+Consider a second-order system (\ref{eq:second-order system}), and for eliminating the singularity, the inputs are selected to complete the nonsingular MDTSM control scheme.
+Introducing the saturation terms~(\ref{eq:saturation}) into the original inputs yields:
 \begin{align}
@@
 \end{align}
-and one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:second-order system}), providing the finite time convergence using MDTSM technique.
+and one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:second-order system}), providing the finite time convergence using MDTSM control technique.
 \end{mythm}
@@
 For guaranteeing $0<R(u)\le 1$, $u_{max}$ and $u_{min}$ satisfy $u_{min}<0<u_{max}$.
-The external disturbance $g_i(\bm x,t)$, $i=1,2$ inputs $u_i$, $i=1,2$ and system state variables are all bounded, accordingly,
+The external disturbance $g_i(\bm x,t)$, inputs $u_i$, $i=1,2$ and system state variables are all bounded, accordingly,
 \begin{align}\begin{split}
@@
 \end{myas}
-Thanks to the above assumption, we give out the adaptive DTSM scheme.
+Thanks to the above assumption, we can give out the adaptive DTSM controller.
 \begin{mythm}\label{thm:4}
@@
 \end{align}
-with $\nu_i>1$ and $\omega_i(0)>0$, such that the trajectories of the system states can converge to the sliding surfaces in Eq.~(\ref{eq:modified dual sliding surface}).
+with $\nu_i>1$ and $\omega_i(0)>0$, such that the trajectories of the system states can converge to the sliding mode  surfaces in Eq.~(\ref{eq:modified dual sliding mode  surface}).
 \end{mythm}
@@
 &\quad + \varpi_1\nu_1(\omega_1-1)\vert s_1\vert+\varpi_2\nu_2(\omega_2-1)\vert s_2\vert\\
-&\le -\varpi_1(\nu_1-1)\vert s_1\vert-\varpi_2(\nu_2-1)\vert s_2\vert\le 0
-\end{split}\end{align}\label{V linmitation}
+&\le -\varpi_1(\nu_1-1)\vert s_1\vert-\varpi_2(\nu_2-1)\vert s_2\vert\le 0\label{V linmitation}
+\end{split}\end{align}
 $\dot V$ is therefore negative semi-deﬁnite while $V_1$ is positive deﬁnite.
-Since  $s_i$ is bounded according to assumption~\ref{myas:1}, we can have $\lim_{t\to\infty}V<\infty$ and proceed to deduce the integration of inequality~(\ref{V linmitation}) to obtain foloowing results
+Since  $s_i$ is bounded according to assumption~\ref{myas:1}, we can have $\lim_{t\to\infty}V<\infty$ and proceed to deduce the integration of inequality~(\ref{V linmitation}) to obtain following results
 \begin{align}\begin{split}
@@
 \end{split}\end{align}
-Hence we can conclude the sliding dynamics are asymptotically stable in the light of Barbalat’s lemmas.
+Hence we can conclude that the sliding dynamics are asymptotically stable in the light of Barbalat’s lemmas.
 Here the proof completes, and the system states can converge to origins by referring to the analyses in Theorem~\ref{theorem:1}.
@@
 When the input $u_1$ equals to $u_2$ in system~(\ref{eq:second-order system}), the number of the inputs is fewer than the degree of the freedom, which leads to the underactuated issue.
-These underactuated systems are ubiquitous in the scientific field, because fewer actuators may decrease the mass and save the energy.
-Cooperating with the hierarchical sliding mode methodology, the presented MDTSM scheme can control this kind of systems~\cite{wang2004design}.
-We give the hierarchical MDTSM controller directly.
+These underactuated systems are ubiquitous and welcomed in the scientific and engineering fields, because fewer actuators may decrease the mass and save the energy.
+Cooperating with the hierarchical sliding mode methodology, the presented MDTSM control law can stabilize this kind of systems~\cite{wang2004design}.
+Here, we provide the hierarchical MDTSM controller directly.
 \begin{mythm}
@@
 \end{align}
-where the conditions of variables are same to the system~(\ref{eq:second-order system}). Construct the SM surfaces as:
+where the conditions of variables are same to the system~(\ref{eq:second-order system}). Construct the sliding mode  surfaces as:
 \begin{align}
@@
 \end{align}
-where $c_1$ and $c_2$ are suitable positive constants, and $s_1$ and $s_2$ have been defined in Eq.~(\ref{eq:dual sliding surface}).
+where $c_1$ and $c_2$ are suitable positive constants, and $s_1$ and $s_2$ have been defined in Eq.~(\ref{eq:dual sliding mode  surface}).
 Adopting the equivalent control design method deduces the individual equivalent inputs:
@@
 \end{align}
-Substituting the input~(\ref{eq:underactuated input}) into Eq.~(\ref{eq:underactuated Lyapunov}) one can obtain
+Substituting the input~(\ref{eq:underactuated input}) into Eq.~(\ref{eq:underactuated Lyapunov}) leads to
 \begin{align}
@@
 As $\vert g_i(\bm x)\vert<l_i$ exists, a big enough $\eta_u$ may be chosen to guarantee the reaching condition of the surface $S$.
-The proof of the stability of the desired sliding surfaces $s_1$ and $s_2$ is same to the one in \cite{wang2004design}, and omitted here.
+The proof of the stability of the desired sliding mode  surfaces $s_1$ and $s_2$ is same to the one in \cite{wang2004design}, and omitted here.
 This completes the proof.
@@
 \section{MDTSM controller design for rigid manipulators}\label{sec:3}
-In this section, the MDTSM scheme designed for the stabilization of the rigid $n$-link robotic manipulator is discussed.
-Firstly, we consider the $2$-link robotic manipulator dynamics described using Eular Lagrange equation~\cite{feng2002non}:
+In this section, the MDTSM controller designed for the stabilization of the rigid $n$-link robotic manipulator is discussed.
+Firstly, we consider the $2$-link robotic manipulator dynamics~\cite{feng2002non}:
 \begin{align}
@@
 where $\bm q\in R^{2} $ is the joint angular position vector; ${M(\bm q)}\in R^{2\times 2}$ is the inertia matrix; ${C(\bm q,\dot{\bm q})}\in R^{2\times 1}$ denotes Coriolis and centrifugal forces; ${g(\bm q)}\in R^{2\times 1}$ stands for the gravitational torque; $\bm{\tau}\in R^{2\times 1}$ is referred to as the joint torques; $\bm d\in R^{2\times 1}$ expresses the bounded disturbance vector.
-Normally, there exist some uncertainties in the manipulator, producing the dynamic equations:
+Normally, there exist some uncertainties in the manipulator, and the dynamic equations are revised as
 \begin{align}
@@
 \end{align}
-With the purpose of simplifying the proceeding derivation, some symbol definitions for vector operating are presented in advance.
+With the purpose of simplifying the proceeding derivation, some symbol definitions for vector operation are presented in advance.
 For expressing the $n$-dimension vector including a sort of compound functions, the following symbol is introduced:
@@
 \end{align*}
-On the basis of the above results, one can design the DTSM scheme for the $2$-link robotic manipulator by utilizing the following theorem.
+On the basis of the above results, one can design the DTSM controller for the $2$-link robotic manipulator by utilizing the following theorem.
 \begin{mythm}\label{theorem:4}
@@
 \end{align}
-and $\Vert\bm s\Vert\neq 0$, hence, the desired SM surface~(\ref{eq:lagrangian surface}) can be reached in finite time.
+and $\Vert\bm s\Vert\neq 0$, hence, the desired sliding mode  surface~(\ref{eq:lagrangian surface}) can be reached in finite time.
 Once the reaching condition is satisfied, one can get the reduced system by substituting $\bm s = \bm 0$ into the system~(\ref{eq:lagrangian system}).
-It owns the form similar to Eq.~(\ref{eq:normal sliding surface}), and therefore, adopting Theorem \ref{theorem:2} drives the reduced system converging to the origin in finite time.
+It owns the form similar to Eq.~(\ref{eq:normal sliding mode  surface}), and therefore, adopting Theorem \ref{theorem:2} drives the reduced system converging to the origin in finite time.
 The proof is completed.
@@
 \begin{myrem}
-At this point, the MDTSM scheme for $2$-link robotic manipulator has been demonstrated.
-We proceed to consider a $n$-link robotic manipulator where $n$ is an even number, and the desired sliding surface is selected as
+At this point, the MDTSM controller for $2$-link robotic manipulator has been demonstrated.
+We proceed to consider a $n$-link robotic manipulator where $n$ is an even number, and the desired sliding mode  surface is selected as
 \begin{align}
@@
 Referring to Theorem \ref{theorem:4}, it's easy to obtain the MDTSM input for the even $n$-link manipulator.
-Essentially, this technique requires that the SM surface has to consist of $n/2$ pairs of individual sliding surfaces, in another words, this design for the surface can be regarded to design the SM surfaces for the $n/2$ sub-systems.\par
-Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension can be excluded using conventional TSM scheme, which results in that the remained $n-1$-link manipulator can be controlled by the proposed MDTSM scheme.
+Essentially, this technique requires that the sliding mode  surface has to consist of $n/2$ pairs of individual sliding mode  surfaces, in another words, this design for the surface can be regarded to design the sliding mode  surfaces for the $n/2$ sub-systems.\par
+Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence one individual dimension can be controlled by using the conventional TSM control scheme, which results in that the remained $n-1$-link manipulator can be controlled by the proposed MDTSM control scheme.
 \end{myrem}
 \begin{myrem}
-The singularity of the MDTSM scheme for the robotic manipulator can be removed using the technique introduced in Theorem \ref{theorem:3}.
+The singularity of the MDTSM controller for the robotic manipulator can be removed by using the technique introduced in Theorem \ref{theorem:3}.
 \end{myrem}
@@
 One can also use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the DTSM control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically.
-For handling the chattering, the $sign(x)$ is replaced with $sat(x,\delta)$, and the boundedness thickness can be selected as $\delta=1\times 10^{-4}$.
+For handling the chattering, the $sign(x)$ can be replaced with $sat(x,\delta)$, and the boundedness thickness can be selected as $\delta=1\times 10^{-4}$.
 \textcolor{red}{Incorporating the adaptive MDTSM technique, the manipulator dynamics subjected to the input limitation can also been stabilized as desired.}
@@
 \section{Simulation studies}\label{sec:4}
-In this section, three simulations will be presented, namely, a verification on the effectiveness of the DTSM and MDTSM schemes, an underactuated example and the robotic manipulator stabilization evaluating the performance of the proposed control schemes.
+In this section, three simulations will be presented, namely, a verification on the effectiveness of the DTSM and MDTSM controllers, an underactuated example and the robotic manipulator stabilization, to evaluate the performance of the proposed control schemes.
 \subsection{Effectiveness study}
@@
 \end{align*}
-and hence, based on the analyses in Theorem~\ref{theorem:1}, $l_1>0.1$ and $l_2>0.8$ are determined accordingly to guarantee the reaching condition of the desired sliding surface.
-Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation second-order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
-The system is supposed to be conducted to the desired state $\bm x_d=(0,0,0,0)$ from a prescript state $\bm x_0=(1.2,1.2,1.2,1.2)$.
-Admittedly, this prescript condition leads to a lager initial reaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding surface, therefore a large reaching speed $k$ is required correspondingly.
+and hence, based on the analyses in Theorem~\ref{theorem:1}, let $l_1>0.1$ and $l_2>0.8$ guarantee the reaching condition of the desired sliding mode  surface.
+Also, the inputs $u_1$ and $u_2$ can be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation second-order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
+The system is supposed to be conducted to the desired condition $\bm x_d=(0,0,0,0)$ from a prescript condition $\bm x_0=(1.2,1.2,1.2,1.2)$.
+Admittedly, this prescript condition leads to a lager initial reaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding mode  surface, therefore a large reaching speed $k$ is required correspondingly.
 The control parameters are chosen as: $\alpha = 0.6$, $\lambda = 0.5$, $\gamma = 3$ and $k = 20$.
 Besides the large reaching speed selected, $\gamma$ accelerates the convergence in the sliding phase indirectly.
-Therefore the design of the MDTSM controller for the system~(\ref{eq:simulation second-order system}) is finished, and the corresponding simulation results are illustrated from Figure~\ref{Figure:2} to Figure~\ref{Figure:3}.\par
-From Figure~\ref{Figure:2}, it's apparent that the states converge to their desired states.
+Therefore the design of the MDTSM controller for the system~(\ref{eq:simulation second-order system}) is finished, and the corresponding simulation results are illustrated from Figure~\ref{Figure:2} to Figure~\ref{Figure:3}.
+
+From Figure~\ref{Figure:2}, it's apparent that all the states converge to zero as desired.
 \textcolor{red}{For the nominal system~(\ref{eq:simulation second-order system}) handled by utilizing the MDTSM controller, accrording to Eq.~(\ref{eq:total convergence time}) and simulation datas, we can calculate the maximum theoretical finite convergence time $t_f=5.2609s$ directly.
@@
 Hence, from the view of the convergence time, the simulation results are in accordance with the theoretical analyses.} Figure~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely related to $\eta$, for the purpose of avoiding the large chattering, the boundary layer technique is adopted.
-Although the states have been adjusted to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range.
+Although the states have been driven to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range.
 The nature of the situation mentioned above means that the fluctuating inputs compensate the error caused by the disturbance.\par
@@
 Figure~\ref{Figure:9} shows the state response curves of the overhead crane system controlled using the HDSM control scheme, and the results show that the controller stabilize the displacement at $6s$ approximately, though the disturbance exists in the system.
-One can find that the swing angle is fluctuating in a fairly small range, the boundary of which is not more than $1\times 10^-3rad$, and this phenomena is reasonable and also occurs in the stable hierarchical SMC scheme~\cite{wang2004design}.
+One can find that the swing angle is fluctuating in a fairly small range, the boundary of which is no more than $1\times 10^-3rad$, and this phenomena is reasonable and also occurs in the stable hierarchical SMC scheme~\cite{wang2004design}.
 \begin{figure}
@@
 
-This section will give a set of simulation to examine the performance of the MDTSM controller in tracking the certain angle condition.
-The behavior of the manipulator should fulfill the initial and desired condition, namely, $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$.
-In order to ensure the stability and a fast convergence speed, the control parameters are chosen conservatively to make the manipulator track the desired attitude in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $k = 150$.
-The TSM scheme, as a comparison, is also implemented to regulate the behavior of the manipulator:
+This section will give a set of simulation to examine the step response performance of the MDTSM controller.
+The behavior of the manipulator should fulfill the initial and desired conditions, namely, $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$.
+In order to ensure the stability and the fast convergence speed, the control parameters are chosen conservatively to make the manipulator stable in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $k = 150$.
+The TSM controller, as a comparison, is also implemented to regulate the behavior of the manipulator:
 \begin{align}
@@
 The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}.
-Comparatively speaking, $q_1$ reaches the desired state at about $2.3s$ with the MDTSM scheme, the reaching time of which is approximating $1s$ less than of the TSM scheme, and $q_2$ performs similar behaviors with a reasonable variable range of the angular rates.
-\textcolor{red}{From the results shown in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}, we can find that the maximum theoretical finite convergence time $t_f=3.0843s$, which can be obtained directly accoring to Eq.~(\ref{eq:total convergence time}) and simulation datas, is more than $2.3s$, the convergence time of the simulation result.
+\textcolor{red}{For the MDTSM controller, the jiont~1 finishes its desired behaviour at about $2.3s$, and meanwhile the joint~2 spends about $1.7s$ completing the desired mission.
+Also, by observing the results, we can find that the stabilization time of the proposed method is less than the TSM controller's, and the regulating process of the manipulators is steady and reasonable.
+We can calculate the maximum theoretical finite convergence time $t_f=3.0843s$, which can be obtained directly accoring to Eq.~(\ref{eq:total convergence time}) and simulation datas, is more than $2.3s$, the convergence time of the simulation result.
 Hence, we can conclude that the results have verified the analyses about the convergence time in Section~\ref{sec:2}.
-For the MDTSM controller, the jiont~1 finishes its desired behaviour at about $2.3s$, and meanwhile the joint~2 spends about $1.6s$ completing the desired mission.
-Also, by observing the results, we can find that the stabilization time of the proposed method is less  than the TSM controller's, and the regulating process of the manipulators is steady and reasonable.
 The control torques of the joints are depicted in Figure~\ref{Figure:torque}.
 It is obvious that the torques of the two jionts are both switching dramatically at the beginning, and this phenomenon is caused directly by the rapidly changing sliding mode dynamics $s_i$.
-Moreover, at about $1.7s$, all the joint states are regulated to locate in the vicinity of the origin, and the boundary layer technique works to generate a continuous torque in the subsequent time.} Therefore these results show that the MDTSM control scheme can achieve the regulation of the manipulator effectively.
+Moreover, at about $1.7s$, all the joint states are regulated to locate in the vicinity of the origin, but the sliding mode dynamics do not yet enter the boundary layer $s_i< \delta$.
+This switching inputs last about $2.7s$ before reaching the boundary layer.
+After $2.7s$ boundary layer technique works to generate continuous torques, which maintain a reasonable constant in the subsequent time, since the overall system have been stable.} Therefore these results show that the MDTSM control scheme can achieve the regulation of the manipulator effectively.
 \begin{figure}
@@
  \textcolor{red}{The simulation results are demonstrated in Figure~\ref{Figure:6} and Figure~\ref{Figure:7}, which plot the trajectories of joints of the manipulator~(\ref{eq:manipulator}) regulated by adopting the MDTSM controller.
-In Figure~\ref{Figure:6}, the error between the variable desired signal and the joint angle $q_1$ keeps decreasing frome the initial state, and the two trajectories reach a confluence at about $3s$, which means that $q_1$ has absolutely tracked the variable desired signal, and the similar conclusion about $q_2$ can also be obtained from the results in Figure~\ref{Figure:7}.
+In Figure~\ref{Figure:6}, the tracking error between the variable desired signal and the joint angle $q_1$ keeps decreasing from the initial status, and the two trajectories reach a confluence at about $3s$, which means that $q_1$ has absolutely tracked the variable desired signal.
+The similar conclusion about $q_2$ can also be obtained from the results in Figure~\ref{Figure:7}.
+From the enlarged figures, we can detect that the controller perform the high-precision tracking due to the completely coincident curves after $3s$.
+In addition, the great slopes of the tangent the tracking curves guarantee that the curves can converge to the desired signal curves in short time, and also lead to small overshoot in joint~1 angle regulation, which is reasonable and does not affect the tracking performance in the subsequent time.
 Taken as a whole, the control system completes the tracking mission at about $3.2s$ from the prescript initial conditions, which performs the smoothly tracking motion subjected to the variable desired signals.}
@@
 Consider the case that there exist the input limitation in the manipulator model~(\ref{eq:manipulator}), and without loss of generality, the maximum torque of the joint is $50Nm$.
-Reviewing the joint 1 torque shown in enlarged details of  Figure~\ref{Figure:torque}, we can find that the torque exceeds the reasonable torque upper limit $50Nm$ around $2.3s$.
-Hence, to overcom this issue, the adaptive MDTSM controller is applied to diminish the effect of the input limitation and to guarantee the rigorous stability analyses of the manipulator dynamics.
-The results shown in Figure~\ref{Figure:limitation_torque} indicate that the joint torques are limited in the region $[-50,50]Nm$ from $0.2s$ to $0.4s$, while in the Figure~\ref{Figure:limitation_q} the trajectories of the manipulator dynamics are still under control.
+Reviewing the torque curve of joint~1  shown in enlarged details of  Figure~\ref{Figure:torque}, we can find that the torque exceeds the reasonable torque upper limit $50Nm$ around $2.3s$.
+If we still use the MDTSM controller to stabilize the system subjected to input limitation, we can not get the same results as shown in Figure~\ref{Figure:torque}, and this is because that the limitation hamper the rigorous theoretical analyses of Theorem~\ref{theorem:2}.
+Hence, to overcom this issue, the adaptive MDTSM controller is applied to diminish the effect of the input limitation and to guarantee the rigorous stability analyses.}
+
+\textcolor{red}{Here we examine the step response of the adaptive MDTSM control scheme for the robotic manipulator dynamics, since the step response is a severe challenge to the controller.
+Accordingly, the initial and desired conditions are $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$, respectively.
+The design parameters of the adaptive MDTSM controller can be selected as $\varpi_1=50$, $\varpi_2=30$, $\varphi_1=\varphi_2=0.01$, $\nu_1 = 5$, $\nu_2=6$, $\omega_1=\omega_2=1$ to satisfy the parameter conditions in Theorem~\ref{thm:4}.
+In addition, for better tracking performance, the boundary layer thickness is revised as $\delta=0.1$.
+}
+
+\textcolor{red}{The results shown in Figure~\ref{Figure:limitation_torque} indicate that the joint torques are limited in the region $[-50,50]Nm$ from $0s$ to $0.4s$, while the trajectories in the Figure~\ref{Figure:limitation_q} demonstrates that the manipulator dynamics are still under control.
+The limitations occur in the beginning stage of the regulation, since the great tracking errors leads to the great command inputs.
 Moveover the boundary layer technique works after $0.4$ and generates continuous torques in the subsequent time.
-In particular, compared to the results from Figure~\ref{Figure:4} and Figure~\ref{Figure:torque}, we can see that the rise time of the adaptive MDTSM controller is less, and the incontinuous joint torques disappear earlier.
-Hence, we can conclude that the proposed adaptive MDTSM controller can regulate the joints of the manipulator subjectd to the input limitation.}
+Compared to the results in Figure~\ref{Figure:torque}, we can find detect that the boundary layer of the adaptive MDTSM controller functions earlier, and this is because that the thickness is modified as $\delta=1\times 10^{-1}$ from $\delta=1\times 10^{-4}$.
+It implies that $s_i<\delta$ appears earlier for the adaptive MDTSM controller than the MDTSM controller.
+Also, compared to the results from Figure~\ref{Figure:4}, we can find that the rise time of the adaptive MDTSM controller is less, although the torques are limited strictly.
+Hence, we can conclude that the proposed adaptive MDTSM controller can regulate the robotic manipulator subjectd to the input limitation, and the control performance is even better than the MDTSM controller for the system without input limitation in some extent.}
 \begin{figure}
@@
 \includegraphics[width=0.7\textwidth]{paper3_fig_limitation_q.eps}
-\caption{Trajectories of manipulator dynamics subjected to the input limitation}
+\caption{Trajectories of manipulator dynamics subjected to input limitation}
 \label{Figure:limitation_q}
@@
 \includegraphics[width=0.7\textwidth]{paper3_fig_limitation_torque.eps}
-\caption{Trajectories of joint torques subjected to the input limitation}
+\caption{Trajectories of joint torques subjected to  input limitation}
 \label{Figure:limitation_torque}
@@
 The method integrates two individual subsystems as a unity, then builds the surfaces and inputs for it to complete the controller design.
-The control scheme can guarantee the reaching condition of the desired sliding surface, meanwhile the system states converge to the origin along the desired SM surface.
+The control scheme can guarantee the reaching condition of the desired sliding mode  surface, meanwhile the system states converge to the origin along the desired sliding mode  surface.
 Also, the entire convergence time can be calculated accordingly.
@@
 For dealing with the under actuated characteristics which may appear in the system, the HDTSM control is derived, and the overhead crane example verifies its effectiveness.
-However, the control parameters selection is still a challenge especially in the HDTSM scheme, and we will effort to excavate a full order dual TSM methodology in the future for removing the obstacle caused by parameters essentially.
+However, the control parameters selection is still a challenge especially in the HDTSM control scheme, and we will effort to excavate a full order dual TSM methodology in the future for removing the obstacle caused by parameters essentially.
 \section{Acknowledgment}

### 2016-11-15 paper3_manuscript.tex
20161115

@@
 This paper proposes a dual terminal sliding mode control scheme for tracking tasks of rigid robotic manipulators.
-\textcolor{red}{As a signiﬁcant novelty, the presented design technique integates the individual sliding mode  surfaces to achieve the finite time convergence of tracking errors utilizing specially designed construct, and accordingly the convergence time is easily obtained due to the integral design.
+\textcolor{red}{As a signiﬁcant novelty, the presented design technique integrate the individual sliding mode  surfaces to achieve the finite time convergence of tracking errors utilizing specially designed construct, and accordingly the convergence time is easily obtained due to the integral design.
 The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue is solved by introducing the hierarchical methodology into the basic dual sliding mode controller.
-The proposed method can easily combine with the adaptive technique to  eliminate the adverse effect caused by the input limitation in the rigious stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the tracking tasks of the rigid robotic manipulator.
+The proposed method can easily combine with the adaptive technique to  eliminate the adverse effect caused by the input limitation in the rigorous stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the tracking tasks of the rigid robotic manipulator.
 Simulation results validate the theoretical analyses about the proposed method.
@@
 designed a robust adaptive sliding mode method to ensure the asymptotically stability of a boost converter~\cite{oucheriah2013pwm}.
-Roughly speaking, the SMC scheme is competent for normal scientific missions, due to its insensitivity to parameteric uncertainties and external disturbances, however, there still exist some obstacles, such as noncontinuous switching inputs in high frequency and low convergence speed of the tracking errors~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some high-precision engineering applications~\cite{fridman2011sliding}.}
+Roughly speaking, the SMC scheme is competent for normal scientific missions, due to its insensitivity to parametric uncertainties and external disturbances, however, there still exist some obstacles, such as noncontinuous switching inputs in high frequency and low convergence speed of the tracking errors~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some high-precision engineering applications~\cite{fridman2011sliding}.}
 
@@
 In this paper, an integral sliding mode  surface design technique breaks the barriers mentioned above, and the novel surface includes two designed variables to guarantee the integral finite time convergence.
-Moreover, nonsingularities of the TSM control scheme, chattering suppressions, underactuated applications and input limitations are also considered in the controller design.}
+Moreover, nonsingularity of the TSM control scheme, chattering suppressions, underactuated applications and input limitations are also considered in the controller design.}
 
@@
 A modified DTSM (MDTSM) control scheme is presented to regulate the motion of the $n$-link robotic manipulators, and the case subjected to input limitations is also taken into consideration.
-The remained paper is organized as follows: Section~\ref{sec:2} introduces the DTSM controller, and the finite time convergences of the reaching and sliding phase are discussed.
-Furthermore, we provide the DTSM control scheme with extra design parameters to obtain the MDTSM controller, which performs better in theoretical analyses; for stabilizing underactuated systems, the HDTSM design is also developed in this section.
+The remained paper is organized as follows: Section~\ref{sec:2} introduces the DTSM controller, and the finite time convergence is discussed.
+Furthermore, we provide the DTSM control scheme with extra design parameters to obtain the MDTSM controller, which performs better in theoretical analyses; for stabilizing underactuated systems, the HDTSM controller design is also developed in this section.
 In Section~\ref{sec:3}, the MDTSM control law is applied to the motion control system of the $n$-link robotic  manipulator, and the stability analyses are also carried out.
@@
 Exactly, $\lambda$ affects the reaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V=\bm s^T\bm s = \bm 0,\forall t\ge t_r$.
-$\eta$ is definied as the reaching speed, because a suitable $\eta$ can adjust the reaching time as desired in some extent.
+$\eta$ is defined as the reaching speed, because a suitable $\eta$ can adjust the reaching time as desired in some extent.
 Hence, $\lambda$ cooperates with $\eta$ to manage the reaching phase dynamics, and similarly the parameter $\gamma$ determine the convergent speed of the sliding phase dynamics.
@@
 
-The finite time convergences of the DTSM and MDTSM controllers have been verified clearly, but similar to the conventional TSM control scheme, there exists another obstacle in the design mentioned above, i.e., the issue of the singularity in control inputs.
+The finite time convergence of the MDTSM controller has been verified clearly, but similar to the conventional TSM control scheme, there exists another obstacle in the design mentioned above, i.e., the issue of the singularity in control inputs.
 Essentially, the singularity occurs in Eq.~(\ref{eq:modified input}) when $x_1=0$ but $x_2\neq 0$ in $u_1$ (the phenomena happens to $u_2$ under the same condition).
-To cope with the singularity, the nonsingular MDTSM control scheme is presented after introducing an analytical technique into the MDTSM controller based on the following lemma~\cite{feng2013nonsingular}.
+To cope with the singularity, the nonsingular MDTSM control scheme is presented after introducing the analytical technique into the MDTSM controller based on the following lemma~\cite{feng2013nonsingular}.
 \begin{mylem}\label{lemma:3}
@@
 \end{align}
-whree $f_b(u) = R(u)u$ is a bounded function, which owns the properties as follows:
+where $f_b(u) = R(u)u$ is a bounded function, which owns the properties as follows:
 \begin{align}\begin{split}
@@
 \end{split}\end{align}
-$\dot V$ is therefore negative semi-deﬁnite while $V_1$ is positive deﬁnite.
+$\dot V$ is therefore negative semi-definite while $V_1$ is positive definite.
 Since  $s_i$ is bounded according to assumption~\ref{myas:1}, we can have $\lim_{t\to\infty}V<\infty$ and proceed to deduce the integration of inequality~(\ref{V linmitation}) to obtain following results
@@
 \end{split}\end{align}
-Hence we can conclude that the sliding dynamics are asymptotically stable in the light of Barbalat’s lemmas.
+Hence we can conclude that the sliding dynamics are asymptotically stable in the light of Barbalat lemma.
 Here the proof completes, and the system states can converge to origins by referring to the analyses in Theorem~\ref{theorem:1}.
@@
 One can also use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the DTSM control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically.
-For handling the chattering, the $sign(x)$ can be replaced with $sat(x,\delta)$, and the boundedness thickness can be selected as $\delta=1\times 10^{-4}$.
+For handling the chattering, the $sign(x)$ can be replaced with $sat(x,\delta)$, and the boundary layer thickness can be selected as $\delta=1\times 10^{-4}$.
 \textcolor{red}{Incorporating the adaptive MDTSM technique, the manipulator dynamics subjected to the input limitation can also been stabilized as desired.}
@@
 \section{Simulation studies}\label{sec:4}
-In this section, three simulations will be presented, namely, a verification on the effectiveness of the DTSM and MDTSM controllers, an underactuated example and the robotic manipulator stabilization, to evaluate the performance of the proposed control schemes.
+In this section, three simulations will be presented, namely, the verification on the effectiveness of the DTSM and MDTSM controllers, the underactuated example and the robotic manipulator stabilization, to evaluate the performance of the proposed control schemes.
 \subsection{Effectiveness study}
@@
 From Figure~\ref{Figure:2}, it's apparent that all the states converge to zero as desired.
-\textcolor{red}{For the nominal system~(\ref{eq:simulation second-order system}) handled by utilizing the MDTSM controller, accrording to Eq.~(\ref{eq:total convergence time}) and simulation datas, we can calculate the maximum theoretical finite convergence time $t_f=5.2609s$ directly.
+\textcolor{red}{For the nominal system~(\ref{eq:simulation second-order system}) handled by utilizing the MDTSM controller, according to Eq.~(\ref{eq:total convergence time}) and simulation data, we can calculate the maximum theoretical finite convergence time $t_f=5.2609s$ directly.
 The system states, in other words, can be stable in no more than $5.2609s$ theoretically.
@@
 The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}.
-\textcolor{red}{For the MDTSM controller, the jiont~1 finishes its desired behaviour at about $2.3s$, and meanwhile the joint~2 spends about $1.7s$ completing the desired mission.
+\textcolor{red}{For the MDTSM controller, the joint~1 finishes its desired behaviour at about $2.3s$, and meanwhile the joint~2 spends about $1.7s$ completing the desired mission.
 Also, by observing the results, we can find that the stabilization time of the proposed method is less than the TSM controller's, and the regulating process of the manipulators is steady and reasonable.
-We can calculate the maximum theoretical finite convergence time $t_f=3.0843s$, which can be obtained directly accoring to Eq.~(\ref{eq:total convergence time}) and simulation datas, is more than $2.3s$, the convergence time of the simulation result.
+We can calculate the maximum theoretical finite convergence time $t_f=3.0843s$, which can be obtained directly according to Eq.~(\ref{eq:total convergence time}) and simulation data, is more than $2.3s$, the convergence time of the simulation result.
 Hence, we can conclude that the results have verified the analyses about the convergence time in Section~\ref{sec:2}.
 The control torques of the joints are depicted in Figure~\ref{Figure:torque}.
-It is obvious that the torques of the two jionts are both switching dramatically at the beginning, and this phenomenon is caused directly by the rapidly changing sliding mode dynamics $s_i$.
+It is obvious that the torques of the two joints are both switching dramatically at the beginning, and this phenomenon is caused directly by the rapidly changing sliding mode dynamics $s_i$.
 Moreover, at about $1.7s$, all the joint states are regulated to locate in the vicinity of the origin, but the sliding mode dynamics do not yet enter the boundary layer $s_i< \delta$.
@@
 
-\textcolor{red}{At this point, we have verifed the feasibility of the MDTSM controller on step responses of the joints of the manipulator, and in mostly engineering applications, manipulators are required to track the variable desied signals, which own the actual physical meanings, such as polish, machine tools and laser beam cutting.
+\textcolor{red}{At this point, we have verified the feasibility of the MDTSM controller on step responses of the joints of the manipulator, and in mostly engineering applications, manipulators are required to track the variable desired signals, which own the actual physical meanings, such as polish, machine tools and laser beam cutting.
 Accordingly, the tracking performance of the robotic manipulator controlled by the proposed methods is studied in this section, and we continue to use the parameters of the controller mentioned above, and the mission condition is changed as follows:}
@@
 The limitations occur in the beginning stage of the regulation, since the great tracking errors leads to the great command inputs.
-Moveover the boundary layer technique works after $0.4$ and generates continuous torques in the subsequent time.
+Moveover the boundary layer technique works after $0.4s$ and generates continuous torques in the subsequent time.
 Compared to the results in Figure~\ref{Figure:torque}, we can find detect that the boundary layer of the adaptive MDTSM controller functions earlier, and this is because that the thickness is modified as $\delta=1\times 10^{-1}$ from $\delta=1\times 10^{-4}$.
@@
 Also, compared to the results from Figure~\ref{Figure:4}, we can find that the rise time of the adaptive MDTSM controller is less, although the torques are limited strictly.
-Hence, we can conclude that the proposed adaptive MDTSM controller can regulate the robotic manipulator subjectd to the input limitation, and the control performance is even better than the MDTSM controller for the system without input limitation in some extent.}
+Hence, we can conclude that the proposed adaptive MDTSM controller can regulate the robotic manipulator subjected to the input limitation, and the control performance is even better than the MDTSM controller for the system without input limitation in some extent.}
 \begin{figure}

### 2016-11-16 paper3_manuscript.tex
20161116

@@
 This paper proposes a dual terminal sliding mode control scheme for tracking tasks of rigid robotic manipulators.
-\textcolor{red}{As a signiﬁcant novelty, the presented design technique integrate the individual sliding mode  surfaces to achieve the finite time convergence of tracking errors utilizing specially designed construct, and accordingly the convergence time is easily obtained due to the integral design.
+\textcolor{red}{As a signiﬁcant novelty, the presented design technique integrates the individual sliding mode  surfaces to achieve the finite time convergence of tracking errors utilizing specially designed construct, and accordingly the convergence time is easily obtained due to the integral design.
 The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue is solved by introducing the hierarchical methodology into the basic dual sliding mode controller.
@@
 Then the sliding mode dynamics function to drive the system states to the origins along the ideal surfaces in the second step, which is usually known as the sliding phase.
-The reaching phase usually requires the states reach the ideal sliding mode surfaces in finite time, and suitably selected Lyapunov function and control parameters may accelerate this process; the sliding phase is related to the designed ideal sliding mode  surfaces closely, and trivial design techniques can guarantee the asymptotically stability of the reduced system~\cite{mu2016switching}.
+The reaching phase usually requires the states to reach the ideal sliding mode surfaces in finite time, and suitably selected Lyapunov function and control parameters may accelerate this process; the sliding phase is related to the designed ideal sliding mode  surfaces closely, and trivial design techniques can guarantee the asymptotically stability of the reduced system~\cite{mu2016switching}.
 To achieve a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and compared with the SMC design mentioned above, the most significant contributions of the TSM concept are introducing the finite time convergence to the sliding phase to complete the global finite time convergence~\cite{mu2016switching}.
@@
 
-\textcolor{red}{Notably, the conventional TSM surface design techniques are similar, since the surfaces are all designed for the single variable based on the finite time stability theory, in another words, only the individual variable and its derivative are concerned on by most designers~\cite{mu2016switching}.
+\textcolor{red}{Notably, the conventional TSM surface design techniques are similar, since the surfaces are all designed for the single variable based on the finite time stability theory, in other words, only the individual variable and its derivative are concerned on by most designers~\cite{mu2016switching}.
 This nature makes the TSM controller become an individual control subsystem, which leads to the complicity of global convergence time in some extent.
@@
 \end{align}
-and oen can select the function $V = \frac{x_1^2+x_2^2}{2}$ to obtain the finite convergence time as follows~\cite{moulay2006finite}:
+and one can select the function $V = \frac{x_1^2+x_2^2}{2}$ to obtain the finite convergence time as follows~\cite{moulay2006finite}:
 %since $\vert x\vert-x^\alpha+\vert x\vert \ge 0,0<\alpha<1$
@@
 \end{mylem}
-\textcolor{red}{For stabilization of the second-order system shown as~Eq.~(\ref{eq:second-order system}), DTSM control inputs are stated according the following to theorem.}
+\textcolor{red}{For stabilization of the second-order system shown as~Eq.~(\ref{eq:second-order system}), DTSM control inputs are stated according the following theorem.}
 \begin{mythm}\label{theorem:1}DTSM Controller Design.
@@
 \end{split}\end{align}
-are the eauivalent control inputs, which ensure $\dot s_1 = 0$ and $\dot s_2=0$ with $u_i = u_{eqi}$, $i=1,2$.
+are the equivalent control inputs, which ensure $\dot s_1 = 0$ and $\dot s_2=0$ with $u_i = u_{eqi}$, $i=1,2$.
 The switching inputs can be selected as $u_{swi}=-b_i^{-1}k_isgn(s_i)$, $i=1,2$ to guarantee the finite time reaching conditions of the sliding mode  surface.}
 
-Considering the Lyapunov function $V=\frac{1}{2}{\bm s}^T\bm s$, it has
+Consider the Lyapunov function $V=\frac{1}{2}{\bm s}^T\bm s$, which has
 \begin{align}
@@
 In the MDTSM control scheme, the performances of the reaching and sliding phases can benefit from suitably selected $\lambda$ and $\gamma$ analytically.
-The establishment of $V(t_0)$ is depended on $\lambda$, if the state $\bm x(t_0)$ has been fixed.
+The establishment of $V(t_0)$ depends on $\lambda$, if the state $\bm x(t_0)$ has been fixed.
 Exactly, $\lambda$ affects the reaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V=\bm s^T\bm s = \bm 0,\forall t\ge t_r$.
 $\eta$ is defined as the reaching speed, because a suitable $\eta$ can adjust the reaching time as desired in some extent.
-Hence, $\lambda$ cooperates with $\eta$ to manage the reaching phase dynamics, and similarly the parameter $\gamma$ determine the convergent speed of the sliding phase dynamics.
+Hence, $\lambda$ cooperates with $\eta$ to manage the reaching phase dynamics, and similarly the parameter $\gamma$ determine the convergence speed of the sliding phase dynamics.
 \begin{myrem}
@@
 Referring to Theorem \ref{theorem:4}, it's easy to obtain the MDTSM input for the even $n$-link manipulator.
-Essentially, this technique requires that the sliding mode  surface has to consist of $n/2$ pairs of individual sliding mode  surfaces, in another words, this design for the surface can be regarded to design the sliding mode  surfaces for the $n/2$ sub-systems.\par
+Essentially, this technique requires that the sliding mode  surface has to consist of $n/2$ pairs of individual sliding mode  surfaces, in other words, this design for the surface can be regarded to design the sliding mode  surfaces for the $n/2$ sub-systems.\par
 Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence one individual dimension can be controlled by using the conventional TSM control scheme, which results in that the remained $n-1$-link manipulator can be controlled by the proposed MDTSM control scheme.
@@
 For handling the chattering, the $sign(x)$ can be replaced with $sat(x,\delta)$, and the boundary layer thickness can be selected as $\delta=1\times 10^{-4}$.
-\textcolor{red}{Incorporating the adaptive MDTSM technique, the manipulator dynamics subjected to the input limitation can also been stabilized as desired.}
+\textcolor{red}{Incorporating the adaptive MDTSM technique, the manipulator dynamics subjected to the input limitation can also be stabilized as desired.}
 \end{myrem}
@@
 Also, the inputs $u_1$ and $u_2$ can be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation second-order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
-The system is supposed to be conducted to the desired condition $\bm x_d=(0,0,0,0)$ from a prescript condition $\bm x_0=(1.2,1.2,1.2,1.2)$.
-Admittedly, this prescript condition leads to a lager initial reaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding mode  surface, therefore a large reaching speed $k$ is required correspondingly.
+The system is supposed to be controlled to the desired condition $\bm x_d=(0,0,0,0)$ from a prescript condition $\bm x_0=(1.2,1.2,1.2,1.2)$.
+Admittedly, this prescript condition leads to a large initial reaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding mode  surface, therefore a large reaching speed $k$ is required correspondingly.
 The control parameters are chosen as: $\alpha = 0.6$, $\lambda = 0.5$, $\gamma = 3$ and $k = 20$.
@@
 At this point, some effectiveness of the proposed MDTSM control scheme has been verified, and in Section \ref{sec:robotica manipulator}, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.
-\begin{figure}
+\begin{figure}[http]
 \centering
@@
 
-\begin{figure}
+\begin{figure}[http]
 \centering
@@
 \label{Figure:3}
+\end{figure}
+\begin{figure}[http]
+\centering
+\includegraphics[width=0.3\textwidth]{paper3_fig8.eps}
+\caption{Overhead crane schematic}
+\label{Figure:8}
 \end{figure}
@@
 One can find that the swing angle is fluctuating in a fairly small range, the boundary of which is no more than $1\times 10^-3rad$, and this phenomena is reasonable and also occurs in the stable hierarchical SMC scheme~\cite{wang2004design}.
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{paper3_fig8.eps}
-\caption{Overhead crane schematic}
-\label{Figure:8}
-\end{figure}
-\begin{figure}
+\begin{figure}[http]
 \centering
@@
 Figure~\ref{Figure:1} is the $2$-link manipulator schematic, the dynamics of which can be explained by the dynamic equations in following forms:
-\begin{figure}
+\begin{figure}[http]
 \centering
@@
 In this model, the uncertainty is brought in by estimated terms, namely, $\bar m_1=0.4$ and $\bar m_2=1.2$ which are all not the actual value obviously.
-In addition, owing to that it sits on many terms in the dynamic equations, it's a severe challenge to guarantee the stability of the system.
 Accordingly, the uncertainty parameters in Eq.~(\ref{eq:manipulator uncertainty}) are assumed to be $\mu_0=10$, $\mu_1=3$, $\mu_2=3$.
@@
 
-The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}.
-\textcolor{red}{For the MDTSM controller, the joint~1 finishes its desired behaviour at about $2.3s$, and meanwhile the joint~2 spends about $1.7s$ completing the desired mission.
-Also, by observing the results, we can find that the stabilization time of the proposed method is less than the TSM controller's, and the regulating process of the manipulators is steady and reasonable.
-We can calculate the maximum theoretical finite convergence time $t_f=3.0843s$, which can be obtained directly according to Eq.~(\ref{eq:total convergence time}) and simulation data, is more than $2.3s$, the convergence time of the simulation result.
-Hence, we can conclude that the results have verified the analyses about the convergence time in Section~\ref{sec:2}.
-The control torques of the joints are depicted in Figure~\ref{Figure:torque}.
-It is obvious that the torques of the two joints are both switching dramatically at the beginning, and this phenomenon is caused directly by the rapidly changing sliding mode dynamics $s_i$.
-Moreover, at about $1.7s$, all the joint states are regulated to locate in the vicinity of the origin, but the sliding mode dynamics do not yet enter the boundary layer $s_i< \delta$.
-This switching inputs last about $2.7s$ before reaching the boundary layer.
-After $2.7s$ boundary layer technique works to generate continuous torques, which maintain a reasonable constant in the subsequent time, since the overall system have been stable.} Therefore these results show that the MDTSM control scheme can achieve the regulation of the manipulator effectively.
-\begin{figure}
+\begin{figure}[http]
 \centering
@@
 \end{figure}
+The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}.
+\textcolor{red}{For the MDTSM controller, the joint~1 finishes its desired behaviour at about $2.3s$, and meanwhile the joint~2 spends about $1.7s$ completing the desired mission.
+Also, by observing the results, we can find that the stabilization time of the proposed method is less than the TSM controller's, and the regulating process of the manipulators is steady and reasonable.
+Through calculation, we can find the maximum theoretical finite convergence time $t_f=3.0843s$, which can be obtained directly according to Eq.~(\ref{eq:total convergence time}) and simulation data, is more than $2.3s$, the convergence time of the simulation result.
+Hence, we can conclude that the results have verified the analyses about the convergence time in Section~\ref{sec:2}.
+The control torques of the joints are depicted in Figure~\ref{Figure:torque}.
+It is obvious that the torques of the two joints are both switching dramatically at the beginning, and this phenomenon is caused directly by the rapidly changing sliding mode dynamics $s_i$.
+Moreover, at about $1.7s$, all the joint states are regulated to locate in the vicinity of the origin, but the sliding mode dynamics do not yet enter the boundary layer $s_i< \delta$.
+This switching inputs last about $2.7s$ before reaching the boundary layer.
+After $2.7s$ boundary layer technique works to generate continuous torques, which maintain a reasonable constant in the subsequent time, since the overall system has been stable.} Therefore these results show that the MDTSM control scheme can achieve the regulation of the manipulator effectively.
 
-\textcolor{red}{At this point, we have verified the feasibility of the MDTSM controller on step responses of the joints of the manipulator, and in mostly engineering applications, manipulators are required to track the variable desired signals, which own the actual physical meanings, such as polish, machine tools and laser beam cutting.
+\textcolor{red}{At this point, we have verified the feasibility of the MDTSM controller on step responses of the joints of the manipulator, and in most engineering applications, manipulators are required to track the variable desired signals, which own the actual physical meanings, such as polish, machine tools and laser beam cutting.
 Accordingly, the tracking performance of the robotic manipulator controlled by the proposed methods is studied in this section, and we continue to use the parameters of the controller mentioned above, and the mission condition is changed as follows:}
@@
 Taken as a whole, the control system completes the tracking mission at about $3.2s$ from the prescript initial conditions, which performs the smoothly tracking motion subjected to the variable desired signals.}
-\begin{figure}
+\begin{figure}[http]
 \centering
@@
 \textcolor{red}{Another important issue that we always meet in engineering applications, is the actuator constraint due to the physical limitation, which can be regarded as the input limitation problem shown in Eq.~(\ref{eq:second-order system subjected to limitation}).
-Consider the case that there exist the input limitation in the manipulator model~(\ref{eq:manipulator}), and without loss of generality, the maximum torque of the joint is $50Nm$.
+Consider the case that there exists the input limitation in the manipulator model~(\ref{eq:manipulator}), and without loss of generality, the maximum torque of the joint is $50Nm$.
 Reviewing the torque curve of joint~1  shown in enlarged details of  Figure~\ref{Figure:torque}, we can find that the torque exceeds the reasonable torque upper limit $50Nm$ around $2.3s$.
 If we still use the MDTSM controller to stabilize the system subjected to input limitation, we can not get the same results as shown in Figure~\ref{Figure:torque}, and this is because that the limitation hamper the rigorous theoretical analyses of Theorem~\ref{theorem:2}.
-Hence, to overcom this issue, the adaptive MDTSM controller is applied to diminish the effect of the input limitation and to guarantee the rigorous stability analyses.}
-
-\textcolor{red}{Here we examine the step response of the adaptive MDTSM control scheme for the robotic manipulator dynamics, since the step response is a severe challenge to the controller.
-Accordingly, the initial and desired conditions are $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$, respectively.
-The design parameters of the adaptive MDTSM controller can be selected as $\varpi_1=50$, $\varpi_2=30$, $\varphi_1=\varphi_2=0.01$, $\nu_1 = 5$, $\nu_2=6$, $\omega_1=\omega_2=1$ to satisfy the parameter conditions in Theorem~\ref{thm:4}.
-In addition, for better tracking performance, the boundary layer thickness is revised as $\delta=0.1$.
-}
-
-\textcolor{red}{The results shown in Figure~\ref{Figure:limitation_torque} indicate that the joint torques are limited in the region $[-50,50]Nm$ from $0s$ to $0.4s$, while the trajectories in the Figure~\ref{Figure:limitation_q} demonstrates that the manipulator dynamics are still under control.
-The limitations occur in the beginning stage of the regulation, since the great tracking errors leads to the great command inputs.
-Moveover the boundary layer technique works after $0.4s$ and generates continuous torques in the subsequent time.
-Compared to the results in Figure~\ref{Figure:torque}, we can find detect that the boundary layer of the adaptive MDTSM controller functions earlier, and this is because that the thickness is modified as $\delta=1\times 10^{-1}$ from $\delta=1\times 10^{-4}$.
-It implies that $s_i<\delta$ appears earlier for the adaptive MDTSM controller than the MDTSM controller.
-Also, compared to the results from Figure~\ref{Figure:4}, we can find that the rise time of the adaptive MDTSM controller is less, although the torques are limited strictly.
-Hence, we can conclude that the proposed adaptive MDTSM controller can regulate the robotic manipulator subjected to the input limitation, and the control performance is even better than the MDTSM controller for the system without input limitation in some extent.}
+Hence, to overcome this issue, the adaptive MDTSM controller is applied to diminish the effect of the input limitation and to guarantee the rigorous stability analyses.}
 \begin{figure}
@@
 \end{figure}
+\textcolor{red}{Here we examine the step response of the adaptive MDTSM control scheme for the robotic manipulator dynamics, since the step response is a severe challenge to the controller.
+Accordingly, the initial and desired conditions are $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$, respectively.
+The design parameters of the adaptive MDTSM controller can be selected as $\varpi_1=50$, $\varpi_2=30$, $\varphi_1=\varphi_2=0.01$, $\nu_1 = 5$, $\nu_2=6$, $\omega_1=\omega_2=1$ to satisfy the parameter conditions in Theorem~\ref{thm:4}.
+In addition, for better tracking performance, the boundary layer thickness is revised as $\delta=0.1$.
+}
+
+\textcolor{red}{The results shown in Figure~\ref{Figure:limitation_torque} indicate that the joint torques are limited in the region $[-50,50]Nm$ from $0s$ to $0.4s$, while the trajectories in the Figure~\ref{Figure:limitation_q} demonstrates that the manipulator dynamics are still under control.
+The limitations occur in the beginning stage of the regulation, since the large tracking errors lead to the great command inputs.
+Moveover the boundary layer technique works after $0.4s$ and generates continuous torques in the subsequent time.
+Compared to the results in Figure~\ref{Figure:torque}, we can find that the boundary layer of the adaptive MDTSM controller functions earlier, and this is because that the thickness is modified as $\delta=1\times 10^{-1}$ from $\delta=1\times 10^{-4}$.
+It implies that $s_i<\delta$ appears earlier for the adaptive MDTSM controller than the MDTSM controller.
+Also, compared to the results from Figure~\ref{Figure:4}, we can find that the rise time of the adaptive MDTSM controller is less, although the torques are limited strictly.
+Hence, we can conclude that the proposed adaptive MDTSM controller can regulate the robotic manipulator subjected to the input limitation, and the control performance is even better than the MDTSM controller for the system without input limitation in some extent.}
 \section{Conclusion}\label{sec:5}
@@
 Also, the entire convergence time can be calculated accordingly.
-Developing the basic DTSM yields the MDTSM controller, providing a solution to eliminating chattering, avoiding singularity and fast convergence.
-For dealing with the under actuated characteristics which may appear in the system, the HDTSM control is derived, and the overhead crane example verifies its effectiveness.
+Developing the basic DTSM yields the MDTSM controller, which provides a solution to eliminating chattering, avoiding singularity and fast convergence.
+For dealing with the underactuated characteristics which may appear in the system, the HDTSM control is derived, and the overhead crane example verifies its effectiveness.
 However, the control parameters selection is still a challenge especially in the HDTSM control scheme, and we will effort to excavate a full order dual TSM methodology in the future for removing the obstacle caused by parameters essentially.

### 2016-11-16 paper3_manuscript.tex
20161116

@@
 Then the sliding mode dynamics function to drive the system states to the origins along the ideal surfaces in the second step, which is usually known as the sliding phase.
-The reaching phase usually requires the states to reach the ideal sliding mode surfaces in finite time, and suitably selected Lyapunov function and control parameters may accelerate this process; the sliding phase is related to the designed ideal sliding mode  surfaces closely, and trivial design techniques can guarantee the asymptotically stability of the reduced system~\cite{mu2016switching}.
+The reaching phase usually requires the states to reach the ideal sliding mode surfaces in finite time, and suitably selected Lyapunov function and control parameters may accelerate this process; the sliding phase is associated with the designed ideal sliding mode  surfaces closely, and trivial design techniques can guarantee the asymptotically stability of the reduced system~\cite{mu2016switching}.
 To achieve a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and compared with the SMC design mentioned above, the most significant contributions of the TSM concept are introducing the finite time convergence to the sliding phase to complete the global finite time convergence~\cite{mu2016switching}.
@@
 Feng et al.
-stated a novel Lagrangian dynamic expression for the the rigid robot, and applied the global TSM control law to manipulate the robotic dynamics ~\cite{feng2002non}.
+stated a novel Lagrangian dynamic expression for the rigid robot, and applied the global TSM control law to manipulate the robotic dynamics ~\cite{feng2002non}.
 In~\cite{kamal2016continuous}, Kamal addressed a continuous homogeneous sliding mode algorithm for a perturbed second-order plant, and the algorithm could be regarded as a combination of TSM and super-twisting sliding mode schemes.}
@@
 The novel DTSM surface is exploited to achieve the finite time convergence, and the reaching and sliding times can both be calculated directly.
-For coping with the underacutated issue, cooperating with the hierarchical sliding mode  surface design methodology, we combine the hierarchical SMC scheme with the DTSM controller to develop a hierarchical dual TSM (HDTSM) control law to ensure the rigorous stability analyses.
+For coping with the underactuated issue, cooperating with the hierarchical sliding mode  surface design methodology, we combine the hierarchical SMC scheme with the DTSM controller to develop a hierarchical dual TSM (HDTSM) control law to ensure the rigorous stability analyses.
 A modified DTSM (MDTSM) control scheme is presented to regulate the motion of the $n$-link robotic manipulators, and the case subjected to input limitations is also taken into consideration.
@@
 \end{mylem}
-\textcolor{red}{For stabilization of the second-order system shown as~Eq.~(\ref{eq:second-order system}), DTSM control inputs are stated according the following theorem.}
+\textcolor{red}{For stabilization of the second-order system shown as Eq.~(\ref{eq:second-order system}), DTSM control inputs are stated according the following theorem.}
 \begin{mythm}\label{theorem:1}DTSM Controller Design.
@@
 \end{align}
-Substituting inputs (\ref{eq:DSM input}) in~Eq.~(\ref{eq:V_1}) yields
+Substituting inputs (\ref{eq:DSM input}) in Eq.~(\ref{eq:V_1}) yields
 \begin{align*}
@@
 However, the system response results in Figure~\ref{Figure:2_20161108} indicate that all the states have been stable after about $1.5s$, which is far less than $t_f$.
-Hence, from the view of the convergence time, the simulation results are in accordance with the theoretical analyses.} Figure~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely related to $\eta$, for the purpose of avoiding the large chattering, the boundary layer technique is adopted.
+Hence, from the view of the convergence time, the simulation results are in accordance with the theoretical analyses.} Figure~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely associated with $\eta$, for the purpose of avoiding the large chattering, the boundary layer technique is adopted.
 Although the states have been driven to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range.
@@
 The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}.
-\textcolor{red}{For the MDTSM controller, the joint~1 finishes its desired behaviour at about $2.3s$, and meanwhile the joint~2 spends about $1.7s$ completing the desired mission.
+\textcolor{red}{For the MDTSM controller, the joint~1 finishes its desired behavior at about $2.3s$, and meanwhile the joint~2 spends about $1.7s$ completing the desired mission.
 Also, by observing the results, we can find that the stabilization time of the proposed method is less than the TSM controller's, and the regulating process of the manipulators is steady and reasonable.

### 2016-11-16 paper3_manuscript.tex
20161116

@@
 The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue is solved by introducing the hierarchical methodology into the basic dual sliding mode controller.
-The proposed method can easily combine with the adaptive technique to  eliminate the adverse effect caused by the input limitation in the rigorous stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the tracking tasks of the rigid robotic manipulator.
+The proposed method can easily combine with the adaptive technique to  eliminate the negative effect caused by the input limitation in the rigorous stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the tracking tasks of the rigid robotic manipulator.
 Simulation results validate the theoretical analyses about the proposed method.
@@
 Zheng et al.
-implemented the SMC law to eliminate the bad effect of the input quantization in the coding and decoding process~\cite{zheng2016sliding}.
+implemented the SMC law to eliminate the negative effect of the input quantization in the coding and decoding process~\cite{zheng2016sliding}.
 Guzman et al.
@@
 Besides the large reaching speed selected, $\gamma$ accelerates the convergence in the sliding phase indirectly.
-Therefore the design of the MDTSM controller for the system~(\ref{eq:simulation second-order system}) is finished, and the corresponding simulation results are illustrated from Figure~\ref{Figure:2} to Figure~\ref{Figure:3}.
+Therefore the design of the MDTSM controller for the system~(\ref{eq:simulation second-order system}) is finished, and the corresponding simulation results are illustrated from Fig.~\ref{Figure:2} to Fig.~\ref{Figure:3}.
 
-From Figure~\ref{Figure:2}, it's apparent that all the states converge to zero as desired.
+From Fig.~\ref{Figure:2}, it's apparent that all the states converge to zero as desired.
 \textcolor{red}{For the nominal system~(\ref{eq:simulation second-order system}) handled by utilizing the MDTSM controller, according to Eq.~(\ref{eq:total convergence time}) and simulation data, we can calculate the maximum theoretical finite convergence time $t_f=5.2609s$ directly.
 The system states, in other words, can be stable in no more than $5.2609s$ theoretically.
-However, the system response results in Figure~\ref{Figure:2_20161108} indicate that all the states have been stable after about $1.5s$, which is far less than $t_f$.
-Hence, from the view of the convergence time, the simulation results are in accordance with the theoretical analyses.} Figure~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely associated with $\eta$, for the purpose of avoiding the large chattering, the boundary layer technique is adopted.
+However, the system response results in Fig.~\ref{Figure:2_20161108} indicate that all the states have been stable after about $1.5s$, which is far less than $t_f$.
+Hence, from the view of the convergence time, the simulation results are in accordance with the theoretical analyses.} Fig.~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely associated with $\eta$, for the purpose of avoiding the large chattering, the boundary layer technique is adopted.
 Although the states have been driven to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range.
@@
 where $x$ is defined as the displacement of the horizontal direction, and $q$ stands for the swing angle from the vertical line.
-$M=1kg$ and $m=0.8kg$ donate the masses of the trolley and the load in Figure~\ref{Figure:8}, respectively, and $g=9.8m/s^2$ refers to as the acceleration of gravity.
+$M=1kg$ and $m=0.8kg$ donate the masses of the trolley and the load in Fig.~\ref{Figure:8}, respectively, and $g=9.8m/s^2$ refers to as the acceleration of gravity.
 $L=0.305m$ represents the length of the rope.
@@
 $c_1=1$, $c_2=4$, $\eta_u = 0.1$, $k_u=1$, $\gamma = 1$, $\lambda = 3$, $\alpha = 0.6$.\par
-Figure~\ref{Figure:9} shows the state response curves of the overhead crane system controlled using the HDSM control scheme, and the results show that the controller stabilize the displacement at $6s$ approximately, though the disturbance exists in the system.
+Fig.~\ref{Figure:9} shows the state response curves of the overhead crane system controlled using the HDSM control scheme, and the results show that the controller stabilize the displacement at $6s$ approximately, though the disturbance exists in the system.
 One can find that the swing angle is fluctuating in a fairly small range, the boundary of which is no more than $1\times 10^-3rad$, and this phenomena is reasonable and also occurs in the stable hierarchical SMC scheme~\cite{wang2004design}.
@@
 In order to evaluate the performance of the proposed control scheme, a simulation about the $2$-link robotic manipulator is presented in the following context.
-Figure~\ref{Figure:1} is the $2$-link manipulator schematic, the dynamics of which can be explained by the dynamic equations in following forms:
+Fig.~\ref{Figure:1} is the $2$-link manipulator schematic, the dynamics of which can be explained by the dynamic equations in following forms:
 \begin{figure}[http]
@@
 \end{figure}
-The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}.
+The performance of the controllers mentioned above is illustrated in Fig.~\ref{Figure:4} and Fig.~\ref{Figure:5}.
 \textcolor{red}{For the MDTSM controller, the joint~1 finishes its desired behavior at about $2.3s$, and meanwhile the joint~2 spends about $1.7s$ completing the desired mission.
@@
 Hence, we can conclude that the results have verified the analyses about the convergence time in Section~\ref{sec:2}.
-The control torques of the joints are depicted in Figure~\ref{Figure:torque}.
+The control torques of the joints are depicted in Fig.~\ref{Figure:torque}.
 It is obvious that the torques of the two joints are both switching dramatically at the beginning, and this phenomenon is caused directly by the rapidly changing sliding mode dynamics $s_i$.
@@
 \end{align*}\par
- \textcolor{red}{The simulation results are demonstrated in Figure~\ref{Figure:6} and Figure~\ref{Figure:7}, which plot the trajectories of joints of the manipulator~(\ref{eq:manipulator}) regulated by adopting the MDTSM controller.
-In Figure~\ref{Figure:6}, the tracking error between the variable desired signal and the joint angle $q_1$ keeps decreasing from the initial status, and the two trajectories reach a confluence at about $3s$, which means that $q_1$ has absolutely tracked the variable desired signal.
-The similar conclusion about $q_2$ can also be obtained from the results in Figure~\ref{Figure:7}.
+ \textcolor{red}{The simulation results are demonstrated in Fig.~\ref{Figure:6} and Fig.~\ref{Figure:7}, which plot the trajectories of joints of the manipulator~(\ref{eq:manipulator}) regulated by adopting the MDTSM controller.
+In Fig.~\ref{Figure:6}, the tracking error between the variable desired signal and the joint angle $q_1$ keeps decreasing from the initial status, and the two trajectories reach a confluence at about $3s$, which means that $q_1$ has absolutely tracked the variable desired signal.
+The similar conclusion about $q_2$ can also be obtained from the results in Fig.~\ref{Figure:7}.
 From the enlarged figures, we can detect that the controller perform the high-precision tracking due to the completely coincident curves after $3s$.
@@
 Consider the case that there exists the input limitation in the manipulator model~(\ref{eq:manipulator}), and without loss of generality, the maximum torque of the joint is $50Nm$.
-Reviewing the torque curve of joint~1  shown in enlarged details of  Figure~\ref{Figure:torque}, we can find that the torque exceeds the reasonable torque upper limit $50Nm$ around $2.3s$.
-If we still use the MDTSM controller to stabilize the system subjected to input limitation, we can not get the same results as shown in Figure~\ref{Figure:torque}, and this is because that the limitation hamper the rigorous theoretical analyses of Theorem~\ref{theorem:2}.
-Hence, to overcome this issue, the adaptive MDTSM controller is applied to diminish the effect of the input limitation and to guarantee the rigorous stability analyses.}
+Reviewing the torque curve of joint~1  shown in enlarged details of  Fig.~\ref{Figure:torque}, we can find that the torque exceeds the reasonable torque upper limit $50Nm$ around $2.3s$.
+If we still use the MDTSM controller to stabilize the system subjected to input limitation, we can not get the same results as shown in Fig.~\ref{Figure:torque}, and this is because that the limitation hamper the rigorous theoretical analyses of Theorem~\ref{theorem:2}.
+Hence, to overcome this issue, the adaptive MDTSM controller is applied to diminish the negative effect of the input limitation and to guarantee the rigorous stability analyses.}
 \begin{figure}
@@
 
-\textcolor{red}{The results shown in Figure~\ref{Figure:limitation_torque} indicate that the joint torques are limited in the region $[-50,50]Nm$ from $0s$ to $0.4s$, while the trajectories in the Figure~\ref{Figure:limitation_q} demonstrates that the manipulator dynamics are still under control.
+\textcolor{red}{The results shown in Fig.~\ref{Figure:limitation_torque} indicate that the joint torques are limited in the region $[-50,50]Nm$ from $0s$ to $0.4s$, while the trajectories in the Fig.~\ref{Figure:limitation_q} demonstrates that the manipulator dynamics are still under control.
 The limitations occur in the beginning stage of the regulation, since the large tracking errors lead to the great command inputs.
 Moveover the boundary layer technique works after $0.4s$ and generates continuous torques in the subsequent time.
-Compared to the results in Figure~\ref{Figure:torque}, we can find that the boundary layer of the adaptive MDTSM controller functions earlier, and this is because that the thickness is modified as $\delta=1\times 10^{-1}$ from $\delta=1\times 10^{-4}$.
+Compared to the results in Fig.~\ref{Figure:torque}, we can find that the boundary layer of the adaptive MDTSM controller functions earlier, and this is because that the thickness is modified as $\delta=1\times 10^{-1}$ from $\delta=1\times 10^{-4}$.
 It implies that $s_i<\delta$ appears earlier for the adaptive MDTSM controller than the MDTSM controller.
-Also, compared to the results from Figure~\ref{Figure:4}, we can find that the rise time of the adaptive MDTSM controller is less, although the torques are limited strictly.
+Also, compared to the results from Fig.~\ref{Figure:4}, we can find that the rise time of the adaptive MDTSM controller is less, although the torques are limited strictly.
 Hence, we can conclude that the proposed adaptive MDTSM controller can regulate the robotic manipulator subjected to the input limitation, and the control performance is even better than the MDTSM controller for the system without input limitation in some extent.}

### 2016-11-16 paper3_manuscript.tex
20161116

@@
 \end{align}
-where $\bm x = [x_1,x_2,x_3,x_4]^T$ is the system state vector ; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$ and $t$; $u_i$, $i=1,2$ stands for the system input; $g_i(\bm x,t)$, $i=1,2$  is defined as the bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0, i=1,2$, meaning uncertainties and disturbances.
+where $\bm x = [x_1,x_2,x_3,x_4]^T$ is the system state vector ; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$ and $t$; $u_i$, $i=1,2$ stands for the system input; $g_i(\bm x,t)$, $i=1,2$  is defined as the bounded nonlinear function that satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0, i=1,2$, meaning uncertainties and disturbances.
 For the system mentioned above, we can design the desired DTSM surface as:
@@
 \end{align}
-in which $k>\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2$, and it's assumed that the parameters $\mu_0$, $\mu_1$ and $\mu_2$ are known.
+where $k>\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2$, and it's assumed that the parameters $\mu_0$, $\mu_1$ and $\mu_2$ are known.
 \end{mythm}
@@
 and hence, based on the analyses in Theorem~\ref{theorem:1}, let $l_1>0.1$ and $l_2>0.8$ guarantee the reaching condition of the desired sliding mode  surface.
-Also, the inputs $u_1$ and $u_2$ can be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation second-order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
+Also, the inputs $u_1$ and $u_2$ can be viewed as virtual input terms that consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation second-order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
 The system is supposed to be controlled to the desired condition $\bm x_d=(0,0,0,0)$ from a prescript condition $\bm x_0=(1.2,1.2,1.2,1.2)$.
@@
 
-\textcolor{red}{At this point, we have verified the feasibility of the MDTSM controller on step responses of the joints of the manipulator, and in most engineering applications, manipulators are required to track the variable desired signals, which own the actual physical meanings, such as polish, machine tools and laser beam cutting.
+\textcolor{red}{At this point, we have verified the feasibility of the MDTSM controller on step responses of the joints of the manipulator, and in most engineering applications, manipulators are required to track the variable desired signals, that own the actual physical meanings, such as polish, machine tools and laser beam cutting.
 Accordingly, the tracking performance of the robotic manipulator controlled by the proposed methods is studied in this section, and we continue to use the parameters of the controller mentioned above, and the mission condition is changed as follows:}
@@
 The limitations occur in the beginning stage of the regulation, since the large tracking errors lead to the great command inputs.
-Moveover the boundary layer technique works after $0.4s$ and generates continuous torques in the subsequent time.
+Moreover the boundary layer technique works after $0.4s$ and generates continuous torques in the subsequent time.
 Compared to the results in Fig.~\ref{Figure:torque}, we can find that the boundary layer of the adaptive MDTSM controller functions earlier, and this is because that the thickness is modified as $\delta=1\times 10^{-1}$ from $\delta=1\times 10^{-4}$.
@@
 \section{Acknowledgment}
-This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61503101).
+This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61673009, 61503101, 91438202).
 \section{References}

### 2017-02-09 paper3_manuscript.tex
20170209

--- 2016-11-16 paper3_manuscript.tex
@@
 This paper proposes a dual terminal sliding mode control scheme for tracking tasks of rigid robotic manipulators.
-\textcolor{red}{As a signiﬁcant novelty, the presented design technique integrates the individual sliding mode  surfaces to achieve the finite time convergence of tracking errors utilizing specially designed construct, and accordingly the convergence time is easily obtained due to the integral design.
+\textcolor{red}{As a significant novelty, the presented design technique integrates the individual sliding mode  surfaces to achieve the finite time convergence of tracking errors utilizing specially designed construct, and accordingly the convergence time is easily obtained due to the integral design.
 The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue is solved by introducing the hierarchical methodology into the basic dual sliding mode controller.
@@
 designed a robust adaptive sliding mode method to ensure the asymptotically stability of a boost converter~\cite{oucheriah2013pwm}.
-Roughly speaking, the SMC scheme is competent for normal scientific missions, due to its insensitivity to parametric uncertainties and external disturbances, however, there still exist some obstacles, such as noncontinuous switching inputs in high frequency and low convergence speed of the tracking errors~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some high-precision engineering applications~\cite{fridman2011sliding}.}
+Roughly speaking, the SMC scheme is competent for normal scientific missions, due to its insensitivity to parameteric uncertainties and external disturbances, however, there still exist some obstacles, such as noncontinuous switching inputs in high frequency and low convergence speed of the tracking errors~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some high-precision engineering applications~\cite{fridman2011sliding}.}
 
@@
 Then the sliding mode dynamics function to drive the system states to the origins along the ideal surfaces in the second step, which is usually known as the sliding phase.
-The reaching phase usually requires the states to reach the ideal sliding mode surfaces in finite time, and suitably selected Lyapunov function and control parameters may accelerate this process; the sliding phase is associated with the designed ideal sliding mode  surfaces closely, and trivial design techniques can guarantee the asymptotically stability of the reduced system~\cite{mu2016switching}.
+The reaching phase usually requires the states reach the ideal sliding mode surfaces in finite time, and suitably selected Lyapunov function and control parameters may accelerate this process; the sliding phase is related to the designed ideal sliding mode  surfaces closely, and trivial design techniques can guarantee the asymptotically stability of the reduced system~\cite{mu2016switching}.
 To achieve a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and compared with the SMC design mentioned above, the most significant contributions of the TSM concept are introducing the finite time convergence to the sliding phase to complete the global finite time convergence~\cite{mu2016switching}.
@@
 
-\textcolor{red}{Notably, the conventional TSM surface design techniques are similar, since the surfaces are all designed for the single variable based on the finite time stability theory, in other words, only the individual variable and its derivative are concerned on by most designers~\cite{mu2016switching}.
-This nature makes the TSM controller become an individual control subsystem, which leads to the complicity of global convergence time in some extent.
+\textcolor{red}{Notably, the conventional TSM surface design techniques are similar, since the surfaces are all designed for the single variable based on the finite time stability theory, in another words, only the individual variable and its derivative are concerned on by most designers~\cite{mu2016switching}.
+This nature makes the TSM controller become an individual control subsystem, which leads to the complication of global convergence time in some extent.
 In this paper, an integral sliding mode  surface design technique breaks the barriers mentioned above, and the novel surface includes two designed variables to guarantee the integral finite time convergence.
-Moreover, nonsingularity of the TSM control scheme, chattering suppressions, underactuated applications and input limitations are also considered in the controller design.}
+Moreover, nonsingularities of the TSM control scheme, chattering suppressions, underactuated applications and input limitations are also considered in the controller design.}
 
@@
 The novel DTSM surface is exploited to achieve the finite time convergence, and the reaching and sliding times can both be calculated directly.
-For coping with the underactuated issue, cooperating with the hierarchical sliding mode  surface design methodology, we combine the hierarchical SMC scheme with the DTSM controller to develop a hierarchical dual TSM (HDTSM) control law to ensure the rigorous stability analyses.
+For coping with the underacutated issue, cooperating with the hierarchical sliding mode  surface design methodology, we combine the hierarchical SMC scheme with the DTSM controller to develop a hierarchical dual TSM (HDTSM) control law to ensure the rigorous stability analyses.
 A modified DTSM (MDTSM) control scheme is presented to regulate the motion of the $n$-link robotic manipulators, and the case subjected to input limitations is also taken into consideration.
-The remained paper is organized as follows: Section~\ref{sec:2} introduces the DTSM controller, and the finite time convergence is discussed.
-Furthermore, we provide the DTSM control scheme with extra design parameters to obtain the MDTSM controller, which performs better in theoretical analyses; for stabilizing underactuated systems, the HDTSM controller design is also developed in this section.
+The remained paper is organized as follows: Section~\ref{sec:2} introduces the DTSM controller, and the finite time convergences of the reaching and sliding phase are discussed.
+Furthermore, we provide the DTSM control scheme with extra design parameters to obtain the MDTSM controller, which performs better in theoretical analyses; for stabilizing underactuated systems, the HDTSM design is also developed in this section.
 In Section~\ref{sec:3}, the MDTSM control law is applied to the motion control system of the $n$-link robotic  manipulator, and the stability analyses are also carried out.
@@
 \end{align}
-and one can select the function $V = \frac{x_1^2+x_2^2}{2}$ to obtain the finite convergence time as follows~\cite{moulay2006finite}:
+and oen can select the function $V = \frac{x_1^2+x_2^2}{2}$ to obtain the finite convergence time as follows~\cite{moulay2006finite}:
 %since $\vert x\vert-x^\alpha+\vert x\vert \ge 0,0<\alpha<1$
@@
 \end{mylem}
-\textcolor{red}{For stabilization of the second-order system shown as Eq.~(\ref{eq:second-order system}), DTSM control inputs are stated according the following theorem.}
+\textcolor{red}{For stabilization of the second-order system shown as~Eq.~(\ref{eq:second-order system}), DTSM control inputs are stated according to the following to theorem.}
 \begin{mythm}\label{theorem:1}DTSM Controller Design.
@@
 \end{split}\end{align}
-are the equivalent control inputs, which ensure $\dot s_1 = 0$ and $\dot s_2=0$ with $u_i = u_{eqi}$, $i=1,2$.
+are the eauivalent control inputs, which ensure $\dot s_1 = 0$ and $\dot s_2=0$ with $u_i = u_{eqi}$, $i=1,2$.
 The switching inputs can be selected as $u_{swi}=-b_i^{-1}k_isgn(s_i)$, $i=1,2$ to guarantee the finite time reaching conditions of the sliding mode  surface.}
 
-Consider the Lyapunov function $V=\frac{1}{2}{\bm s}^T\bm s$, which has
+Considering the Lyapunov function $V=\frac{1}{2}{\bm s}^T\bm s$, it has
 \begin{align}
@@
 \end{align}
-Substituting inputs (\ref{eq:DSM input}) in Eq.~(\ref{eq:V_1}) yields
+Substituting inputs (\ref{eq:DSM input}) in~Eq.~(\ref{eq:V_1}) yields
 \begin{align*}
@@
 In the MDTSM control scheme, the performances of the reaching and sliding phases can benefit from suitably selected $\lambda$ and $\gamma$ analytically.
-The establishment of $V(t_0)$ depends on $\lambda$, if the state $\bm x(t_0)$ has been fixed.
+The establishment of $V(t_0)$ is depended on $\lambda$, if the state $\bm x(t_0)$ has been fixed.
 Exactly, $\lambda$ affects the reaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V=\bm s^T\bm s = \bm 0,\forall t\ge t_r$.
-$\eta$ is defined as the reaching speed, because a suitable $\eta$ can adjust the reaching time as desired in some extent.
-Hence, $\lambda$ cooperates with $\eta$ to manage the reaching phase dynamics, and similarly the parameter $\gamma$ determine the convergence speed of the sliding phase dynamics.
+$\eta$ is definied as the reaching speed, because a suitable $\eta$ can adjust the reaching time as desired in some extent.
+Hence, $\lambda$ cooperates with $\eta$ to manage the reaching phase dynamics, and similarly the parameter $\gamma$ determine the convergent speed of the sliding phase dynamics.
 \begin{myrem}
@@
 
-The finite time convergence of the MDTSM controller has been verified clearly, but similar to the conventional TSM control scheme, there exists another obstacle in the design mentioned above, i.e., the issue of the singularity in control inputs.
+The finite time convergences of the DTSM and MDTSM controllers have been verified clearly, but similar to the conventional TSM control scheme, there exists another obstacle in the design mentioned above, i.e., the issue of the singularity in control inputs.
 Essentially, the singularity occurs in Eq.~(\ref{eq:modified input}) when $x_1=0$ but $x_2\neq 0$ in $u_1$ (the phenomena happens to $u_2$ under the same condition).
-To cope with the singularity, the nonsingular MDTSM control scheme is presented after introducing the analytical technique into the MDTSM controller based on the following lemma~\cite{feng2013nonsingular}.
+To cope with the singularity, the nonsingular MDTSM control scheme is presented after introducing an analytical technique into the MDTSM controller based on the following lemma~\cite{feng2013nonsingular}.
 \begin{mylem}\label{lemma:3}
@@
 \end{align}
-where $f_b(u) = R(u)u$ is a bounded function, which owns the properties as follows:
+whree $f_b(u) = R(u)u$ is a bounded function, which owns the properties as follows:
 \begin{align}\begin{split}
@@
 \end{split}\end{align}
-$\dot V$ is therefore negative semi-definite while $V_1$ is positive definite.
+$\dot V$ is therefore negative semi-deﬁnite while $V_1$ is positive deﬁnite.
 Since  $s_i$ is bounded according to assumption~\ref{myas:1}, we can have $\lim_{t\to\infty}V<\infty$ and proceed to deduce the integration of inequality~(\ref{V linmitation}) to obtain following results
@@
 \end{split}\end{align}
-Hence we can conclude that the sliding dynamics are asymptotically stable in the light of Barbalat lemma.
+Hence we can conclude that the sliding dynamics are asymptotically stable in the light of Barbalat’s lemmas.
 Here the proof completes, and the system states can converge to origins by referring to the analyses in Theorem~\ref{theorem:1}.
@@
 Referring to Theorem \ref{theorem:4}, it's easy to obtain the MDTSM input for the even $n$-link manipulator.
-Essentially, this technique requires that the sliding mode  surface has to consist of $n/2$ pairs of individual sliding mode  surfaces, in other words, this design for the surface can be regarded to design the sliding mode  surfaces for the $n/2$ sub-systems.\par
+Essentially, this technique requires that the sliding mode  surface has to consist of $n/2$ pairs of individual sliding mode  surfaces, in another words, this design for the surface can be regarded to design the sliding mode  surfaces for the $n/2$ sub-systems.\par
 Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence one individual dimension can be controlled by using the conventional TSM control scheme, which results in that the remained $n-1$-link manipulator can be controlled by the proposed MDTSM control scheme.
@@
 One can also use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the DTSM control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically.
-For handling the chattering, the $sign(x)$ can be replaced with $sat(x,\delta)$, and the boundary layer thickness can be selected as $\delta=1\times 10^{-4}$.
-\textcolor{red}{Incorporating the adaptive MDTSM technique, the manipulator dynamics subjected to the input limitation can also be stabilized as desired.}
+For handling the chattering, the $sign(x)$ can be replaced with $sat(x,\delta)$, and the boundedness thickness can be selected as $\delta=1\times 10^{-4}$.
+\textcolor{red}{Incorporating the adaptive MDTSM technique, the manipulator dynamics subjected to the input limitation can also been stabilized as desired.}
 \end{myrem}
 \section{Simulation studies}\label{sec:4}
-In this section, three simulations will be presented, namely, the verification on the effectiveness of the DTSM and MDTSM controllers, the underactuated example and the robotic manipulator stabilization, to evaluate the performance of the proposed control schemes.
+In this section, three simulations will be presented, namely, a verification on the effectiveness of the DTSM and MDTSM controllers, an underactuated example and the robotic manipulator stabilization, to evaluate the performance of the proposed control schemes.
 \subsection{Effectiveness study}
@@
 Also, the inputs $u_1$ and $u_2$ can be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation second-order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
-The system is supposed to be controlled to the desired condition $\bm x_d=(0,0,0,0)$ from a prescript condition $\bm x_0=(1.2,1.2,1.2,1.2)$.
-Admittedly, this prescript condition leads to a large initial reaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding mode  surface, therefore a large reaching speed $k$ is required correspondingly.
+The system is supposed to be conducted to the desired condition $\bm x_d=(0,0,0,0)$ from a prescript condition $\bm x_0=(1.2,1.2,1.2,1.2)$.
+Admittedly, this prescript condition leads to a lager initial reaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding mode  surface, therefore a large reaching speed $k$ is required correspondingly.
 The control parameters are chosen as: $\alpha = 0.6$, $\lambda = 0.5$, $\gamma = 3$ and $k = 20$.
@@
 
-From Figure~\ref{Figure:2}, it's apparent that all the states converge to zero as desired.
-\textcolor{red}{For the nominal system~(\ref{eq:simulation second-order system}) handled by utilizing the MDTSM controller, according to Eq.~(\ref{eq:total convergence time}) and simulation data, we can calculate the maximum theoretical finite convergence time $t_f=5.2609s$ directly.
+From Figure~\ref{Figure:2}, it is apparent that all the states converge to zero as desired.
+\textcolor{red}{For the nominal system~(\ref{eq:simulation second-order system}) handled by utilizing the MDTSM controller, accrording to Eq.~(\ref{eq:total convergence time}) and simulation datas, we can calculate the maximum theoretical finite convergence time $t_f=5.2609s$ directly.
 The system states, in other words, can be stable in no more than $5.2609s$ theoretically.
 However, the system response results in Figure~\ref{Figure:2_20161108} indicate that all the states have been stable after about $1.5s$, which is far less than $t_f$.
-Hence, from the view of the convergence time, the simulation results are in accordance with the theoretical analyses.} Figure~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely associated with $\eta$, for the purpose of avoiding the large chattering, the boundary layer technique is adopted.
+Hence, from the view of the convergence time, the simulation results are in accordance with the theoretical analyses.} Figure~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely related to $\eta$, for the purpose of avoiding the large chattering, the boundary layer technique is adopted.
 Although the states have been driven to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range.
@@
 At this point, some effectiveness of the proposed MDTSM control scheme has been verified, and in Section \ref{sec:robotica manipulator}, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.
-\begin{figure}[http]
+\begin{figure}
 \centering
@@
 
-\begin{figure}[http]
+\begin{figure}
 \centering
@@
 \label{Figure:3}
-\end{figure}
-\begin{figure}[http]
-\centering
-\includegraphics[width=0.3\textwidth]{paper3_fig8.eps}
-\caption{Overhead crane schematic}
-\label{Figure:8}
 \end{figure}
@@
 One can find that the swing angle is fluctuating in a fairly small range, the boundary of which is no more than $1\times 10^-3rad$, and this phenomena is reasonable and also occurs in the stable hierarchical SMC scheme~\cite{wang2004design}.
-\begin{figure}[http]
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{paper3_fig8.eps}
+\caption{Overhead crane schematic}
+\label{Figure:8}
+\end{figure}
+\begin{figure}
 \centering
@@
 Figure~\ref{Figure:1} is the $2$-link manipulator schematic, the dynamics of which can be explained by the dynamic equations in following forms:
-\begin{figure}[http]
+\begin{figure}
 \centering
@@
 In this model, the uncertainty is brought in by estimated terms, namely, $\bar m_1=0.4$ and $\bar m_2=1.2$ which are all not the actual value obviously.
+In addition, owing to that it sits on many terms in the dynamic equations, it's a severe challenge to guarantee the stability of the system.
 Accordingly, the uncertainty parameters in Eq.~(\ref{eq:manipulator uncertainty}) are assumed to be $\mu_0=10$, $\mu_1=3$, $\mu_2=3$.
@@
 
-\begin{figure}[http]
+The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}.
+\textcolor{red}{For the MDTSM controller, the jiont~1 finishes its desired behaviour at about $2.3s$, and meanwhile the joint~2 spends about $1.7s$ completing the desired mission.
+Also, by observing the results, we can find that the stabilization time of the proposed method is less than the TSM controller's, and the regulating process of the manipulators is steady and reasonable.
+We can calculate the maximum theoretical finite convergence time $t_f=3.0843s$, which can be obtained directly accoring to Eq.~(\ref{eq:total convergence time}) and simulation datas, is more than $2.3s$, the convergence time of the simulation result.
+Hence, we can conclude that the results have verified the analyses about the convergence time in Section~\ref{sec:2}.
+The control torques of the joints are depicted in Figure~\ref{Figure:torque}.
+It is obvious that the torques of the two jionts are both switching dramatically at the beginning, and this phenomenon is caused directly by the rapidly changing sliding mode dynamics $s_i$.
+Moreover, at about $1.7s$, all the joint states are regulated to locate in the vicinity of the origin, but the sliding mode dynamics do not yet enter the boundary layer $s_i< \delta$.
+This switching inputs last about $2.7s$ before reaching the boundary layer.
+After $2.7s$ boundary layer technique works to generate continuous torques, which maintain a reasonable constant in the subsequent time, since the overall system have been stable.} Therefore these results show that the MDTSM control scheme can achieve the regulation of the manipulator effectively.
+\begin{figure}
 \centering
@@
 \end{figure}
-The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}.
-\textcolor{red}{For the MDTSM controller, the joint~1 finishes its desired behavior at about $2.3s$, and meanwhile the joint~2 spends about $1.7s$ completing the desired mission.
-Also, by observing the results, we can find that the stabilization time of the proposed method is less than the TSM controller's, and the regulating process of the manipulators is steady and reasonable.
-Through calculation, we can find the maximum theoretical finite convergence time $t_f=3.0843s$, which can be obtained directly according to Eq.~(\ref{eq:total convergence time}) and simulation data, is more than $2.3s$, the convergence time of the simulation result.
-Hence, we can conclude that the results have verified the analyses about the convergence time in Section~\ref{sec:2}.
-The control torques of the joints are depicted in Figure~\ref{Figure:torque}.
-It is obvious that the torques of the two joints are both switching dramatically at the beginning, and this phenomenon is caused directly by the rapidly changing sliding mode dynamics $s_i$.
-Moreover, at about $1.7s$, all the joint states are regulated to locate in the vicinity of the origin, but the sliding mode dynamics do not yet enter the boundary layer $s_i< \delta$.
-This switching inputs last about $2.7s$ before reaching the boundary layer.
-After $2.7s$ boundary layer technique works to generate continuous torques, which maintain a reasonable constant in the subsequent time, since the overall system has been stable.} Therefore these results show that the MDTSM control scheme can achieve the regulation of the manipulator effectively.
 
-\textcolor{red}{At this point, we have verified the feasibility of the MDTSM controller on step responses of the joints of the manipulator, and in most engineering applications, manipulators are required to track the variable desired signals, which own the actual physical meanings, such as polish, machine tools and laser beam cutting.
+\textcolor{red}{At this point, we have verifed the feasibility of the MDTSM controller on step responses of the joints of the manipulator, and in mostly engineering applications, manipulators are required to track the variable desied signals, which own the actual physical meanings, such as polish, machine tools and laser beam cutting.
 Accordingly, the tracking performance of the robotic manipulator controlled by the proposed methods is studied in this section, and we continue to use the parameters of the controller mentioned above, and the mission condition is changed as follows:}
@@
 Taken as a whole, the control system completes the tracking mission at about $3.2s$ from the prescript initial conditions, which performs the smoothly tracking motion subjected to the variable desired signals.}
-\begin{figure}[http]
+\begin{figure}
 \centering
@@
 \textcolor{red}{Another important issue that we always meet in engineering applications, is the actuator constraint due to the physical limitation, which can be regarded as the input limitation problem shown in Eq.~(\ref{eq:second-order system subjected to limitation}).
-Consider the case that there exists the input limitation in the manipulator model~(\ref{eq:manipulator}), and without loss of generality, the maximum torque of the joint is $50Nm$.
+Consider the case that there exist the input limitation in the manipulator model~(\ref{eq:manipulator}), and without loss of generality, the maximum torque of the joint is $50Nm$.
 Reviewing the torque curve of joint~1  shown in enlarged details of  Figure~\ref{Figure:torque}, we can find that the torque exceeds the reasonable torque upper limit $50Nm$ around $2.3s$.
 If we still use the MDTSM controller to stabilize the system subjected to input limitation, we can not get the same results as shown in Figure~\ref{Figure:torque}, and this is because that the limitation hamper the rigorous theoretical analyses of Theorem~\ref{theorem:2}.
-Hence, to overcome this issue, the adaptive MDTSM controller is applied to diminish the effect of the input limitation and to guarantee the rigorous stability analyses.}
+Hence, to overcom this issue, the adaptive MDTSM controller is applied to diminish the effect of the input limitation and to guarantee the rigorous stability analyses.}
+
+\textcolor{red}{Here we examine the step response of the adaptive MDTSM control scheme for the robotic manipulator dynamics, since the step response is a severe challenge to the controller.
+Accordingly, the initial and desired conditions are $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$, respectively.
+The design parameters of the adaptive MDTSM controller can be selected as $\varpi_1=50$, $\varpi_2=30$, $\varphi_1=\varphi_2=0.01$, $\nu_1 = 5$, $\nu_2=6$, $\omega_1=\omega_2=1$ to satisfy the parameter conditions in Theorem~\ref{thm:4}.
+In addition, for better tracking performance, the boundary layer thickness is revised as $\delta=0.1$.
+}
+
+\textcolor{red}{The results shown in Figure~\ref{Figure:limitation_torque} indicate that the joint torques are limited in the region $[-50,50]Nm$ from $0s$ to $0.4s$, while the trajectories in the Figure~\ref{Figure:limitation_q} demonstrates that the manipulator dynamics are still under control.
+The limitations occur in the beginning stage of the regulation, since the great tracking errors leads to the great command inputs.
+Moveover the boundary layer technique works after $0.4$ and generates continuous torques in the subsequent time.
+Compared to the results in Figure~\ref{Figure:torque}, we can find detect that the boundary layer of the adaptive MDTSM controller functions earlier, and this is because that the thickness is modified as $\delta=1\times 10^{-1}$ from $\delta=1\times 10^{-4}$.
+It implies that $s_i<\delta$ appears earlier for the adaptive MDTSM controller than the MDTSM controller.
+Also, compared to the results from Figure~\ref{Figure:4}, we can find that the rise time of the adaptive MDTSM controller is less, although the torques are limited strictly.
+Hence, we can conclude that the proposed adaptive MDTSM controller can regulate the robotic manipulator subjectd to the input limitation, and the control performance is even better than the MDTSM controller for the system without input limitation in some extent.}
 \begin{figure}
@@
 \end{figure}
-\textcolor{red}{Here we examine the step response of the adaptive MDTSM control scheme for the robotic manipulator dynamics, since the step response is a severe challenge to the controller.
-Accordingly, the initial and desired conditions are $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$, respectively.
-The design parameters of the adaptive MDTSM controller can be selected as $\varpi_1=50$, $\varpi_2=30$, $\varphi_1=\varphi_2=0.01$, $\nu_1 = 5$, $\nu_2=6$, $\omega_1=\omega_2=1$ to satisfy the parameter conditions in Theorem~\ref{thm:4}.
-In addition, for better tracking performance, the boundary layer thickness is revised as $\delta=0.1$.
-}
-
-\textcolor{red}{The results shown in Figure~\ref{Figure:limitation_torque} indicate that the joint torques are limited in the region $[-50,50]Nm$ from $0s$ to $0.4s$, while the trajectories in the Figure~\ref{Figure:limitation_q} demonstrates that the manipulator dynamics are still under control.
-The limitations occur in the beginning stage of the regulation, since the large tracking errors lead to the great command inputs.
-Moveover the boundary layer technique works after $0.4s$ and generates continuous torques in the subsequent time.
-Compared to the results in Figure~\ref{Figure:torque}, we can find that the boundary layer of the adaptive MDTSM controller functions earlier, and this is because that the thickness is modified as $\delta=1\times 10^{-1}$ from $\delta=1\times 10^{-4}$.
-It implies that $s_i<\delta$ appears earlier for the adaptive MDTSM controller than the MDTSM controller.
-Also, compared to the results from Figure~\ref{Figure:4}, we can find that the rise time of the adaptive MDTSM controller is less, although the torques are limited strictly.
-Hence, we can conclude that the proposed adaptive MDTSM controller can regulate the robotic manipulator subjected to the input limitation, and the control performance is even better than the MDTSM controller for the system without input limitation in some extent.}
 \section{Conclusion}\label{sec:5}
@@
 Also, the entire convergence time can be calculated accordingly.
-Developing the basic DTSM yields the MDTSM controller, which provides a solution to eliminating chattering, avoiding singularity and fast convergence.
-For dealing with the underactuated characteristics which may appear in the system, the HDTSM control is derived, and the overhead crane example verifies its effectiveness.
+Developing the basic DTSM yields the MDTSM controller, providing a solution to eliminating chattering, avoiding singularity and fast convergence.
+For dealing with the under actuated characteristics which may appear in the system, the HDTSM control is derived, and the overhead crane example verifies its effectiveness.
 However, the control parameters selection is still a challenge especially in the HDTSM control scheme, and we will effort to excavate a full order dual TSM methodology in the future for removing the obstacle caused by parameters essentially.

### 2017-07-13 paper3_manuscript.tex

--- 2016-11-16 paper3_manuscript.tex
@@
 \begin{abstract}
+
 This paper proposes a dual terminal sliding mode control scheme for tracking tasks of rigid robotic manipulators.
-\textcolor{red}{As a signiﬁcant novelty, the presented design technique integrates the individual sliding mode  surfaces to achieve the finite time convergence of tracking errors utilizing specially designed construct, and accordingly the convergence time is easily obtained due to the integral design.
+\textcolor{red}{As a significant novelty, the presented design technique integrates the individual sliding mode  surfaces to achieve the finite time convergence of tracking errors utilizing specially designed construct, and accordingly the convergence time is easily obtained due to the integral design.
 The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue is solved by introducing the hierarchical methodology into the basic dual sliding mode controller.
-The proposed method can easily combine with the adaptive technique to  eliminate the negative effect caused by the input limitation in the rigorous stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the tracking tasks of the rigid robotic manipulator.
+The proposed method can easily combine with the adaptive technique to  eliminate the adverse effect caused by the input limitation in the rigorous stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the tracking tasks of the rigid robotic manipulator.
 Simulation results validate the theoretical analyses about the proposed method.
+
 \end{abstract}
@@
 \end{mylem}
-\textcolor{red}{For stabilization of the second-order system shown as Eq.~(\ref{eq:second-order system}), DTSM control inputs are stated according the following theorem.}
+
+\textcolor{red}{For stabilization of the second-order system shown as~Eq.~(\ref{eq:second-order system}), DTSM control inputs are stated according to the following to theorem.}
+
 \begin{mythm}\label{theorem:1}DTSM Controller Design.
@@
 
-From Fig.~\ref{Figure:2}, it's apparent that all the states converge to zero as desired.
-\textcolor{red}{For the nominal system~(\ref{eq:simulation second-order system}) handled by utilizing the MDTSM controller, according to Eq.~(\ref{eq:total convergence time}) and simulation data, we can calculate the maximum theoretical finite convergence time $t_f=5.2609s$ directly.
+From Figure~\ref{Figure:2}, it is apparent that all the states converge to zero as desired.
+\textcolor{red}{For the nominal system~(\ref{eq:simulation second-order system}) handled by utilizing the MDTSM controller, accrording to Eq.~(\ref{eq:total convergence time}) and simulation datas, we can calculate the maximum theoretical finite convergence time $t_f=5.2609s$ directly.
 The system states, in other words, can be stable in no more than $5.2609s$ theoretically.
-However, the system response results in Fig.~\ref{Figure:2_20161108} indicate that all the states have been stable after about $1.5s$, which is far less than $t_f$.
-Hence, from the view of the convergence time, the simulation results are in accordance with the theoretical analyses.} Fig.~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely associated with $\eta$, for the purpose of avoiding the large chattering, the boundary layer technique is adopted.
+However, the system response results in Figure~\ref{Figure:2_20161108} indicate that all the states have been stable after about $1.5s$, which is far less than $t_f$.
+Hence, from the view of the convergence time, the simulation results are in accordance with the theoretical analyses.} Figure~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely related to $\eta$, for the purpose of avoiding the large chattering, the boundary layer technique is adopted.
 Although the states have been driven to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range.
 The nature of the situation mentioned above means that the fluctuating inputs compensate the error caused by the disturbance.\par
+
 At this point, some effectiveness of the proposed MDTSM control scheme has been verified, and in Section \ref{sec:robotica manipulator}, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.
